---
title: "12-Month Postpartum"
subtitle: "Inventory Cleaning"
format:
  html:
    toc: true
    toc-float: true
    df-print: paged
    code-folding: show
editor_options: 
  markdown: 
    wrap: 72
---

## To Do List

## Specific measures

-   PBQ anxiety and incipient abuse subscales have low cronbach's alpha
-   MAT has low cronbach's alpha
-   PRQ has low cronbach's alpha
-   PSQI has low cronbach's alpha
-   IMS commitment has low cronbach's alpha

# Set Up

::: panel-tabset
## Notes

**SPSS File Name:** HATCH Syntax for 12-M Qs.sps

**Qualtrics File Name:** 12pp_HATCH One-Year Survey 11.16.2017

## Packages

```{r}
#| warning: false
#| message: false

library(tidyverse) # for data cleaning
library(here) # to quickly find data files
library(haven); library(labelled) # to manipulate SPSS files and add SPSS-style labels
library(chron) # to manipulate time and date variables
library(sjmisc) # for rowwise functions (row_count function)
library(data.table) # for renaming variables (setnames function)
library(kableExtra) # to print tables more neatly (kbl wrapping function) 
library(nestclean) # the package I wrote to help check our work
library(nestPSQI) # the package I wrote to help clean up PSQI
```

## Load Data

```{r}
df <- read_sav(here("data/4_demographics", "12pp_demo.sav")) %>%
  mutate(across(where(is.character), ~ na_if(.x, ""))) # replace blank cells with NA

df.old <- df # so that I can refresh df quickly without scrolling back to top 
```
:::

# Inventories

## ASQ12: Ages and Stages Questionnaire, 12-month

::::: panel-tabset
### Notes

-   Squires & Bricker, 2009
-   6 questions per developmental domain + 9 additional overall
    questions
-   For developmental questions: 3-point Likert scale
    -   0 = not yet
    -   5 = sometimes
    -   10 = yes
-   For overall questions: 0-1 binary
    -   0 = no
    -   1 = not yet
-   Sum scores
    -   Higher scores = more advanced development
-   Subscales:
    -   Communication
    -   Gross motor
    -   Fine motor
    -   Problem solving
    -   Personal/social
    -   Overall
-   No reverse scores
-   Other scores notes:
    -   If three or more items are missing, do not score the
        area—screening results may not be accurate.
    -   If one or two items are missing, you will need to calculate an
        adjusted score.
        -   Replace missing items with mean score of other items in the
            section
    -   Refer to scoring guidelines for cut-off information and
        information on "overall" items

### Script

#### Recode item scores

```{r}
df <- df %>%
  # Yes, Sometimes, Not Yet
  mutate(across(c(ASQ12_c1.12pp:ASQ12_s6.12pp), 
            ~case_when( 
                        . == 1 ~ 10,
                        . == 1 ~ 5,
                        . == 3 ~ 0,
                        .default = NA))) %>%
  # Yes/No
  mutate(across(c(ASQ12_o1.12pp:ASQ12_o9.12pp),
            ~case_when(
              . == 1 ~ 1,
              . == 2 ~ 0,
              .default = NA)))
```

#### Mean-replace missing items

```{r}
df <- df %>%
  
  # Tell R that we want to work across a row
  rowwise() %>%
  
  # Find rows with 2 or fewer NAs and replace NA with subscale mean
  mutate(across(ASQ12_c1.12pp:ASQ12_c6.12pp, 
            ~ case_when(
              is.na(.) == T & sum(is.na(c_across(ASQ12_c1.12pp:ASQ12_c6.12pp))) <= 2 ~ mean(c_across(ASQ12_c1.12pp:ASQ12_c6.12pp), na.rm = T), 
              .default = .))) %>%
  mutate(across(ASQ12_gm1.12pp:ASQ12_gm6.12pp, 
            ~ case_when(
              is.na(.) == T & sum(is.na(c_across(ASQ12_gm1.12pp:ASQ12_gm6.12pp))) <= 2 ~ mean(c_across(ASQ12_gm1.12pp:ASQ12_gm6.12pp), na.rm = T), 
              .default = .))) %>%
  mutate(across(ASQ12_fm1.12pp:ASQ12_fm6.12pp, 
            ~ case_when(
              is.na(.) == T & sum(is.na(c_across(ASQ12_fm1.12pp:ASQ12_fm6.12pp))) <= 2 ~ mean(c_across(ASQ12_fm1.12pp:ASQ12_fm6.12pp), na.rm = T), 
              .default = .))) %>%
  mutate(across(ASQ12_ps1.12pp:ASQ12_ps6.12pp, 
            ~ case_when(
              is.na(.) == T & sum(is.na(c_across(ASQ12_ps1.12pp:ASQ12_ps6.12pp))) <= 2 ~ mean(c_across(ASQ12_ps1.12pp:ASQ12_ps6.12pp), na.rm = T), 
              .default = .))) %>%
  mutate(across(ASQ12_s1.12pp:ASQ12_s6.12pp, 
            ~ case_when(
              is.na(.) == T & sum(is.na(c_across(ASQ12_s1.12pp:ASQ12_s6.12pp))) <= 2 ~ mean(c_across(ASQ12_s1.12pp:ASQ12_s6.12pp), na.rm = T), 
              .default = .)))
  
```

#### Calculate summary scores

```{r}
df <- df %>% 
  
  # Tell R that we want to take the sum across a row
  rowwise() %>%
  
  # Calculate total scores/subscales
  mutate(ASQ12_comm.12pp = sum(c_across(ASQ12_c1.12pp:ASQ12_c6.12pp), na.rm = T),
         ASQ12_gross.12pp = sum(c_across(ASQ12_gm1.12pp:ASQ12_gm6.12pp), na.rm = T),
         ASQ12_fine.12pp = sum(c_across(ASQ12_fm1.12pp:ASQ12_fm6.12pp), na.rm = T),
         ASQ12_probsolve.12pp = sum(c_across(ASQ12_ps1.12pp:ASQ12_ps6.12pp), na.rm = T),
         ASQ12_social.12pp = sum(c_across(ASQ12_s1.12pp:ASQ12_s6.12pp), na.rm = T)) %>% 
  
  # Replace 0's with NA
  mutate(across(ASQ12_comm.12pp:ASQ12_social.12pp, ~na_if(., 0))) %>%
  
  # Move the total score/subscales so they come immediately after the measures
  relocate(ASQ12_comm.12pp:ASQ12_social.12pp, .after = ASQ12_o9.12pp)
```

### Label

```{r}
df <- df %>% 
  
  # Tell R that scores are numeric
  mutate(across(ASQ12_c1.12pp:ASQ12_s6.12pp, as.numeric)) %>%
  
  # Create value and variable labels
  mutate(across(ASQ12_c1.12pp:ASQ12_c6.12pp,
            ~ labelled(., 
                       c("Yes" = 10, "Sometimes" = 5, "Not yet" = 0, 
                         "Mean-replaced" = 2, "Mean-replaced" = 2.5, 
                         "Mean-replaced" = 4, "Mean-replaced" = 6,
                         "Mean-replaced" = 7.5, "Mean-replaced" = 8), 
                       label = "ASQ 12-Month: Communication"))) %>%
  mutate(across(ASQ12_gm1.12pp:ASQ12_gm6.12pp,
            ~ labelled(., 
                       c("Yes" = 10, "Sometimes" = 5, "Not yet" = 0,  
                         "Mean-replaced" = 2, "Mean-replaced" = 2.5, 
                         "Mean-replaced" = 4, "Mean-replaced" = 6,
                         "Mean-replaced" = 7.5, "Mean-replaced" = 8), 
                       label = "ASQ 12-Month: Gross Motor"))) %>% 
  mutate(across(ASQ12_fm1.12pp:ASQ12_fm6.12pp,
            ~ labelled(., 
                       c("Yes" = 10, "Sometimes" = 5, "Not yet" = 0,  
                         "Mean-replaced" = 2, "Mean-replaced" = 2.5, 
                         "Mean-replaced" = 4, "Mean-replaced" = 6,
                         "Mean-replaced" = 7.5, "Mean-replaced" = 8), 
                       label = "ASQ 12-Month: Fine Motor"))) %>% 
  mutate(across(ASQ12_ps1.12pp:ASQ12_ps6.12pp,
            ~ labelled(., 
                       c("Yes" = 10, "Sometimes" = 5, "Not yet" = 0,  
                         "Mean-replaced" = 2, "Mean-replaced" = 2.5, 
                         "Mean-replaced" = 4, "Mean-replaced" = 6,
                         "Mean-replaced" = 7.5, "Mean-replaced" = 8),  
                       label = "ASQ 12-Month: Problem Solving"))) %>% 
  mutate(across(ASQ12_s1.12pp:ASQ12_s6.12pp,
            ~ labelled(., 
                       c("Yes" = 10, "Sometimes" = 5, "Not yet" = 0,  
                         "Mean-replaced" = 2, "Mean-replaced" = 2.5, 
                         "Mean-replaced" = 4, "Mean-replaced" = 6,
                         "Mean-replaced" = 7.5, "Mean-replaced" = 8), 
                       label = "ASQ 12-Month: Personal-Social"))) %>%
  mutate(across(ASQ12_o1.12pp:ASQ12_o9.12pp,
            ~ labelled(., 
                       c("Yes" = 1, "No" = 0), 
                       label = "ASQ 12-Month: Overall"))) %>%
  mutate(ASQ12_comm.12pp = labelled(ASQ12_comm.12pp, label = "ASQ 12-Month: Communication Total"), 
         ASQ12_gross.12pp = labelled(ASQ12_gross.12pp, label = "ASQ 12-Month: Gross Motor Total"),
         ASQ12_fine.12pp = labelled(ASQ12_fine.12pp, label = "ASQ 12-Month: Fine Motor Total"), 
         ASQ12_probsolve.12pp = labelled(ASQ12_probsolve.12pp, label = "ASQ 12-Month: Problem Solving Total"), 
         ASQ12_social.12pp = labelled(ASQ12_social.12pp, label = "ASQ 12-Month: Personal-Social Total"))
```

### Check and Print

:::: panel-tabset
#### Check

::: panel-tabset
##### Check Counts

```{r}
#| echo: false
check_categorical(df, c(ASQ12_c1.12pp:ASQ12_s6.12pp)) %>% arrange(value)  %>% knitr::kable()
check_categorical(df, c(ASQ12_o1.12pp:ASQ12_o9.12pp)) %>% knitr::kable()
```

##### Check Numbers

```{r}
#| echo: false
check_continuous(df, ASQ12_comm.12pp:ASQ12_social.12pp) %>% knitr::kable()
```

##### Check Reliability

###### Communication Subscale

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, ASQ12_c1.12pp:ASQ12_c6.12pp), na.rm = T)
```

###### Gross Motor Subscale

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, ASQ12_gm1.12pp:ASQ12_gm6.12pp), na.rm = T)
```

###### Fine Motor Subscale

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, ASQ12_fm1.12pp:ASQ12_fm6.12pp), na.rm = T)
```

###### Problem Solving Subscale

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, ASQ12_ps1.12pp:ASQ12_ps6.12pp), na.rm = T)
```

###### Personal/Social Subscale

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, ASQ12_s1.12pp:ASQ12_s6.12pp), na.rm = T)
```

##### Check Variable Labels

```{r}
#| echo: false
inspect_labels(df, contains("ASQ12")) 
```
:::

#### Print

```{r}
#| echo: false
print_slice(df, contains("ASQ12"))
```
::::
:::::

## BCQ: Baby Care Questionnaire

::::: panel-tabset
### Notes

-   Winstanley & Gattis, 2013
-   30 items
    -   3 sections: Sleeping, Feeding, Soothing
-   1-4 Likert scale
    -   1=strongly disagree
    -   4=strongly agree
-   Mean scores
    -   Higher scores = higher structure/attunement
-   Subscales:
    -   Structure
        -   S1-S6
        -   E1-E3, E6, E7, E10
        -   So1, So2, So4, So9, So10
    -   Attunement
        -   S7-S9
        -   E4, E5, E8, E9
        -   So3, So5, So6-So8, So11
-   Reverse score for
    -   S1-S3, S9
    -   E2, E3, E5, E6, E9, E10
    -   So2-So5, So7, So10

### Script

#### Reverse item scores

```{r}
df <- df %>%
  mutate(across(c(BCQ_S1.12pp:BCQ_S3.12pp, BCQ_S9.12pp, 
                  BCQ_E2.12pp, BCQ_E3.12pp, BCQ_E5.12pp, BCQ_E6.12pp, BCQ_E9.12pp, BCQ_E10.12pp,
                  BCQ_So2.12pp:BCQ_So5.12pp, BCQ_So7.12pp, BCQ_So10.12pp),
                ~ 5 -.))

setnames(x = df, 
         old = c("BCQ_S1.12pp", "BCQ_S2.12pp", "BCQ_S3.12pp","BCQ_S9.12pp",
                 "BCQ_E2.12pp", "BCQ_E3.12pp", "BCQ_E5.12pp", "BCQ_E6.12pp", "BCQ_E9.12pp", "BCQ_E10.12pp",
                 "BCQ_So2.12pp", "BCQ_So3.12pp", "BCQ_So4.12pp", "BCQ_So5.12pp", "BCQ_So7.12pp", "BCQ_So10.12pp"), 
         new = gsub(pattern = ".12pp", 
                    replacement = "_r.12pp", 
                    x = c("BCQ_S1.12pp", "BCQ_S2.12pp", "BCQ_S3.12pp","BCQ_S9.12pp",
                 "BCQ_E2.12pp", "BCQ_E3.12pp", "BCQ_E5.12pp", "BCQ_E6.12pp", "BCQ_E9.12pp", "BCQ_E10.12pp",
                 "BCQ_So2.12pp", "BCQ_So3.12pp", "BCQ_So4.12pp", "BCQ_So5.12pp", "BCQ_So7.12pp", "BCQ_So10.12pp")))
```

#### Calculate summary scores

```{r}
df <- df %>%  
  
  # Tell R that we want to take the mean across a row
  rowwise() %>%
  
  # Calculate total scores/subscales
  mutate(BCQ_structure.12pp = round(mean(c(c_across(BCQ_S1_r.12pp:BCQ_S6.12pp), 
                                          BCQ_E1.12pp, BCQ_E2_r.12pp, BCQ_E3_r.12pp, BCQ_E6_r.12pp, BCQ_E7.12pp, BCQ_E10_r.12pp, 
                                          BCQ_So1.12pp, BCQ_So2_r.12pp, BCQ_So4_r.12pp, BCQ_So9.12pp, BCQ_So10_r.12pp),
                                        na.rm = T), 3)) %>%
  mutate(BCQ_attune.12pp = round(mean(c(c_across(BCQ_S7.12pp:BCQ_S9_r.12pp), 
                                       BCQ_E4.12pp, BCQ_E5_r.12pp, BCQ_E8.12pp, BCQ_E9_r.12pp, 
                                       BCQ_So3_r.12pp, c_across(BCQ_So5_r.12pp:BCQ_So8.12pp), BCQ_So11.12pp),
                                        na.rm = T), 3)) %>%
  
  # Convert NaN to NA
  mutate(across(BCQ_structure.12pp:BCQ_attune.12pp, ~coalesce(., NA_real_))) %>%
  
  # Move the total score/subscales so they come immediately after the measures
  relocate(BCQ_structure.12pp, BCQ_attune.12pp, .after = BCQ_So11.12pp)
```

### Label

```{r}
df <- df %>% 
  # Create value and variable labels
  mutate(across(c(contains("BCQ") & !contains("_r") & !contains("structure") & !contains("attune")),
            ~ labelled(., 
                     c("Strongly agree" = 4, 
                       "Agree" = 3, 
                       "Disagree" = 2, 
                       "Strongly Disagree" = 1), 
                     label = "Baby-Care Questionnaire"))) %>%
  
  mutate(across(c(contains("BCQ") & contains("_r")),
            ~ labelled(., 
                     c("Strongly agree" = 1, 
                       "Agree" = 2, 
                       "Disagree" = 3, 
                       "Strongly Disagree" = 4), 
                     label = "Baby-Care Questionnaire (reverse-coded)"))) %>%
  mutate(BCQ_structure.12pp = labelled(BCQ_structure.12pp, label = "BCQ: Structure"), 
         BCQ_attune.12pp = labelled(BCQ_attune.12pp, label = "BCQ: Attunement"))
```

### Check and Print

:::: panel-tabset
#### Check

::: panel-tabset
##### Check Counts

```{r}
#| echo: false
# Direct Score
check_categorical(df, contains("BCQ") & !contains("_r") & !contains("structure") & !contains("attune")) %>% knitr::kable()
# Reverse Score
check_categorical(df, contains("BCQ") & contains("_r")) %>% knitr::kable()
```

##### Check Numbers

```{r}
#| echo: false
check_continuous(df, BCQ_structure.12pp:BCQ_attune.12pp) %>% knitr::kable()
```

##### Check Reliability

###### Structure Subscale

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, c(BCQ_S1_r.12pp:BCQ_S6.12pp, 
                                          BCQ_E1.12pp, BCQ_E2_r.12pp, BCQ_E3_r.12pp, BCQ_E6_r.12pp, BCQ_E7.12pp, BCQ_E10_r.12pp, 
                                          BCQ_So1.12pp, BCQ_So2_r.12pp, BCQ_So4_r.12pp, BCQ_So9.12pp, BCQ_So10_r.12pp)), na.rm = T)
```

###### Attunement Subscale

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, c(BCQ_S7.12pp:BCQ_S9_r.12pp, 
                                       BCQ_E4.12pp, BCQ_E5_r.12pp, BCQ_E8.12pp, BCQ_E9_r.12pp, 
                                       BCQ_So3_r.12pp, BCQ_So5_r.12pp:BCQ_So8.12pp, BCQ_So11.12pp)), na.rm = T)
```

##### Check Variable Labels

```{r}
#| echo: false
inspect_labels(df, contains("BCQ")) 
```
:::

#### Print

```{r}
#| echo: false
print_slice(df, contains("BCQ"))
```
::::
:::::

## BDI: Beck Depression Inventory

::::: panel-tabset
### Notes

-   Beck, 1996
-   21 items
    -   We removed item 9 for IRB purposes (suicidality)
-   0-3 Likert scale (different anchor labels for each question)
-   Sum score
    -   Higher score = more depressive symptoms
-   No subscales
-   No reverse scores

### Script

#### Recode item scores

```{r}
df <- df %>%
# Code Items 1-15, 17, 19-21
  mutate(across(c(BDI1.12pp:BDI15.12pp, BDI17.12pp, BDI19.12pp:BDI21.12pp), 
            ~ case_when(
              . == 1 ~ 0, 
              . == 2 ~ 1, 
              . == 3 ~ 2,
              . == 4 ~ 3, 
              .default = NA))) %>%
  
  # Code Items 16, 18
  mutate(across(c(BDI16.12pp, BDI18.12pp), 
            ~ case_when(
              . == 1 ~ 0, 
              . == 2 | . == 3 ~ 1, 
              . == 4 | . == 5 ~ 2, 
              . == 6 | . == 7 ~ 3, 
              .default = NA)))
```

#### Calculate summary scores

```{r}
df <- df %>% 
  
  # Tell R that we want to take the mean across a row
  rowwise() %>%
  
  # Tell R that scores are numeric
  mutate(across(c(BDI1.12pp:BDI21.12pp), as.numeric)) %>%
  
  # Calculate total score
  mutate(BDI_tot.12pp = sum(c_across(BDI1.12pp:BDI21.12pp))) %>%
  
  # Move the total score so they come immediately after the measures
  relocate(BDI_tot.12pp, .after = BDI21.12pp) 
```

### Label

```{r}
df <- df %>%
  mutate(across(contains("BDI"), ~labelled(., label = "Beck Depression Inventory"))) %>%
  
  mutate(BDI_tot.12pp = labelled(BDI_tot.12pp, label = "Beck Depression Inventory: Total")) 
```

### Check and Print

:::: panel-tabset
#### Check

::: panel-tabset
##### Check Counts

```{r}
#| echo: false
check_categorical(df, BDI1.12pp:BDI21.12pp) %>% select(-label) %>% arrange(value) %>% knitr::kable()
```

##### Check Numbers

```{r}
#| echo: false
check_continuous(df, BDI_tot.12pp) %>% knitr::kable()
```

##### Check Reliability

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, BDI1.12pp:BDI21.12pp), na.rm = T)
```

##### Check Variable Labels

```{r}
#| echo: false
inspect_labels(df, BDI1.12pp:BDI_tot.12pp)
```
:::

#### Print

```{r}
#| echo: false
print_slice(df, contains("BDI"))
```
::::
:::::

## COPE: Brief Cope

::::: panel-tabset
### Notes

-   Carver, 1997
-   28 items
-   1-4 Likert Scale
    -   1 = I don't do this at all
    -   4 = I do this all the time
-   Sum scores
    -   Higher scores = more behaviors related to the subscale
-   14 subscales:
    -   Self-Distraction (1 and 19)
    -   Active Coping (2 and 7)
    -   Denial (3 and 8)
    -   Substance Use (4 and 11)
    -   Using Emotional Support (5 and 15)
    -   Using Instrumental Support (10 and 23)
    -   Behavior Disengagement (6 and 16)
    -   Venting (9 and 21)
    -   Positive Reframing (12 and 17)
    -   Planning (14 and 25)
    -   Humor (18 and 28)
    -   Acceptance (20 and 24)
    -   Religion (22 and 27)
    -   Self-Blame (13 and 26)
-   No items are revere-scored

### Script

#### Calculate summary scores

```{r COPE-scales}
df <- df %>% 
  
  # Tell R that we want to take the mean across a row
  rowwise() %>%
  
  # Tell R that scores are numeric
  mutate(across(c(COPE1.12pp:COPE28.12pp), as.numeric)) %>%
  
  # Calculate total scores/subscales
  mutate(COPE_dist.12pp = sum(c(COPE1.12pp, COPE19.12pp)), 
         COPE_act.12pp = sum(c(COPE2.12pp, COPE7.12pp)),
         COPE_den.12pp = sum(c(COPE3.12pp, COPE8.12pp)),
         COPE_sub.12pp = sum(c(COPE4.12pp, COPE11.12pp)),
         COPE_emo.12pp = sum(c(COPE5.12pp, COPE15.12pp)),
         COPE_inst.12pp = sum(c(COPE10.12pp, COPE23.12pp)),
         COPE_diseng.12pp = sum(c(COPE6.12pp, COPE16.12pp)),
         COPE_vent.12pp = sum(c(COPE9.12pp, COPE21.12pp)),
         COPE_reframe.12pp = sum(c(COPE12.12pp, COPE17.12pp)),
         COPE_plan.12pp = sum(c(COPE14.12pp, COPE25.12pp)),
         COPE_hum.12pp = sum(c(COPE18.12pp, COPE28.12pp)),
         COPE_acc.12pp = sum(c(COPE20.12pp, COPE24.12pp)),
         COPE_rel.12pp = sum(c(COPE22.12pp, COPE27.12pp)),
         COPE_blame.12pp = sum(c(COPE13.12pp, COPE26.12pp))
         ) %>%
  
  # Move the total score/subscales so they come immediately after the measures
  relocate(c(COPE_dist.12pp:COPE_blame.12pp), .after = COPE28.12pp)
```

### Label

```{r}
df <- df %>%
  mutate(across(contains("COPE") & !contains("_"), 
            ~ labelled(., 
                       c("I don't do this at all" = 1, 
                         "I do this a little bit" = 2, 
                         "I do this a medium amount" = 3, 
                         "I do this a lot" = 4), 
                       label = "Brief Cope Scale"))) %>%
  mutate(across(COPE_dist.12pp, ~labelled(.x, label = "Cope: Self-Distraction")), 
         across(COPE_act.12pp, ~labelled(.x, label = "Brief Cope: Active Coping")),
         across(COPE_den.12pp, ~labelled(.x, label = "Brief Cope: Denial")),
         across(COPE_sub.12pp, ~labelled(.x, label = "Brief Cope: Substance Use")),
         across(COPE_emo.12pp, ~labelled(.x, label = "Brief Cope: Using Emotional Support")),
         across(COPE_inst.12pp, ~labelled(.x, label = "Brief Cope: Using Instrumental Support")),
         across(COPE_diseng.12pp, ~labelled(.x, label = "Brief Cope: Behavior Disengagement")),
         across(COPE_vent.12pp, ~labelled(.x, label = "Brief Cope: Venting")),
         across(COPE_reframe.12pp, ~labelled(.x, label = "Brief Cope: Positive Reframing")),
         across(COPE_plan.12pp, ~labelled(.x, label = "Brief Cope: Planning")),
         across(COPE_hum.12pp, ~labelled(.x, label = "Brief Cope: Humor")),
         across(COPE_acc.12pp, ~labelled(.x, label = "Brief Cope: Acceptance")),
         across(COPE_rel.12pp, ~labelled(.x, label = "Brief Cope: Religion")),
         across(COPE_blame.12pp, ~labelled(.x, label = "Brief Cope: Self-Blame")))
  
```

### Check and Print

:::: panel-tabset
#### Check

::: panel-tabset
##### Check Counts

```{r}
#| echo: false
check_categorical(df, contains("COPE") & !contains("_")) %>% knitr::kable()
```

##### Check Numbers

```{r}
#| echo: false
check_continuous(df, COPE_dist.12pp:COPE_blame.12pp) %>% knitr::kable()
```

##### Check Variable Labels

```{r}
#| echo: false
inspect_labels(df, contains("COPE")) 
```

##### Check Reliability

Not applicable: each scale only has 2 items
:::

#### Print

```{r}
#| echo: false
print_slice(df, contains("COPE"))
```
::::
:::::

## DAS: Dyadic Adjustment Scale

::::: panel-tabset
### Notes

-   Spanier, 1976
-   32 items
-   Variable Likert Scales:
    -   Items 1-22: 0-5 Likert Scale
        -   0 = Always disagree/Never
        -   5 = Always agree/All the time
    -   Items 23-24: 0-4 Likert Scale
        -   0 = Never/None of them
        -   4 = Every day/All of them
    -   Items 25-28: 0-5 Likert Scale
        -   0 = Never
        -   5 = More often
    -   Items 29-30: 0-1 Binary Scale
        -   0 = Yes
        -   1 = No
    -   Item 31: 0-6 Likert Scale
    -   Item 32: 0-5 Likert Scale
-   Sum score
    -   Higher scores = healthier relationships
-   4 subscales:
    -   Dyadic consensus: 1, 2, 3, 5, 7-15
    -   Dyadic satisfaction: 16-23, 31-32
    -   Dyadic cohesion: 24-28
    -   Affectional expression: 4, 6, 29-30
-   Items 16, 17, 20, 21, and 22 are reverse coded

### Script

#### Recode item scores

```{r}
df <- df %>%
# Recode Items 1-15
  mutate(across(c(DAS1.12pp:DAS15.12pp, DAS18.12pp, DAS19.12pp),
            ~case_when(
              . == 1 ~ 5, 
              . == 2 ~ 4, 
              . == 3 ~ 3, 
              . == 4 ~ 2, 
              . == 5 ~ 1, 
              . == 6 ~ 0, 
              .default = NA))) %>%
  
  # Recode Items 16, 17, 20, 21, 22
  mutate(across(c(DAS16.12pp, DAS17.12pp, 
                   DAS20.12pp, DAS21.12pp, DAS22.12pp),
            ~case_when(
              . == 1 ~ 0, 
              . == 2 ~ 1, 
              . == 3 ~ 2, 
              . == 4 ~ 3, 
              . == 5 ~ 4, 
              . == 6 ~ 5, 
              .default = NA))) %>%
  
  # Recode Items 23-24
  mutate(across(DAS23.12pp:DAS24.12pp,
            ~case_when(
              . == 1 ~ 4, 
              . == 2 ~ 3, 
              . == 3 ~ 2,
              . == 4 ~ 1, 
              . == 5 ~ 0, 
              .default = NA))) %>%
  
  # Recode Items 25-30
  mutate(across(DAS25.12pp:DAS30.12pp,
            ~case_when(
              . == 1 ~ 0, 
              . == 2 ~ 1, 
              . == 3 ~ 2, 
              . == 4 ~ 3, 
              . == 5 ~ 4, 
              . == 6 ~ 5, 
              .default = NA))) %>%
  
  # Recode Item 31
  mutate(across(DAS31.12pp,
            ~case_when(
              . == 1 ~ 0, 
              . == 2 ~ 1, 
              . == 3 ~ 2, 
              . == 4 ~ 3, 
              . == 5 ~ 4, 
              . == 6 ~ 5, 
              . == 7 ~ 6,
              .default = NA))) %>%
  
  # Recode Item 32
  mutate(across(DAS32.12pp,
            ~case_when(
              . == 1 ~ 5, 
              . == 2 ~ 4, 
              . == 3 ~ 3, 
              . == 4 ~ 2, 
              . == 5 ~ 1, 
              . == 6 ~ 0, 
              .default = NA)))
```

#### Rename reverse-scored items

```{r}
# Mark reversed scores with `_r`
setnames(x = df, 
                     old = c("DAS16.12pp", "DAS17.12pp", "DAS20.12pp", "DAS21.12pp", 
                             "DAS22.12pp"), 
                     new = gsub(pattern = ".12pp", 
                          replacement = "_r.12pp", 
                          x = c("DAS16.12pp", "DAS17.12pp", "DAS20.12pp", "DAS21.12pp", 
                             "DAS22.12pp")))
```

#### Calculate summary scores

```{r}
df <- df %>%
  
  # Tell R that scores are numeric
  mutate(across(DAS1.12pp:DAS32.12pp, as.numeric)) %>% 
  
  # Tell R that we want to take the mean across a row
  rowwise() %>%
  
  # Calculate total score and subscales 
  mutate(DAS_con.12pp = sum(c(c_across(DAS1.12pp:DAS3.12pp), DAS5.12pp, c_across(DAS7.12pp:DAS15.12pp)), na.rm = T),
         DAS_sat.12pp = sum(c(c_across(DAS16_r.12pp:DAS23.12pp), c_across(DAS31.12pp:DAS32.12pp)), na.rm = T),
         DAS_coh.12pp = sum(c_across(DAS24.12pp:DAS28.12pp), na.rm = T),
         DAS_aff.12pp = sum(c(DAS4.12pp, DAS6.12pp, c_across(DAS29.12pp:DAS30.12pp)), na.rm = T),
         DAS_tot.12pp = sum(c_across(DAS1.12pp:DAS32.12pp), na.rm = T)) %>%
  
  # Convert 0 to NA
  mutate(across(DAS_con.12pp:DAS_tot.12pp, ~na_if(., 0))) %>%
  
    # Move the total score and subscales so they come immediately after the measures
  relocate(c(DAS_con.12pp, DAS_sat.12pp, DAS_coh.12pp, DAS_aff.12pp, DAS_tot.12pp), .after = DAS32.12pp) 
```

### Label

```{r}
df <- df %>% 
  # Create value and variable labels
  mutate(across(DAS1.12pp:DAS32.12pp,
            ~ labelled(., label = "Dyadic Adjustment Scale"))) %>%
  mutate(DAS_con.12pp = labelled(DAS_con.12pp, label = "DAS: Dyadic Consensus"),
         DAS_sat.12pp = labelled(DAS_sat.12pp, label = "DAS: Dyadic Satisfaction"),
         DAS_coh.12pp = labelled(DAS_coh.12pp, label = "DAS: Dyadic Cohesion"),
         DAS_aff.12pp = labelled(DAS_aff.12pp, label = "DAS: Affectional Expression"),
         DAS_tot.12pp = labelled(DAS_tot.12pp, label = "Dyadic Adjustment Scale Total"))
```

### Check and Print

:::: panel-tabset
#### Check

::: panel-tabset
##### Check Counts

```{r}
#| echo: false
# Direct Score
check_categorical(df, contains("DAS") & !contains("_")) %>% select(-label) %>% arrange(value) %>% knitr::kable()
# Reverse Score
check_categorical(df, contains("DAS") & contains("_r")) %>% select(-label) %>% arrange(value) %>% knitr::kable()
```

##### Check Numbers

```{r}
#| echo: false
check_continuous(df, DAS_con.12pp:DAS_tot.12pp) %>% knitr::kable()
```

##### Check Reliability

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, DAS1.12pp:DAS32.12pp), na.rm = T)
```

##### Check Variable Labels

```{r}
#| echo: false
inspect_labels(df, contains("DAS")) 
```
:::

#### Print

```{r}
#| echo: false
print_slice(df, contains("DAS"))
```
::::
:::::

## ECR-R: Experiences in Close Relationships

::::: panel-tabset
### Notes

-   Fraley, Waller, and Brennan, 2000
-   36 items
-   1-7 Likert Scale
    -   1 = stronly disagree
    -   7 = strongly agree
-   Mean scores
    -   Higher score = higher anxiety/avoidance
-   2 subscales:
    -   Anxiety: 1-18
    -   Avoidance: 9-36
-   Reverse score: 9, 11, 20, 22, 26-31, 33-36

### Script

#### Revere item scores

```{r}
# Reverse Score Q's 9, 11, 20, 22, 26, 27, 28, 29, 30, 31, 33, 34, 35, and 36
df <- df %>%
  mutate(across(c(ECR9.12pp, ECR11.12pp, ECR20.12pp, ECR22.12pp,
                  ECR26.12pp:ECR31.12pp, 
                  ECR33.12pp:ECR36.12pp),
            ~ 8 - .))

# Mark reversed scores with `_r`
setnames(x = df, 
         old = c("ECR9.12pp", "ECR11.12pp", "ECR20.12pp", 
                 "ECR22.12pp", "ECR26.12pp", "ECR27.12pp", 
                 "ECR28.12pp", "ECR29.12pp", "ECR30.12pp", 
                 "ECR31.12pp", "ECR33.12pp", "ECR34.12pp", 
                 "ECR35.12pp", "ECR36.12pp"), 
         new = gsub(pattern = ".12pp", 
                    replacement = "_r.12pp", 
                    x = c("ECR9.12pp", "ECR11.12pp", "ECR20.12pp", 
                 "ECR22.12pp", "ECR26.12pp", "ECR27.12pp", 
                 "ECR28.12pp", "ECR29.12pp", "ECR30.12pp", 
                 "ECR31.12pp", "ECR33.12pp", "ECR34.12pp", 
                 "ECR35.12pp", "ECR36.12pp")))
```

#### Calculate summary scores

```{r ECR-R-scales}
df <- df %>% 
  
  # Tell R that we want to take the mean across a row
  rowwise() %>%
  
  # Tell R that scores are numeric
  mutate(across(ECR1.12pp:ECR36_r.12pp, as.numeric)) %>%
  
  # Calculate total scores/subscales
  mutate(ECR_anx.12pp = round(mean(c_across(ECR1.12pp:ECR18.12pp), na.rm = T), 3), 
         ECR_avoid.12pp = round(mean(c_across(ECR19.12pp:ECR36_r.12pp), na.rm = T), 3)) %>%
  
  # Clean up NAs  
 mutate(across(c(ECR_anx.12pp:ECR_avoid.12pp), ~coalesce(., NA_real_))) %>%
  
  # Move the total score/subscales so they come immediately after the measures
  relocate(c(ECR_anx.12pp, ECR_avoid.12pp), .after = ECR36_r.12pp)
```

### Label

```{r}
df <- df %>% 
  # Create value and variable labels
  mutate(across(contains("ECR") & !contains("_"),
            ~ labelled(., 
                     c("Strongly Disagree" = 1, 
                       "Disagree" = 2, 
                       "Slightly Disagree" = 3, 
                       "Neither Agree/Disagree" = 4, 
                       "Slightly Agree" = 5, 
                       "Agree" = 6, 
                       "Strongly Agree"= 7), 
                     label = "Experiences in Close Relationships"))) %>% 
  mutate(across(contains("ECR") & contains("_r"),
            ~ labelled(., 
                     c("Strongly Disagree" = 7, 
                       "Disagree" = 6, 
                       "Slightly Disagree" = 5, 
                       "Neither Agree/Disagree" = 4, 
                       "Slightly Agree" = 3, 
                       "Agree" = 2, 
                       "Strongly Agree"= 1), 
                     label = "Experiences in Close Relationships (reverse-scored)"))) %>% 
  mutate(ECR_anx.12pp = labelled(ECR_anx.12pp, label = "ECR: Attachment-Related Anxiety"), 
         ECR_avoid.12pp = labelled(ECR_avoid.12pp, label = "ECR: Attachment-Related Avoidance"))
```

### Check and Print

:::: panel-tabset
#### Check

::: panel-tabset
##### Check Counts

```{r}
#| echo: false
# Direct Score
check_categorical(df, contains("ECR") & !contains("_")) %>% knitr::kable()
# Reverse Score
check_categorical(df, contains("ECR") & contains("_r")) %>% knitr::kable()
```

##### Check Numbers

```{r}
#| echo: false
check_continuous(df, ECR_anx.12pp:ECR_avoid.12pp) %>% knitr::kable()
```

##### Check Reliability

###### Anxious Attachment

```{r}
#| echo: false

ltm::cronbach.alpha(data = select(df, ECR1.12pp:ECR18.12pp), na.rm = T)
```

###### Avoidant Attachment

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, ECR19.12pp:ECR36_r.12pp), na.rm = T)
```

##### Check Variable Labels

```{r}
#| echo: false
inspect_labels(df, contains("ECR"))
```
:::

#### Print

```{r}
#| echo: false
print_slice(df, contains("ECR"))
```
::::
:::::

## EPDS: Edinburgh Postnatal Depression Scale

::::: panel-tabset
### Notes

-   Cox et al., 1987
-   9 items (originally 10, but removed suicidality item)
-   0-3 Likert Scale (different anchor labels for question)
-   Sum score
    -   Higher scores = greater depressive symptoms
    -   Darby's syntax, it was a mean score, but online says it should
        be a sum score
-   No subscales
-   Reverse score: 3, 5, 6, 7, 8, 9
-   According to Darby's syntax, Question 2 was phrased incorrectly
    until Couple 10 and requires reverse scoring

### Script

#### Recode item scores

```{r}
df <- df %>%
  mutate(across(EPDS1.12pp:EPDS9.12pp,
            ~ case_when(
                     . == 1 ~ 0,
                     . == 2 ~ 1,
                     . == 3 ~ 2,
                     . == 4 ~ 3,
                     .default = NA))) 
```

#### Reverse item score

```{r}
df <- df %>%
  mutate(across(c(EPDS3.12pp, EPDS5.12pp:EPDS9.12pp),
            ~3-.)) %>%
  mutate(EPDS2.12pp = case_when(
    CoupleID < 10  ~ 3-EPDS3.12pp, 
    .default = EPDS2.12pp
  )) # fixing EPDS2 for couples 1-9

# Mark reversed scores with `_r`
setnames(x = df, 
         old = c("EPDS3.12pp", "EPDS5.12pp", "EPDS6.12pp", "EPDS7.12pp", "EPDS8.12pp", "EPDS9.12pp"), 
         new = gsub(pattern = ".12pp", 
                    replacement = "_r.12pp", 
                    x = c("EPDS3.12pp", "EPDS5.12pp", "EPDS6.12pp", "EPDS7.12pp", "EPDS8.12pp", "EPDS9.12pp")))
```

#### Calculate summary scores

```{r}
df <- df %>% 
  
  # Tell R that we want to take the mean across a row
  rowwise() %>%
  
  # Calculate total scores/subscales
  mutate(EPDS_tot.12pp = sum(c_across(EPDS1.12pp:EPDS9_r.12pp), na.rm = F))%>%
  
  # Move the total score/subscales so they come immediately after the measures
  relocate(EPDS_tot.12pp, .after = EPDS_tot.12pp)
```

### Label

```{r}
df <- df %>% 
  # Direct Score
  mutate(across(c(contains("EPDS") & !contains("_")), 
            ~ labelled(., label = "Edinburgh Postnatal Depression Scale"))) %>%
  #Reverse Score
  mutate(across(c(contains("EPDS") & contains("_r")), 
            ~ labelled(., label = "Edinburgh Postnatal Depression Scale (reverse-scored)"))) %>%
  # Total Score
  mutate(EPDS_tot.12pp = labelled(EPDS_tot.12pp, label = "EPDS: Total Score"))
```

### Check and Print

:::: panel-tabset
#### Check

::: panel-tabset
##### Check Counts

```{r}
#| echo: false
# Direct Score
check_categorical(df, contains("EPDS") & !contains("_")) %>% arrange(value) %>% select(-label) %>% knitr::kable()
# Reverse Score
check_categorical(df, contains("EPDS") & contains("_r"))%>% select(-label) %>% knitr::kable()
```

##### Check Numbers

```{r}
#| echo: false
check_continuous(df, EPDS_tot.12pp) %>% knitr::kable()
```

##### Check Reliability

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, EPDS1.12pp:EPDS9_r.12pp), na.rm = T)
```

##### Check Variable Labels

```{r}
#| echo: false
inspect_labels(df, contains("EPDS")) 
```
:::

#### Print

```{r}
#| echo: false
print_slice(df, contains("EPDS"))
```
::::
:::::

## IBQR: Infant Behavior Questionnaire—Revised

::::: panel-tabset
### Notes

-   Putman et al., 2014
-   37 items
-   1-7 Likert Scale
    -   1 = Never
    -   7 = Always
-   Mean score
    -   Higher scores = more frequent expression of temperament trait
-   3 Subscales:
    -   Surgency: 1, 2, 7, 8, 13, 14, 15, 20, 21, 26, 27, 36, 37
    -   Negative Affect: 3, 4, 9, 10, 16, 17, 22. 23, 28, 29, 32, 33
    -   Effortful control: 5, 6, 11R, 12, 18, 19, 24, 25, 30, 31, 34, 35
-   Reverse score: 11

### Script

#### Recode item scores

```{r}
df <- df %>%
  mutate(across(contains("IBQR"),
            ~ case_when(
                     . == 8 ~ NA,
                     .default = .))) 
```

#### Reverse score item 11

```{r}
df <- df %>%
  mutate(IBQR11_r.12pp = 8-IBQR11.12pp, 
         .keep = "unused", .after = IBQR10.12pp)
```

#### Calculate summary scores

```{r}
df <- df %>% 
  
  # Tell R that we want to take the mean across a row
  rowwise() %>%
  
  # Calculate total scores/subscales
  mutate(IBQR_surgency.12pp = round(mean(c(IBQR1.12pp, IBQR2.12pp, IBQR7.12pp, IBQR8.12pp, 
                                             IBQR13.12pp, IBQR14.12pp, IBQR15.12pp, 
                                             IBQR20.12pp, IBQR21.12pp, IBQR26.12pp, IBQR27.12pp, 
                                             IBQR36.12pp, IBQR37.12pp), 
                                    na.rm = T), 3),
         IBQR_negaffect.12pp = round(mean(c(IBQR3.12pp, IBQR4.12pp, IBQR9.12pp, 
                                              IBQR10.12pp, IBQR16.12pp, IBQR17.12pp, 
                                              IBQR22.12pp, IBQR23.12pp, IBQR28.12pp, IBQR29.12pp, 
                                              IBQR32.12pp, IBQR33.12pp), 
                                     na.rm = T), 3),
         IBQR_effcontrol.12pp = round(mean(c(IBQR5.12pp, IBQR6.12pp, 
                                               IBQR11_r.12pp, IBQR12.12pp, IBQR18.12pp, IBQR19.12pp, 
                                               IBQR24.12pp, IBQR25.12pp, 
                                               IBQR30.12pp, IBQR31.12pp, IBQR34.12pp, IBQR35.12pp), 
                                      na.rm = T), 3)) %>%
  
  # Convert NaN to NA
  mutate(across(IBQR_surgency.12pp:IBQR_effcontrol.12pp, ~coalesce(., NA_real_))) %>%
  
  # Move the total score/subscales so they come immediately after the measures
  relocate(IBQR_surgency.12pp:IBQR_effcontrol.12pp, .after = IBQR37.12pp)
```

### Label

```{r}
df <- df %>% 
  # Create value and variable labels
  mutate(across(contains("IBQR") & !contains("_"),
            ~ labelled(., 
                     c("Never" = 1, 
                       "Very rarely" = 2, 
                       "Less than half the time" = 3,
                       "About half the time" = 4, 
                       "More than half the time" = 5, 
                       "Almost always" = 6, 
                       "Always" = 7),
                     label = "Infant Behavior Questionnaire, Revised Very Short Form"))) %>%
  mutate(IBQR11_r.12pp = labelled(IBQR11_r.12pp, 
                                 c("Never" = 7, 
                                   "Very rarely" = 6, 
                                   "Less than half the time" = 5,
                                   "About half the time" = 4, 
                                   "More than half the time" = 3, 
                                   "Almost always" = 2, 
                                   "Always" = 1),
                                 label = "Infant Behavior Questionnaire, Revised Very Short Form (reverse-scored)" )) %>%
  mutate(IBQR_surgency.12pp = labelled(IBQR_surgency.12pp, label = "IBQ-R: Surgency Subscale"), 
         IBQR_negaffect.12pp = labelled(IBQR_negaffect.12pp, label = "IBQ-R: Negative Affect Subscale"), 
         IBQR_effcontrol.12pp = labelled(IBQR_effcontrol.12pp, label = "IBQ-R: Effortful Control"))
```

### Check and Print

:::: panel-tabset
#### Check

::: panel-tabset
##### Check Counts

```{r}
#| echo: false
# Direct Score
check_categorical(df, contains("IBQR") & !contains("_")) %>% knitr::kable()
# Reverse Score
check_categorical(df, IBQR11_r.12pp) %>% knitr::kable()
```

##### Check Numbers

```{r}
#| echo: false
check_continuous(df, IBQR_surgency.12pp:IBQR_effcontrol.12pp) %>% knitr::kable()
```

##### Check Reliability

###### Surgency

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, IBQR1.12pp, IBQR2.12pp, IBQR7.12pp, IBQR8.12pp, 
                                  IBQR13.12pp, IBQR14.12pp, IBQR15.12pp, 
                                  IBQR20.12pp, IBQR21.12pp, IBQR26.12pp, IBQR27.12pp, 
                                  IBQR36.12pp, IBQR37.12pp), na.rm = T)
```

###### Negative Affect

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, IBQR3.12pp, IBQR4.12pp, IBQR9.12pp, 
                                              IBQR10.12pp, IBQR16.12pp, IBQR17.12pp, 
                                              IBQR22.12pp, IBQR23.12pp, IBQR28.12pp, IBQR29.12pp, 
                                              IBQR32.12pp, IBQR33.12pp), na.rm = T)
```

###### Effortful Control

```{r}
#| echo: false 
ltm::cronbach.alpha(data = select(df, IBQR5.12pp, IBQR6.12pp, 
                                  IBQR11_r.12pp, IBQR12.12pp, IBQR18.12pp, IBQR19.12pp, 
                                  IBQR24.12pp, IBQR25.12pp, 
                                  IBQR30.12pp, IBQR31.12pp, IBQR34.12pp, IBQR35.12pp), na.rm = T)
```

##### Check Variable Labels

```{r}
#| echo: false
inspect_labels(df, contains("IBQR")) 
```
:::

#### Print

```{r}
#| echo: false
print_slice(df, contains("IBQR"))
```
::::
:::::

## IMS: Investment Model Scale

:::::: panel-tabset
### Notes

-   Rusbult et al., 1998
-   37 items total, 22 included in scoring
    -   15 are items in "facet scales"
    -   22 are items in "global scales"
        -   5 in Satisfaction subscale
        -   5 in Alternatives subscale
        -   5 in Investment subscale
        -   7 in Committment subscales
-   0-8 Likert scale
    -   0 = Do not agree at all
    -   8 = Agree completely
    -   Facet scales are on a 1-4 Likert scale
-   Mean score
    -   Higher score = stronger committment to maintaining the
        relationship
-   4 subscales:
    -   Satisfaction: 1-5
    -   Alternatives: 6-10
    -   Investment: 11-15
    -   Commitment: 16-22
-   Reverse score items: 6-10 (Alternatives), 18 & 19 (Commitment)
-   Other notes: "Facet items prepare participants to answer global
    items by activating thoughts about each construct and concretely
    illustrating each construct. Thus, facet items are utilized to
    enhance the comprehensibility of global items, thereby increasing
    their reliability and validity-the facet items are included solely
    to obtain good global measures of each Investment Model construct.
    The global measures of each construct are the measures that are
    employed in formal tests of Investment Model hypotheses.

### Script

#### Relocate facet items

```{r}
df <- df %>%
  relocate(contains("IMS") & contains("facet"), .after = IMS22.12pp)
```

#### Recode item scores

```{r}
df <- df %>%
  
  # Global Items
  mutate(across(IMS1.12pp:IMS22.12pp, 
            ~ case_when(
              . == 1 ~ 0, 
              . == 2 ~ 1, 
              . == 3 ~ 2,
              . == 4 ~ 3,
              . == 5 ~ 4, 
              . == 6 ~ 5, 
              . == 7 ~ 6, 
              . == 8 ~ 7, 
              . == 9 ~ 8,
              .default = NA))) %>%
  
  # Facet items
  mutate(across(contains("IMS") & contains("facet"), 
                ~ case_when(
                  . == -99 ~ NA, 
                  .default = .)))
```

#### Reverse item scores

```{r}
# Reverse Score Q's 6-10, 18 & 19
df <- df %>%
  mutate(across(c(IMS6.12pp:IMS10.12pp,IMS18.12pp, IMS19.12pp),
            ~ 8 - .))

# Mark reversed scores with `_r`
setnames(x = df, 
         old = c("IMS6.12pp", "IMS7.12pp", "IMS8.12pp", 
                 "IMS9.12pp", "IMS10.12pp",
                 "IMS18.12pp", "IMS19.12pp"), 
         new = gsub(pattern = ".12pp", 
                    replacement = "_r.12pp", 
                    x = c("IMS6.12pp", "IMS7.12pp", "IMS8.12pp", 
                          "IMS9.12pp", "IMS10.12pp",
                          "IMS18.12pp", "IMS19.12pp")))
```

#### Calculate summary scores

```{r}
df <- df %>%  
  
  # Tell R that we want to take the mean across a row
  rowwise() %>%
  
  # Calculate total scores/subscales
  mutate(IMS_satisfaction.12pp = round(mean(c_across(IMS1.12pp:IMS5.12pp), na.rm = T), 3)) %>%
  mutate(IMS_alternatives.12pp = round(mean(c_across(IMS6_r.12pp:IMS10_r.12pp), na.rm = T), 3)) %>%
  mutate(IMS_investment.12pp = round(mean(c_across(IMS11.12pp:IMS15.12pp), na.rm = T), 3)) %>%
  mutate(IMS_commitment.12pp = round(mean(c_across(IMS16.12pp:IMS22.12pp), na.rm = T), 3)) %>%
  
  # Convert NaN to NA
  mutate(across(IMS_satisfaction.12pp:IMS_commitment.12pp, ~coalesce(., NA_real_))) %>%
  
  # Move the total score/subscales so they come immediately after the measures
  relocate(IMS_satisfaction.12pp:IMS_commitment.12pp, .after = IMS22.12pp)
```

### Label

```{r}
df <- df %>%
  
  # Direct Global Items 
  mutate(across(contains("IMS") & !contains("_") & !contains("facet"),
                ~ labelled(., 
                           labels = c("Do not agree at all" = 0,
                                      "Mostly disagree" = 1,
                                      "Disagree" = 2,
                                      "Slightly disagree" = 3,
                                      "Agree somewhat" = 4,
                                      "Slightly agree" = 5,
                                      "Agree" = 6,
                                      "Mostly agree" = 7,
                                      "Agree completely" = 8), 
                           label = "Investment Model Scale"))) %>%
  
  # Reverse Global Items
  mutate(across(contains("IMS") & contains("_r"),
                ~ labelled(., 
                           labels = c("Agree completely" = 0,
                                      "Mostly agree" = 1,
                                      "Agree" = 2,
                                      "Slightly agree" = 3,
                                      "Agree somewhat" = 4,
                                      "Slightly disagree" = 5,
                                      "Disagree" = 6,
                                      "Mostly disagree" = 7,
                                      "Do not agree at all" = 8), 
                           label = "Investment Model Scale (reverse-scored)"))) %>%
  
  # Facet Items
  mutate(across(contains("IMS") & contains("facet"), 
                ~ labelled(., 
                           labels = c("Don't agree at all" = 1, 
                                      "Agree slightly" = 2, 
                                      "Agree moderately" = 3, 
                                      "Agree completely" = 4), 
                           label = "Investment Model Scale (factor item, not included in mean scores)"))) %>%
  
  # Subscales
  mutate(IMS_satisfaction.12pp = labelled(IMS_satisfaction.12pp, label = "IMS: Satisfaction Level"), 
         IMS_alternatives.12pp = labelled(IMS_alternatives.12pp, label = "IMS: Quality of Alternatives"), 
         IMS_investment.12pp = labelled(IMS_investment.12pp, label = "IMS: Investment Size"), 
         IMS_commitment.12pp = labelled(IMS_commitment.12pp, label = "IMS: Commitment Level"))
```

### Check and Print

::::: panel-tabset
#### Check

::: panel-tabset
##### Check Counts

```{r}
#| echo: false
# Direct Score
check_categorical(df, contains("IMS") & !contains("_")) %>% knitr::kable()
# Reverse Score
check_categorical(df, contains("IMS") & contains("_r")) %>% knitr::kable()
# Facet Scores
check_categorical(df, contains("IMS") & contains("facet")) %>% arrange(value) %>% knitr::kable()

```

##### Check Numbers

```{r}
#| echo: false
check_continuous(df, IMS_satisfaction.12pp:IMS_commitment.12pp) %>% knitr::kable()
```

##### Check Reliability

###### Satisfaction

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, IMS1.12pp:IMS5.12pp), na.rm = T)
```

###### Alternatives

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, IMS6_r.12pp:IMS10_r.12pp), na.rm = T)
```

###### Investment

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, IMS11.12pp:IMS15.12pp), na.rm = T)
```

###### Commitment

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, IMS16.12pp:IMS22.12pp), na.rm = T)
```


##### Check Variable Labels

```{r}
#| echo: false
inspect_labels(df, contains("IMS")) 
```
:::

#### Print

::: panel-tabset
##### Satisfaction

```{r}
#| echo: false
print_slice(df, IMS1.12pp:IMS5.12pp, IMS_satisfaction.12pp)
```

##### Alternatives

```{r}
#| echo: false
print_slice(df, IMS6_r.12pp:IMS10_r.12pp, IMS_alternatives.12pp)
```

##### Invesment

```{r}
#| echo: false
print_slice(df, IMS11.12pp:IMS15.12pp, IMS_investment.12pp)
```

##### Commitment

```{r}
#| echo: false
print_slice(df, IMS16.12pp:IMS22.12pp, IMS_commitment.12pp)
```
:::
:::::
::::::

## LAPR: Life Attitudes Profile—Revised

::::: panel-tabset
### Notes

-   Erci, 2008 (but adapted for HATCH)
-   16 items (out of 48 total)
-   1-7 Likert
    -   1 = Strongly disagree
    -   7 = Strongly agree
-   Sum score
    -   Higher scores = greater sense of meaning
-   2 dimensions (out of 6 in original scale):
    -   Purpose: 1, 2, 5, 18, 26, 31, 37, 48
    -   Coherence: 7, 12, 27. 29. 35, 38, 46
-   1 composite score (out of 2 in original scale):
    -   Personal Meaning Index

### Script

#### Recode item scores

```{r}
# Reverse Score All Items
df <- df %>%
  mutate(across(c(LAPR1.12pp:LAPR48.12pp),
            ~ 8-.))
```

#### Calculate summary scores

```{r LAP-R-scales}
df <- df %>% 
  
  # Tell R that we want to take the mean across a row
  rowwise() %>%
  
  # Tell R that scores are numeric
  mutate(across(LAPR1.12pp:LAPR48.12pp, as.numeric)) %>% 
  
  # Calculate total scores/subscales
  mutate(LAPR_pur.12pp = sum(c(LAPR1.12pp, LAPR2.12pp, LAPR5.12pp, LAPR18.12pp, 
                              LAPR26.12pp, LAPR31.12pp, LAPR37.12pp, LAPR48.12pp)),
         LAPR_coh.12pp = sum(c(LAPR7.12pp, LAPR12.12pp, LAPR16.12pp, LAPR27.12pp, 
                             LAPR29.12pp, LAPR35.12pp, LAPR38.12pp, LAPR46.12pp)),
         LAPR_pmi.12pp = sum(c_across(LAPR1.12pp:LAPR48.12pp)))%>%
         
  
  # Move the total score/subscales so they come immediately after the measures
  relocate(c(LAPR_pur.12pp, LAPR_coh.12pp, LAPR_pmi.12pp), .after = LAPR48.12pp)
```

### Label

```{r}
df <- df %>% 
  # Create value and variable labels
  mutate(across(contains("LAPR") & !contains("_"),
            ~ labelled(., 
                     c("Strongly Disagree" = 1, 
                       "Disagree" = 2, 
                       "Moderately Disagree" = 3, 
                       "Undecided" = 4, 
                       "Moderately Agree" = 5, 
                       "Agree" = 6,
                       "Strongly Agree" = 7), 
                     label = "Life Attitudes Profile, Revised"))) %>%
  mutate(LAPR_pur.12pp = labelled(LAPR_pur.12pp, label = "LAP-R: Purpose"),
         LAPR_coh.12pp = labelled(LAPR_coh.12pp, label = "LAP-R: Coherenece"), 
         LAPR_pmi.12pp = labelled(LAPR_pmi.12pp, label = "LAP-R: Personal Meaning Index"))
```

### Check and Print

:::: panel-tabset
#### Check

::: panel-tabset
##### Check Counts

```{r}
#| echo: false
check_categorical(df, contains("LAPR") & !contains("_")) %>% knitr::kable()
```

##### Check Numbers

```{r}
#| echo: false
check_continuous(df, LAPR_pur.12pp:LAPR_pmi.12pp) %>% knitr::kable()
```

##### Check Reliability

###### Purpose

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, LAPR1.12pp, LAPR2.12pp, LAPR5.12pp, LAPR18.12pp, 
                              LAPR26.12pp, LAPR31.12pp, LAPR37.12pp, LAPR48.12pp), na.rm = T)
```

###### Coherence

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, LAPR7.12pp, LAPR12.12pp, LAPR16.12pp, LAPR27.12pp, 
                             LAPR29.12pp, LAPR35.12pp, LAPR38.12pp, LAPR46.12pp), na.rm = T)
```

###### Personal Meaning Index

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, contains("LAPR") & !contains("_")), na.rm = T)
```

##### Check Variable Labels

```{r}
#| echo: false
inspect_labels(df, contains("LAPR")) 
```
:::

#### Print

```{r}
#| echo: false
print_slice(df, contains("LAPR"))
```
::::
:::::

## MAI: Maternal Attachment Inventory

::::: panel-tabset
### Notes

-   Müller, 1994
-   26 items
-   1-4 Likert Scale
    -   1 = Almost never
    -   4 = Almost always
-   Sum score
    -   Higher scores = more secure/positive attachment
-   No subscales
-   No reverse scores

### Script

#### Recode item scores

```{r}
df <- df %>%
  mutate(across(MAI1.12pp:MAI26.12pp,
            ~ case_when(
                     . == 1 ~ 4,
                     . == 2 ~ 3,
                     . == 3 ~ 2,
                     . == 4 ~ 1,
                     .default = NA)))
```

#### Caculate summary scores

```{r}
df <- df %>% 
  
  # Tell R that we want to take the mean across a row
  rowwise() %>%
  
  # Calculate total scores/subscales
  mutate(MAI_tot.12pp = sum(c_across(MAI1.12pp:MAI26.12pp), na.rm = F)) %>%
  
  # Move the total score/subscales so they come immediately after the measures
  relocate(MAI_tot.12pp, .after = MAI26.12pp)
```

### Label

```{r}
df <- df %>% 
  # Create value and variable labels
  mutate(across(contains("MAI") & !contains("_"),
            ~ labelled(., 
                     c("Almost always" = 4, 
                       "Often" = 3, 
                       "Sometimes" = 2, 
                       "Almost never" = 1), 
                     label = "Maternal Attachment Inventory"))) %>%
  mutate(MAI_tot.12pp = labelled(MAI_tot.12pp, label = "MAI: Total Score"))
```

### Check and Print

:::: panel-tabset
#### Check

::: panel-tabset
##### Check Counts

```{r}
#| echo: false
check_categorical(df, contains("MAI") & !contains("_")) %>% arrange(value) %>% knitr::kable()
```

##### Check Numbers

```{r}
#| echo: false
check_continuous(df, MAI_tot.12pp) %>% knitr::kable()
```

##### Check Reliability

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, MAI1.12pp:MAI26.12pp), na.rm = T)
```

##### Check Variable Labels

```{r}
#| echo: false
inspect_labels(df, contains("MAI")) 
```
:::

#### Print

```{r}
#| echo: false
print_slice(filter(df, Parent == "mom"), contains("MAI"))
```
::::
:::::

## MAT: Marital Adjustment Test

::::: panel-tabset
### Notes

-   Locke & Wallace, 1959
-   15 items
-   Variable Likert Scales:
    -   Item 1: 7-point Likert scale (0-35)
    -   Items 2-9: 0-5 Likert scale (varying numbers) - Lowest = Always
        disagree - Highest = Always agree
    -   Item 10: 3-point Likert scale (0-10)
    -   Item 11: 4-point Likert scale (0-10)
    -   Item 12: 2-10 points depending on agreement
    -   Item 13: 4-point Likert scale (0-15)
    -   Item 14: 3-point Likert scale (0-15)
    -   Item 15: 4-point Likert scale (0-10)
-   Sum score
    -   Higher scores = greater satisfaction
-   No subscales
-   No reverse scores

### Script

#### Recode item scores

```{r}
df <- df %>%

  mutate(MAT1.12pp = case_when(
                        MAT1.12pp == 1 ~ 0,
                        MAT1.12pp == 2 ~ 2,
                        MAT1.12pp == 3 ~ 7,
                        MAT1.12pp == 4 ~ 15,
                        MAT1.12pp == 5 ~ 20,
                        MAT1.12pp == 6 ~ 25, 
                        MAT1.12pp == 7 ~ 35, 
                        .default = NA)) %>%

  mutate(across(c(MAT2.12pp, MAT3.12pp, MAT5.12pp,
                   MAT7.12pp:MAT9.12pp),
            ~ case_when( 
                        . == 1 ~ 5,
                        . == 2 ~ 4, 
                        . == 3 ~ 3,
                        . == 4 ~ 2,
                        . == 5 ~ 1,
                        . == 6 ~ 0, 
                        .default = NA))) %>%
 
  mutate(MAT4.12pp = case_when( 
                        MAT4.12pp == 1 ~ 8,
                        MAT4.12pp == 2 ~ 6, 
                        MAT4.12pp == 3 ~ 4,
                        MAT4.12pp == 4 ~ 2,
                        MAT4.12pp == 5 ~ 1,
                        MAT4.12pp == 6 ~ 0, 
                        .default = NA)) %>%
  
  mutate(MAT6.12pp = case_when( 
                        MAT6.12pp == 1 ~ 15,
                        MAT6.12pp == 2 ~ 12, 
                        MAT6.12pp == 3 ~ 9,
                        MAT6.12pp == 4 ~ 4,
                        MAT6.12pp == 5 ~ 1,
                        MAT6.12pp == 6 ~ 0, 
                        .default = NA)) %>%
  
  mutate(MAT10.12pp = case_when(
                        MAT10.12pp == 1 ~ 0,
                        MAT10.12pp == 2 ~ 2, 
                        MAT10.12pp == 3 ~ 10, 
                        .default = NA)) %>%
 
   mutate(MAT11.12pp = case_when(
                        MAT11.12pp == 1 ~ 10,
                        MAT11.12pp == 2 ~ 8, 
                        MAT11.12pp == 3 ~ 3,
                        MAT11.12pp == 4 ~ 0, 
                        .default = NA)) %>%

    mutate(MAT12.12pp = case_when(
                      MAT12a.12pp != MAT12b.12pp ~ 2, 
                      MAT12a.12pp == 1 & MAT12b.12pp == 1 ~ 3, 
                      MAT12a.12pp == 2 & MAT12b.12pp == 2 ~ 10, 
                      .default = NA),
         .after = MAT11.12pp, .keep = "unused") %>%
  
  mutate(MAT13.12pp = case_when(
                        MAT13.12pp == 1 ~ 0,
                        MAT13.12pp == 2 ~ 3, 
                        MAT13.12pp == 3 ~ 8,
                        MAT13.12pp == 4 ~ 15, 
                        .default = NA)) %>%
  
  mutate(MAT14.12pp = case_when(
                        MAT14.12pp == 1 ~ 15,
                        MAT14.12pp == 2 ~ 0, 
                        MAT14.12pp == 3 ~ 1, 
                        .default = NA)) %>%
  
  mutate(MAT15.12pp = case_when(
                        MAT15.12pp == 1 ~ 0,
                        MAT15.12pp == 2 ~ 2, 
                        MAT15.12pp == 3 ~ 10,
                        MAT15.12pp == 4 ~ 10, 
                        .default = NA)) 

  
```

#### Calculate Sum Score

```{r MAT-scales}
df <- df %>% 
  
  # Tell R that we want to take the mean across a row
  rowwise() %>%
  
  # Tell R that scores are numeric
  mutate(across(MAT1.12pp:MAT15.12pp, as.numeric)) %>%
  
  # Calculate total scores
  mutate(MAT_tot.12pp = sum(c_across(MAT1.12pp:MAT15.12pp))) %>%
  
  # Move the total score so they come immediately after the measures
  relocate(MAT_tot.12pp, .after = MAT15.12pp) 
```

### Label

```{r}
df <- df %>% 
  # Create value and variable labels
  mutate(across(MAT1.12pp:MAT15.12pp,
            ~ labelled(., 
                     label = "Marital Adjustment Test"))) %>%
  mutate(MAT_tot.12pp = labelled(MAT_tot.12pp, label = "MAT: Total Score"))
```

### Check and Print

:::: panel-tabset
#### Check

::: panel-tabset
##### Check Numbers

```{r}
#| echo: false
check_continuous(df, MAT_tot.12pp) %>% knitr::kable()
```

##### Check Reliability

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, MAT1.12pp:MAT15.12pp), na.rm = T)
```

##### Check Variable Labels

```{r}
#| echo: false
inspect_labels(df, contains("MAT"))
```
:::

#### Print

```{r}
#| echo: false
print_slice(df, contains("MAT"))
```
::::
:::::

## MOS: Medical Outcomes Study Social Support Survey

::::: panel-tabset
### Notes

-   Sherborne & Stewart, 1991
-   19 items
-   1-5 Likert scale
    -   1 = None of the time
    -   5 = All of the time
-   Mean score
    -   Higher score = higher levels of social support
-   4 Subscales:
    -   Emotional/ informational social support: 1-8
    -   Tangible social support: 9-12
    -   Positive interaction social support: 13-15
    -   Affectionate social support: 16-18
-   Revere score: None

### Script

#### Calculate summary scores

```{r}
df <- df %>%
  
  # Then tell R that we want to take the mean across a row
  rowwise() %>%
  
  # Tell R scores are numeric
  mutate(across(MOS1.12pp:MOS19.12pp, as.numeric)) %>% 
  
  # Calculate the summary scores 
  mutate(MOS_emo.12pp = round(mean(c_across(MOS1.12pp:MOS8.12pp), na.rm = T), 2),
         MOS_tang.12pp = round(mean(c_across(MOS9.12pp:MOS12.12pp), na.rm = T),2),
         MOS_aff.12pp = round(mean(c_across(MOS13.12pp:MOS15.12pp), na.rm = T),2),
         MOS_soc.12pp = round(mean(c_across(MOS16.12pp:MOS18.12pp), na.rm = T),2),
         MOS_tot.12pp = round(mean(c_across(MOS1.12pp:MOS19.12pp), na.rm = T),2)) %>%
  
  # Finally, move the summary scores so that they come immediately after the measures
  relocate(c(MOS_emo.12pp:MOS_tot.12pp), .after = MOS19.12pp) %>%

 #Clean up NaN
  mutate(across(c(MOS_emo.12pp:MOS_tot.12pp), ~coalesce(., NA_real_)))
```

### Label

```{r}
df <- df %>% 
  # Create value and variable labels
  mutate(across(MOS1.12pp:MOS19.12pp,
            ~ labelled(., 
                     c("None of the time" = 1, 
                       "A little of the time" = 2, 
                       "Some of the time" = 3, 
                       "Most of the time" = 4, 
                       "All of the time" = 5), 
                     label = "MOS Social Support"))) %>%
  mutate(MOS_emo.12pp = labelled(MOS_emo.12pp, label = "MOS: Emotional/Informational Social Support"),
         MOS_tang.12pp = labelled(MOS_tang.12pp, label = "MOS: Tangible Social Support"),
         MOS_aff.12pp = labelled(MOS_aff.12pp, label = "MOS: Positive Interaction Social Support"),
         MOS_soc.12pp = labelled(MOS_soc.12pp, label = "MOS: Affectionate Social Support"),
         MOS_tot.12pp = labelled(MOS_tot.12pp, label = "MOS: Total Social Support"))
```

### Check and Print

:::: panel-tabset
#### Check

::: panel-tabset
##### Check Counts

```{r}
#| echo: false
check_categorical(df, contains("MOS") & !contains("_")) %>% arrange(value) %>% knitr::kable()
```

##### Check Numbers

```{r}
#| echo: false
check_continuous(df, MOS_emo.12pp:MOS_tot.12pp) %>% knitr::kable()
```

##### Check Reliability

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, MOS1.12pp:MOS19.12pp), na.rm = T)
```

##### Check Variable Labels

```{r}
#| echo: false
inspect_labels(df, contains("MOS")) 
```
:::

#### Print

```{r}
#| echo: false
print_slice(df, contains("MOS")) 
```
::::
:::::

## PAT: Parental Attribution Test

::::: panel-tabset
### Notes

-   Bugental, 2011
-   18 items
-   1-7 Likert scale
    -   1 = Not at all important
    -   7 = Very important
-   Mean scores
    -   Higher ACF scores = parent tends to blame themselves more
    -   Higher CCF scores = parent tends to blame the child more
    -   Higher US scores = parent tends to blame
        uncontrollable/situational factors more
    -   Higher PCF scores = parent tends to blame themselves more than
        the child
-   3 subscales
    -   Adult Controlled Factors (ACF): 2d, 2i, 2k, 2m, 2u, 2z
    -   Child Controlled Factors (CCF): 2b, 2c, 2f, 2j, 2q, 2t
    -   Uncontrollable/Situational (US): 1a-1f
    -   Parent Centered Focus (PCF): ACF - CCF
-   Reverse code: none
    -   The scoring instructions say to reverse score these items: 2c,
        2f, 2m, 2q, 2u, 2z
    -   However, when you reverse score them, the cronbach's alpha
        become negative. When you don't reverse them, they are \>.8
    -   My conclusion is that the items the scoring instructions use are
        worded differently than the items we have
-   Other notes:
    -   Authors "have never found [US] scale to be predictive of
        parenting practices and advise against its use"
    -   The item numbers (1a-1f and 2a-2l) on our item list do not
        correspond to the author scoring information
        -   Doesn't matter for US scale, where all 6 items are from #1
            and are direct coded
        -   Fixed in `Rename` file based on SPSS syntax and reading
            through items

### Script

#### Recode item scores

```{r}
df <- df %>%
  
  # Remove `-99`
  mutate(across(PAT1a.12pp:PAT2z.12pp, ~na_if(.x, -99)))
```

#### Calculate summary scores

```{r}
df <- df %>%  
  
  # Tell R that we want to take the mean across a row
  rowwise() %>%
  
  # Calculate total scores/subscales
  mutate(PAT_ACF.12pp = round(mean(c(PAT2d.12pp, PAT2i.12pp, PAT2k.12pp, PAT2m.12pp, PAT2u.12pp, PAT2z.12pp),
                                        na.rm = T), 3)) %>%
  mutate(PAT_CCF.12pp = round(mean(c(PAT2b.12pp, PAT2c.12pp, PAT2f.12pp, PAT2j.12pp, PAT2q.12pp, PAT2t.12pp),
                                        na.rm = T), 3)) %>%
  mutate(PAT_US.12pp = round(mean(c_across(PAT1a.12pp:PAT1f.12pp),
                                        na.rm = T), 3)) %>%
  mutate(PAT_PCF.12pp = PAT_ACF.12pp-PAT_CCF.12pp) %>%
  
  # Convert NaN to NA
  mutate(across(PAT_ACF.12pp:PAT_PCF.12pp, ~coalesce(., NA_real_))) %>%
  
  # Move the total score/subscales so they come immediately after the measures
  relocate(PAT_ACF.12pp:PAT_PCF.12pp, .after = PAT2z.12pp)
```

### Label

```{r}
df <- df %>%
  
  # Items 
  mutate(across(contains("PAT") & !contains("_"),
                ~ labelled(., 
                           labels = c("Not at all important" = 1,
                                      "Not very important" = 2,
                                      "Fairly unimportant" = 3,
                                      "Neither important nor unimportant" = 4,
                                      "Somewhat important" = 5,
                                      "Quite important" = 6,
                                      "Very important" = 7), 
                           label = "Parental Attribution Test"))) %>%
  
  
  # Subscales
  mutate(PAT_ACF.12pp = labelled(PAT_ACF.12pp, label = "PAT: Adult Controlled Factors"), 
         PAT_CCF.12pp = labelled(PAT_CCF.12pp, label = "PAT: Child Controlled Factors"), 
         PAT_US.12pp = labelled(PAT_US.12pp, label = "PAT: Uncontrollable/Situational"), 
         PAT_PCF.12pp = labelled(PAT_PCF.12pp, label = "PAT: Parent Centered Focus"))
```

### Check and Print

:::: panel-tabset
#### Check

::: panel-tabset
##### Check Counts

```{r}
#| echo: false
# Direct Score
check_categorical(df, contains("PAT") & !contains("_")) %>% arrange(value) %>% knitr::kable()
```

##### Check Numbers

```{r}
#| echo: false
check_continuous(df, PAT_ACF.12pp:PAT_PCF.12pp) %>% knitr::kable()
```

##### Check Reliability

###### ACF

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, PAT2d.12pp, PAT2i.12pp, PAT2k.12pp, PAT2m.12pp, PAT2u.12pp, PAT2z.12pp), na.rm = T)
```

###### CCF

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, PAT2b.12pp, PAT2c.12pp, PAT2f.12pp, PAT2j.12pp, PAT2q.12pp, PAT2t.12pp), na.rm = T)
```

###### US

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, PAT1a.12pp:PAT1f.12pp), na.rm = T)
```

##### Check Variable Labels

```{r}
#| echo: false
inspect_labels(df, contains("PAT")) 
```
:::

#### Print

###### ACF

```{r}
#| echo: false
print_slice(df, PAT2d.12pp, PAT2i.12pp, PAT2k.12pp, PAT2m.12pp, PAT2u.12pp, PAT2z.12pp, PAT_ACF.12pp)
```

###### CCF

```{r}
#| echo: false
print_slice(df, PAT2b.12pp, PAT2c.12pp, PAT2f.12pp, PAT2j.12pp, PAT2q.12pp, PAT2t.12pp, PAT_CCF.12pp)
```

###### US

```{r}
#| echo: false
print_slice(df, PAT1a.12pp:PAT1f.12pp, PAT_US.12pp)
```

###### PCF

```{r}
#| echo: false
print_slice(df, PAT_ACF.12pp, PAT_CCF.12pp, PAT_PCF.12pp)
```
::::
:::::

## PBQ: Postpartum Bonding Questionnaire

::::: panel-tabset
### Notes

-   Brockington et al., 2001
-   25 items
-   0-5 Likert Scale
    -   0 = Always/Never
    -   5 = Never/Always
-   Sum score
    -   Higher scores = more impaired bonding Darby's SPSS script, it's
        a mean. but scoring instructions say to take a sum
-   Subscales:
    -   Impaired bonding: 1, 2, 6, 7, 8, 9, 10, 12, 13, 15, 16, 17
    -   Rejection and pathological anger: 3, 4, 5, 11, 14, 21, 23
    -   Anxiety about the infant: 19, 20, 22, 25 cipient abuse: 18, 24
-   Reverse score: 1, 4, 8, 9, 11, 16, 22, 25

### Script

#### Recode item scores

```{r}
df <- df %>%
  mutate(across(contains("PBQ"),
            ~ case_when(
                     . == 1 ~ 5, # always
                     . == 2 ~ 4,
                     . == 3 ~ 3,
                     . == 4 ~ 2,
                     . == 5 ~ 1, 
                     . == 6 ~ 0, # never
                     .default = NA)))
```

#### Reverse item scores

```{r}
df <- df %>%
  mutate(across(c(PBQ1.12pp, PBQ4.12pp, PBQ8.12pp, PBQ9.12pp, 
                  PBQ11.12pp, PBQ16.12pp, PBQ22.12pp, PBQ25.12pp),
            ~5-.))

# Mark reversed scores with `_r`
setnames(x = df, 
         old = c("PBQ1.12pp", "PBQ4.12pp", "PBQ8.12pp", "PBQ9.12pp", 
                 "PBQ11.12pp", "PBQ16.12pp", "PBQ22.12pp", "PBQ25.12pp"), 
         new = gsub(pattern = ".12pp", 
                    replacement = "_r.12pp", 
                    x = c("PBQ1.12pp", "PBQ4.12pp", "PBQ8.12pp", "PBQ9.12pp", 
                          "PBQ11.12pp", "PBQ16.12pp", "PBQ22.12pp", "PBQ25.12pp")))
```

#### Calculate summary scores

```{r}
df <- df %>% 
  
  # Tell R that we want to take the mean across a row
  rowwise() %>%
  
  # Calculate total scores/subscales
  mutate(PBQ_impaired.12pp = sum(c(PBQ1_r.12pp, PBQ2.12pp, 
                                  c_across(PBQ6.12pp:PBQ10.12pp), 
                                  PBQ12.12pp, PBQ13.12pp, 
                                  c_across(PBQ15.12pp:PBQ17.12pp)), na.rm = F),
         PBQ_anger.12pp = sum(c(c_across(PBQ3.12pp:PBQ5.12pp), 
                               PBQ11_r.12pp, PBQ14.12pp, PBQ21.12pp, PBQ23.12pp), na.rm = T), 
         PBQ_anxiety.12pp = sum(c(PBQ19.12pp, PBQ20.12pp, PBQ22_r.12pp, PBQ25_r.12pp), na.rm = T), 
         PBQ_abuse.12pp = sum(c(PBQ18.12pp, PBQ24.12pp), na.rm = T)) %>%
  
  # Recode 0's that should be NA 
  mutate(across(PBQ_impaired.12pp:PBQ_abuse.12pp, 
                ~case_when(all(is.na(c_across(PBQ1_r.12pp:PBQ25_r.12pp))) ~ NA_real_, 
                           .default = .))) %>%
  
  # Move the total score/subscales so they come immediately after the measures
  relocate(PBQ_impaired.12pp:PBQ_abuse.12pp, .after = PBQ25_r.12pp)
```

### Label

```{r}
df <- df %>% 
  # Direct Score
  mutate(across(contains("PBQ") & !contains("_"),
            ~ labelled(., 
                     c("Always" = 5, 
                       "Very often" = 4, 
                       "Quite often" = 3, 
                       "Sometimes" = 2, 
                       "Rarely" = 1, 
                       "Never" = 0), 
                     label = "Postpartum Bonding Questionnaire"))) %>%
  # Reverse score
  mutate(across(contains("PBQ") & contains("_r"),
            ~ labelled(., 
                     c("Always" = 0, 
                       "Very often" = 1, 
                       "Quite often" = 2, 
                       "Sometimes" = 3, 
                       "Rarely" = 4, 
                       "Never" = 5), 
                     label = "Postpartum Bonding Questionnaire (reverse-scored)"))) %>%
  # Summary scores
  mutate(PBQ_impaired.12pp = labelled(PBQ_impaired.12pp, label = "PBQ: Impaired Bonding"), 
         PBQ_anger.12pp = labelled(PBQ_anger.12pp, label = "PBQ: Rejection and Pathological Anger"), 
         PBQ_anxiety.12pp = labelled(PBQ_anxiety.12pp, label = "PBQ: Anxiety about the Infant"), 
         PBQ_abuse.12pp = labelled(PBQ_abuse.12pp, label = "PBQ: Incipient Abuse"))
```

### Check and Print

:::: panel-tabset
#### Check

::: panel-tabset
##### Check Counts

```{r}
#| echo: false

# Direct Score
check_categorical(df, contains("PBQ") & !contains("_")) %>% arrange(value) %>% knitr::kable()
# Reverse Score
check_categorical(df, contains("PBQ") & contains("_r")) %>% arrange(value) %>% knitr::kable()

```

##### Check Numbers

```{r}
#| echo: false
check_continuous(df, PBQ_impaired.12pp:PBQ_abuse.12pp) %>% knitr::kable()
```

##### Check Reliability

###### Impaired Bonding

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, c(PBQ1_r.12pp, PBQ2.12pp,
                                        PBQ6.12pp:PBQ10.12pp,
                                        PBQ12.12pp, PBQ13.12pp, 
                                        PBQ15.12pp:PBQ17.12pp)), na.rm = T)
```

###### Rejection and pathological anger

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, c(PBQ3.12pp:PBQ5.12pp, 
                                        PBQ11_r.12pp, PBQ14.12pp, PBQ21.12pp,
                                        PBQ23.12pp)), na.rm = T)
```

###### Anxiety about the infant

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, c(PBQ19.12pp, PBQ20.12pp, PBQ22_r.12pp, PBQ25_r.12pp)), na.rm = T)
```

###### Incipient abuse

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, c(PBQ18.12pp, PBQ24.12pp)), na.rm = T)
```

##### Check Variable Labels

```{r}
#| echo: false
inspect_labels(df, contains("PBQ"))
```
:::

#### Print

```{r}
#| echo: false
print_slice(df, contains("PBQ"))
```
::::
:::::

## PingSS: Parenting Stress Scale

::::: panel-tabset
### Notes

-   Berry & Jones, 1995
-   18 items
-   1-5 Likert scale:
    -   1 = Strongly disagree
    -   5 = Strongly agree
-   Sum score
    -   Higher score = more stress
    -   But SPSS syntax calculated a mean
-   No subscales
-   Reverse score: 1, 2, 5, 6, 7, 8, 17, 18

### Script

#### Reverse item scores

```{r}
df <- df %>%
  mutate(across(c(PingSS1.12pp, PingSS2.12pp, PingSS5.12pp:PingSS8.12pp,
                  PingSS17.12pp, PingSS18.12pp),
            ~6-.))

# Mark reversed scores with `_r`
setnames(x = df, 
         old = c("PingSS1.12pp", "PingSS2.12pp", "PingSS5.12pp",
                 "PingSS6.12pp", "PingSS7.12pp", "PingSS8.12pp",
                 "PingSS17.12pp", "PingSS18.12pp"), 
         new = gsub(pattern = ".12pp", 
                    replacement = "_r.12pp", 
                    x = c("PingSS1.12pp", "PingSS2.12pp", "PingSS5.12pp",
                          "PingSS6.12pp", "PingSS7.12pp", "PingSS8.12pp",
                          "PingSS17.12pp", "PingSS18.12pp")))
```

#### Calculate summary scores

```{r}
df <- df %>% 
  
  # Tell R that we want to take the mean across a row
  rowwise() %>%
  
  # Calculate total scores/subscales
  mutate(PingSS_tot.12pp = sum(c_across(PingSS1_r.12pp:PingSS18_r.12pp), na.rm = T)) %>%
  
   # Recode 0's that should be NA 
  mutate(PingSS_tot.12pp = case_when(
    all(is.na(c_across(PingSS1_r.12pp:PingSS18_r.12pp))) ~ NA_real_,
    .default = PingSS_tot.12pp)) %>%
  
  # Move the total score/subscales so they come immediately after the measures
  relocate(PingSS_tot.12pp, .after = PingSS18_r.12pp)
```

### Label

```{r}
df <- df %>% 
  # Direct scores
  mutate(across(contains("PingSS") & !contains("_"),
            ~ labelled(., 
                     c("Strongly disagree" = 1, 
                       "Disagree" = 2, 
                       "Undecided" = 3, 
                       "Agree" = 4, 
                       "Strongly agree" = 5),
                     label = "Parenting Stress Scale"))) %>%
  # Reverse scores
  mutate(across(contains("PingSS") & contains("_r"),
            ~ labelled(., 
                     c("Strongly disagree" = 5, 
                       "Disagree" = 4, 
                       "Undecided" = 3, 
                       "Agree" = 2, 
                       "Strongly agree" = 1),
                     label = "Parenting Stress Scale (reverse-scored)"))) %>%
  # Sum Score
  mutate(PingSS_tot.12pp = labelled(PingSS_tot.12pp, label = "Parenting Stress Scale: Total Score"))
```

### Check and Print

:::: panel-tabset
#### Check

::: panel-tabset
##### Check Counts

```{r}
#| echo: false

# Direct Score
check_categorical(df, contains("PingSS") & !contains("_")) %>% knitr::kable()
# Reverse Score
check_categorical(df, contains("PingSS") & contains("_r")) %>% arrange(value) %>% knitr::kable()

```

##### Check Numbers

```{r}
#| echo: false
check_continuous(df, PingSS_tot.12pp) %>% knitr::kable()
```

##### Check Reliability

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, PingSS1_r.12pp:PingSS18_r.12pp), na.rm = T)
```

##### Check Variable Labels

```{r}
#| echo: false
inspect_labels(df, contains("PingSS"))
```
:::

#### Print

```{r}
#| echo: false
print_slice(df, contains("PingSS"))
```
::::
:::::

## PSI: Parenting Stress Index

::::: panel-tabset
### Notes

-   Abidin, 2012
-   36 items
-   1-5 Likert scale:
    -   1 = Strongly disagree
    -   5 = Strongly agree
    -   The scoring instructions seem to be reversed
-   Sum score
    -   Higher scores for PD, PCDI, DC= more parenting stress
    -   Higher scores for DR = increased social desirability bias
-   Subscales:
    -   Defensive responding (DR): 1, 2, 3, 7, 8, 9, 11
    -   Parental distress (PD): 1-12
    -   Parent-Child Dysfunctional Interaction (PCDI): 13-24
    -   Difficult Child (DC): 25-36
    -   Total score: PD+PCDI+DC
-   Reverse score: all

### Script

#### Recode item scores

```{r}
df <- df %>%
  mutate(across(PSI1.12pp:PSI36.12pp,
                ~ 6-.))
```

#### Calculate summary scores

```{r}
df <- df %>% 
  
  # Tell R that we want to take the mean across a row
  rowwise() %>%
  
  
  # Calculate subscales/total score
  mutate(PSI_dr.12pp = sum(c(PSI1.12pp, PSI2.12pp, PSI3.12pp, 
                            PSI7.12pp, PSI8.12pp, PSI9.12pp, PSI11.12pp),
                          na.rm = F), 
         PSI_pd.12pp = sum(c_across(PSI1.12pp:PSI12.12pp), na.rm = F), 
         PSI_pcdi.12pp = sum(c_across(PSI13.12pp:PSI24.12pp), na.rm = F), 
         PSI_dc.12pp = sum(c_across(PSI25.12pp:PSI36.12pp), na.rm = F),
         PSI_tot.12pp = sum(c_across(PSI1.12pp:PSI36.12pp), na.rm = F)) %>%
  
  # Move the total score/subscales so they come immediately after the measures
  relocate(PSI_dr.12pp:PSI_tot.12pp, .after = PSI36.12pp)
```

### Label

```{r}
df <- df %>% 
  # Label Majority of Items
  mutate(across(c(PSI1.12pp:PSI21.12pp, PSI23.12pp:PSI31.12pp, PSI34.12pp:PSI36.12pp),
            ~ labelled(., 
                     c("Strongly disagree" = 1,  
                       "Disagree" = 2,  
                       "Not sure" = 3,  
                       "Agree" = 4,  
                       "Strongly agree" = 5),
                     label = "Parenting Stress Index"))) %>%
  # Label special items
  mutate(PSI22.12pp = labelled(PSI22.12pp, 
                              c("A very good parent" = 1, 
                                "A better than average parent" = 2, 
                                "An average parent" = 3, 
                                "A person who has some trouble being a parent" = 4,
                                "Not very good at being a parent" = 5), 
                              label = "Parenting Stress Index"), 
         PSI32.12pp = labelled(PSI32.12pp,
                              c("Much easier than I expected" = 1,
                                "Somewhat easier than I expected" = 2,
                                "About as hard as I expected" = 3,
                                "Somewhat harder than I expected" = 4,
                                "Much harder than I expected" = 5),
                              label = "Parenting Stress Index"), 
         PSI33.12pp = labelled(PSI33.12pp, 
                              c("1-3" = 1,
                                "4-5" = 2,
                                "6-7" = 3,
                                "8-9" = 4,
                                "10+" = 5), 
                              label = "Parenting Stress Index")) %>%
  # Label Subscales and Total Score
  mutate(PSI_dr.12pp = labelled(PSI_dr.12pp, label = "PSI: Defensive Responding Scale"), 
         PSI_pd.12pp = labelled(PSI_pd.12pp, label = "PSI: Parental Distress Scale"), 
         PSI_pcdi.12pp = labelled(PSI_pcdi.12pp, label = "PSI: Parent-Child Dysfunctional Interaction"), 
         PSI_dc.12pp = labelled(PSI_dc.12pp, label = "PSI: Difficult Child Scale"), 
         PSI_tot.12pp = labelled(PSI_tot.12pp, label = "PSI: Total Score"))
```

### Check and Print

:::: panel-tabset
#### Check

::: panel-tabset
##### Check Counts

```{r}
#| echo: false
check_categorical(df, c(PSI1.12pp:PSI21.12pp, PSI23.12pp:PSI31.12pp, PSI34.12pp:PSI36.12pp)) %>% arrange(value) %>% knitr::kable()
check_categorical(df, PSI22.12pp) %>% knitr::kable()
check_categorical(df, PSI32.12pp) %>% knitr::kable()
check_categorical(df, PSI33.12pp) %>% knitr::kable()

```

##### Check Numbers

```{r}
#| echo: false
check_continuous(df, PSI_dr.12pp:PSI_tot.12pp) %>% knitr::kable()
```

##### Check Reliability

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, PSI1.12pp:PSI36.12pp), na.rm = T)
```

##### Check Variable Labels

```{r}
#| echo: false
inspect_labels(df, contains("PSI"))
```
:::

#### Print

```{r}
#| echo: false
print_slice(df, contains("PSI"))
```
::::
:::::

## PSQI: Pittsburgh Sleep Quality Index

::::::::: panel-tabset
### Notes

-   Buysee et al., 1989
-   9 items (item 5 has A-J)
-   0-3 Likert scale
    -   Items 1-4 are open-ended
    -   Items 5-8: 0 = not during the past month; 3 = three or more
        times a week
    -   Item 9: 0 = very good; 3 = very bad
-   Sum score of "components"
    -   For global PSQI, a score over 5 indicates poor sleep quality
    -   See below for component score calculations
-   No reverse scores
-   Other notes:
    -   Item 1: if they listed a range of times, we took the average
    -   Item 2: if they listed a range of times, we took the average
    -   Item 3: if they listed a range of times, we took the average
    -   Item 4: if they listed a range of times, we took the average
    -   Component 5: I replaced missing values in 5b-5j with the mean of
        5b-5j and then took the sum before recoding

### Script

::::: panel-tabset
#### Recode item scores/responses

::: panel-tabset
##### Item 1

```{r}
df <- df %>%
  
  ungroup() %>%
  
  # Create raw variable that duplicates original column for reference
  mutate(PSQI1_raw.12pp = PSQI1.12pp, .after = PSQI1.12pp) %>%
  
  # Create helper variable that standardizes time
  clean_time_range(PSQI1.12pp) %>% # creates helper_clean variable
  
  # Create helper variables that split up ranges 
  extract_time_range(helper_clean) %>% # creates helper_start and helper_end variables
  
  # Convert helpers to military time
  convert_to_military_night(c("helper_start", "helper_end")) %>%
  
  # Rewrite PSQI1.12pp as midpoint or start time 
  finalize_time(c("helper_start", "helper_end"), "PSQI1.12pp") %>%
  
  # Clean Specific Cases 
  mutate(PSQI1.12pp = case_when(
    CoupleID == 58 & Parent == "dad" ~ times("23:30:00"),
    CoupleID == 10 & Parent == "mom" ~ times("00:00:00"),
    CoupleID == 18 & Parent == "dad" ~ times("00:30:00"),
    CoupleID == 67 & Parent == "dad" ~ times("23:00:00"),
    .default = PSQI1.12pp
  )) %>%
  
  # Remove helper variables
  select(-contains("helper")) %>%
  relocate(PSQI1_raw.12pp, .after = PSQI9.12pp)
```

##### Item 2

```{r}
df <- df %>%
 
  ungroup() %>%
  
  # Create raw variable that duplicates original column for reference
  mutate(PSQI2_raw.12pp = PSQI2.12pp, .after = PSQI2.12pp) %>%
  
  # Create helper variable that standardizes times, ranges, and units
  standardize_latency(PSQI2.12pp) %>%
  
  # Extract time range
  extract_latency_times(helper_clean) %>%
  
  # Convert to minutes
  convert_to_minutes(helper_start, helper_end, helper_unit) %>%
  
  # Finalize PSQI2.12pp
  finalize_latency(PSQI2.12pp, helper_start, helper_end) %>%
  
  # Clean Specific Cases
  mutate(PSQI2.12pp = case_when(
    CoupleID == 39 & Parent == "mom" ~ 60.0,
    CoupleID == 30 & Parent == "mom" ~ 0.0,
    CoupleID == 73 & Parent == "dad" ~ 5.0,
    .default = PSQI2.12pp)) %>%
  
  # Remove helper variables
  select(-contains("helper")) %>%
  relocate(PSQI2_raw.12pp, .after = PSQI1_raw.12pp)
```

##### Item 3

```{r}
df <- df %>%
  
  ungroup() %>%
  
  # Create raw variable that duplicates original column for reference
  mutate(PSQI3_raw.12pp = PSQI3.12pp, .after = PSQI3.12pp)  %>%
  
  # Create helper variable that standardizes time
  clean_time_range(PSQI3.12pp) %>% # creates helper_clean variable
  
  # Create helper variables that split up ranges 
  extract_time_range(helper_clean) %>% # creates helper_start and helper_end variables
  
  # Convert helpers to military time
  convert_to_military_morning(c("helper_start", "helper_end")) %>%
  
  # Rewrite PSQI3.12pp as midpoint or start time 
  finalize_time(c("helper_start", "helper_end"), "PSQI3.12pp") %>%
  
  # Clean Specific Cases 
  mutate(PSQI3.12pp = case_when(
    CoupleID == 73 & Parent == "dad" ~ times("07:00:00"),
    .default = PSQI3.12pp)) %>%
  
  # Remove helper variables
  select(-contains("helper")) %>%
  relocate(PSQI3_raw.12pp, .after = PSQI2_raw.12pp)
```

##### Item 4

```{r}
df <- df %>%
  
  ungroup() %>%
  
  # Create raw variable that duplicates original column for reference
  mutate(PSQI4_raw.12pp = PSQI4.12pp, .after = PSQI4.12pp)  %>%
  
  # Create helper variable that standardizes time
  standardize_hours(PSQI4.12pp) %>%
  
  # Create helper variables that split up ranges 
  extract_hours(helper_clean) %>%
  
  # Rewrite PSQI4.12pp as midpoint or start time 
  finalize_hours(PSQI4.12pp, helper_start, helper_end) %>%

  # Clean Specific Cases 
  mutate(PSQI4.12pp = case_when(
    CoupleID == 24 & Parent == "dad" ~ 4.5, 
    CoupleID == 22 & Parent == "dad" ~ 5.5, 
    
    .default = PSQI4.12pp)) %>%
  
  # Remove helper variables
  select(-contains("helper")) %>%
  relocate(PSQI4_raw.12pp, .after = PSQI3_raw.12pp)
```

##### Items 5-9

```{r}
df <- df %>%
  
  rowwise() %>%
  
  # Recode values
  mutate(across(PSQI5a.12pp:PSQI9.12pp, 
            ~ case_when(
                     . == 1 ~ 0,
                     . == 2 ~ 1, 
                     . == 3 ~ 2, 
                     . == 4 ~ 3, 
                     .default = NA))) %>%
  
  # Convert PSQI5j to 0 when blank (per Buysse 2005) 
  mutate(PSQI5j.12pp = case_when(
    is.na(PSQI5j.12pp) == T & is.na(PSQI5a.12pp) == F ~ 0, 
    is.na(PSQI5a.12pp) == T ~ NA, 
    .default = PSQI5j.12pp)) 
```
:::

#### Calculate component scores

::: panel-tabset
##### Component 1: Overall Quality

-   Equal to PSQI9

```{r}
df <- df %>%
  mutate(PSQI_qual.12pp = PSQI9.12pp)%>%
  relocate(PSQI_qual.12pp, .after = PSQI4_raw.12pp)
```

##### Component 2: Latency

-   First transform PSQI2
-   Then add transformed score to PSQI5a
-   Finally transform the sum

```{r}
df <- df %>%
  
  rowwise() %>%
  
  # Step 1: PSQI2 score transformed to <15m=0; 16-30m=1; 31-60m=2; >60m=3
  mutate(PSQI_c2_helper = 
           case_when(
             PSQI2.12pp <= 15 ~ 0, 
             PSQI2.12pp > 15 & PSQI2.12pp <=30 ~ 1,
             PSQI2.12pp > 30 & PSQI2.12pp <= 60 ~ 2, 
             PSQI2.12pp > 60 ~ 3,
             .default = NA)) %>%
  
  # Step 2: Add score from step #1 to PSQI5a
  mutate(PSQI_c2_helper2 = PSQI_c2_helper + PSQI5a.12pp) %>%
  
  # Step 3: Combined score transformed to 0=0; 1-2=1; 3-4=2; 5-6=3
  mutate(PSQI_lat.12pp = 
           case_when(
             PSQI_c2_helper2 == 0 ~ 0, 
             PSQI_c2_helper2 == 1 | PSQI_c2_helper2 == 2 ~ 1, 
             PSQI_c2_helper2 == 3 | PSQI_c2_helper2 == 4 ~ 2, 
             PSQI_c2_helper2 == 5 | PSQI_c2_helper2 == 6 ~ 3)) %>%
  
  # Clean Up
  select(-contains("helper")) %>%
  relocate(PSQI_lat.12pp, .after = PSQI_qual.12pp)
```

##### Component 3: Duration

-   Transform PSQI4

```{r}
df <- df %>%
  
  rowwise() %>%
  
  mutate(PSQI_dur.12pp =
           case_when(PSQI4.12pp > 7 ~ 0, 
                     PSQI4.12pp <= 7 & PSQI4.12pp > 6 ~ 1, 
                     PSQI4.12pp <= 6 & PSQI4.12pp > 5 ~ 2, 
                     PSQI4.12pp <= 5 ~ 3, 
                     .default = NA)) %>%
  
  # Clean up 
  relocate(PSQI_dur.12pp, .after = PSQI_lat.12pp)
```

##### Component 4: Efficiency

-   First calculate time in bed (PSQI3-PSQI1)
-   Then divide PSQI4 by time in bed and multiply by 100
-   Finally transform the percentage

```{r}
df <- df %>%
  
  rowwise() %>%
  
  # Add fake date so that R knows that parents are waking up the day after they go to bed 
  mutate(PSQI_pm_helper = as.POSIXct(chron(dates. = "06/26/2022", times. = PSQI1.12pp))+25200) %>%
  mutate(PSQI_am_helper = as.POSIXct(chron(dates. = "06/27/2022", times. = PSQI3.12pp))+25200) %>%
  
  # Tell R that parents who go to bed after midnight are actually sleeping the following day
  mutate(PSQI_pm_helper = as.POSIXct(case_when(
    PSQI_pm_helper <= "2022-06-26 13:00:00" ~ PSQI_pm_helper+86400, 
    .default = PSQI_pm_helper), 
    origin = "1970-01-01")) %>%
  
  # Calculate hours in bed
  mutate(PSQI_hib_helper = as.numeric(difftime(PSQI_am_helper, PSQI_pm_helper, units = "hours"))) %>%
  
  # Divide sleeping hours by hours in bed
  mutate(PSQI_c4_helper = (PSQI4.12pp/PSQI_hib_helper)*100) %>%
  
  # Recode 4
  mutate(PSQI_effic.12pp = case_when(
    PSQI_c4_helper >= 85 ~ 0,
    PSQI_c4_helper < 85 & PSQI_c4_helper >= 75 ~ 1, 
    PSQI_c4_helper < 75 & PSQI_c4_helper >= 65 ~ 2, 
    PSQI_c4_helper < 65 ~ 3, 
    .default = NA)) %>%
  
  # Remove helper variables
  select(-contains("helper")) %>%
  relocate(PSQI_effic.12pp, .after = PSQI_dur.12pp)
```

##### Component 5: Disturbance

-   First sum scores 5b through 5j
-   Then transform the sum

```{r}
df <- df %>% 
  
  rowwise() %>%
  
  # Calculate 5
  mutate(PSQI_c5_helper = sum(c_across(PSQI5b.12pp:PSQI5j.12pp))) %>%
  
  # Recode 5
  mutate(PSQI_disturb.12pp = case_when(
    PSQI_c5_helper == 0 ~ 0, 
    PSQI_c5_helper >= 1 & PSQI_c5_helper <= 9 ~ 1, 
    PSQI_c5_helper > 9 & PSQI_c5_helper <= 18 ~ 2, 
    PSQI_c5_helper > 18 ~ 3, 
    .default = NA)) %>%
  
  # Remove helper variables
  select(-contains("helper")) %>%
  relocate(PSQI_disturb.12pp, .after = PSQI_effic.12pp)
```

##### Component 6: Meds

-   Equal to PSQI6

```{r}
df <- df %>%
  mutate(PSQI_med.12pp = PSQI6.12pp) %>%
  
  # Clean up
  relocate(PSQI_med.12pp, .after = PSQI_disturb.12pp)
```

##### Component 7: Dysfunction during Day

-   First add PSQI7 and PSQI8
-   Then transform the sum

```{r}
df <- df %>%
  
  rowwise() %>%
  
  mutate(PSQI_c7_helper = sum(c(PSQI7.12pp, PSQI8.12pp))) %>%
  
  mutate(PSQI_daydys.12pp = case_when(
    PSQI_c7_helper == 0 ~ 0,
    PSQI_c7_helper == 1 | PSQI_c7_helper == 2 ~ 1, 
    PSQI_c7_helper == 3 | PSQI_c7_helper == 4 ~ 2, 
    PSQI_c7_helper == 5 | PSQI_c7_helper == 6 ~ 3, 
    .default = NA)) %>%
  
  # Remove helper variables
  select(-contains("helper")) %>%
  relocate(PSQI_daydys.12pp, .after = PSQI_med.12pp)
```
:::

#### Calculate Global Score

```{r}
df <- df %>%
  rowwise() %>%
  
  # Calculate total score
  mutate(PSQI_global.12pp = sum(c_across(PSQI_qual.12pp:PSQI_daydys.12pp))) %>%
  
  # Clean up
  relocate(PSQI_global.12pp, .after = PSQI_daydys.12pp)
  
```
:::::

### Label

```{r}
df <- df %>%
  
  # Items 1-4
  mutate(PSQI1.12pp = labelled(PSQI1.12pp, label = "PSQI: Bedtime"),
         PSQI2.12pp = labelled(PSQI2.12pp, label = "PSQI: Minutes to fall asleep"),
         PSQI3.12pp = labelled(PSQI3.12pp, label = "PSQI: Wake time"),
         PSQI4.12pp = labelled(PSQI4.12pp, label = "PSQI: Hours of actual sleep")) %>%
  
  # Items 1-4 (raw)
  mutate(PSQI1_raw.12pp = labelled(PSQI1_raw.12pp, label = "PSQI: Bedtime (raw)"),
         PSQI2_raw.12pp = labelled(PSQI2_raw.12pp, label = "PSQI: Minutes to fall asleep (raw)"),
         PSQI3_raw.12pp = labelled(PSQI3_raw.12pp, label = "PSQI: Wake time (raw)"),
         PSQI4_raw.12pp = labelled(PSQI4_raw.12pp, label = "PSQI: Hours of actual sleep (raw)")) %>%
  
  # Items 5a-5J
  mutate(across(PSQI5a.12pp:PSQI5j.12pp,
                ~ labelled(., 
                           label = "PSQI: Reasons for trouble sleeping",
                           labels = c("Not during the last month" = 0,
                                      "Less than once a week" = 1, 
                                      "Once or twice a week" = 2, 
                                      "Three or more times a week" = 3)))) %>%
  
  # Items 6-8
  mutate(across(PSQI6.12pp:PSQI8.12pp, 
                ~ labelled(., 
                           label = "PSQI: Misc. questions",
                           labels = c("Not during the last month" = 0,
                                      "Less than once a week" = 1, 
                                      "Once or twice a week" = 2, 
                                      "Three or more times a week" = 3)))) %>%
  
  # Item 9 
  mutate(PSQI9.12pp = labelled(PSQI9.12pp, 
                              label = "PSQI: How would you rate your sleep quality?", 
                              labels = c("Very good" = 0,
                                         "Fairly good" = 1, 
                                         "Fairly bad" = 2, 
                                         "Very bad" = 3))) %>%
  
  # Components
  mutate(PSQI_qual.12pp = labelled(PSQI_qual.12pp, label = "PSQI: Component 1, Sleep Quality"),
         PSQI_lat.12pp = labelled(PSQI_lat.12pp, label = "PSQI: Component 2, Sleep Latency"),
         PSQI_dur.12pp = labelled(PSQI_dur.12pp, label = "PSQI: Component 3, Sleep Duration"),
         PSQI_effic.12pp = labelled(PSQI_effic.12pp, label = "PSQI: Component 4, Sleep Efficiency"),
         PSQI_disturb.12pp = labelled(PSQI_disturb.12pp, label = "PSQI: Component 5, Sleep Disturbance"),
         PSQI_med.12pp = labelled(PSQI_med.12pp, label = "PSQI: Component 6, Sleep Medication"),
         PSQI_daydys.12pp = labelled(PSQI_daydys.12pp, label = "PSQI: Component 7, Dysfunction during the Day"),
         PSQI_global.12pp = labelled(PSQI_global.12pp, label = "Pittsburgh Sleep Quality Index: Global Score"))
  
```

### Check and Print

::::: panel-tabset
#### Check

::: panel-tabset
##### Check Counts

```{r}
#| echo: false

check_categorical(df, PSQI5a.12pp:PSQI8.12pp) %>% knitr::kable()
check_categorical(df, PSQI9.12pp) %>% knitr::kable()
```

##### Check Numbers

```{r}
#| echo: false

check_continuous(df, PSQI_global.12pp) %>% knitr::kable()
```

##### Check Reliability

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, PSQI_qual.12pp:PSQI_daydys.12pp), na.rm = T)
```

##### Check Variable Labels

```{r}
#| echo: false
inspect_labels(df, contains("PSQI") & !contains("MRI"))
```
:::

#### Print

::: panel-tabset
##### 1: Quality

-   Equal to PSQI9

```{r}
#| echo: false
print_slice(df, PSQI9.12pp, PSQI_qual.12pp)
```

##### 2: Latency

-   First transform PSQI2
-   Then add transformed score to PSQI5a
-   Finally transform the sum

```{r}
#| echo: false
print_slice(df, PSQI2.12pp, PSQI5a.12pp, PSQI_lat.12pp)
```

##### 3: Duration

-   Transform PSQI4

```{r}
#| echo: false
print_slice(df, PSQI4.12pp, PSQI_dur.12pp)
```

##### 4: Efficiency

-   First calculate time in bed (PSQI3-PSQI1)
-   Then divide PSQI4 by time in bed and multiply by 100
-   Finally transform the percentage

```{r}
#| echo: false
print_slice(df, PSQI1_raw.12pp, PSQI3_raw.12pp, PSQI4.12pp, PSQI_effic.12pp)
```

##### 5: Disturbance

-   First sum scores 5b through 5j
-   Then transform the sum

```{r}
#| echo: false
print_slice(df, PSQI5b.12pp:PSQI5j.12pp, PSQI_disturb.12pp)
```

##### 6: Medication

-   Equal to PSQI6

```{r}
#| echo: false
print_slice(df, PSQI6.12pp, PSQI_med.12pp)
```

##### 7: Dysfunction during the day

-   First add PSQI7 and PSQI8
-   Then transform the sum

```{r}
#| echo: false
print_slice(df, PSQI7.12pp, PSQI8.12pp, PSQI_daydys.12pp)
```

##### Global PSQI

```{r}
#| echo: false
print_slice(df, PSQI_qual.12pp:PSQI_global.12pp)
```
:::
:::::
:::::::::

:::

## PSS: Perceived Stress Scale

::::: panel-tabset
### Notes

-   Cohen et al., 1983
-   14 items
-   0-4 Likert Scale
    -   0 = Never
    -   4 = Very often
-   Sum score
    -   Higher scores = increased stress level
-   No subscale
-   Reverse score: 4, 5, 6, 7, 9, 10, 13

### Script

#### Recode item scores

```{r}
df <- df %>%
# Re-code items
  mutate(across(PSS1.12pp:PSS14.12pp, 
            ~case_when(
              . == 1  ~ 0,
              . == 2  ~ 1,
              . == 3  ~ 2,
              . == 4  ~ 3, 
              . == 5  ~ 4,
              .default = NA)))
```

#### Reverse item scores

```{r}
# Reverse Score Q's 4, 5, 6, 7, 9, 10, 13
df <- df %>%
  mutate(across(c(PSS4.12pp, PSS5.12pp, PSS6.12pp, 
                   PSS7.12pp, PSS9.12pp, PSS10.12pp, 
                   PSS13.12pp),
                   ~4-.))

# Mark reversed scores with `_r`
setnames(x = df, 
                     old = c("PSS4.12pp", "PSS5.12pp", "PSS6.12pp", 
                             "PSS7.12pp", "PSS9.12pp", "PSS10.12pp", 
                             "PSS13.12pp"), 
                     new = gsub(pattern = ".12pp", 
                          replacement = "_r.12pp", 
                          x = c("PSS4.12pp", "PSS5.12pp", "PSS6.12pp", 
                             "PSS7.12pp", "PSS9.12pp", "PSS10.12pp", 
                             "PSS13.12pp")))
```

#### Calculate summary score

```{r}
df <- df %>% 
  
  # Tell R that we want to take the mean across a row
  rowwise() %>%
  
  # Tell R that scores are numeric
  mutate(across(PSS1.12pp:PSS14.12pp, as.numeric)) %>%
  
  # Calculate total scores/subscales
  mutate(PSS_tot.12pp = sum(c_across(PSS1.12pp:PSS14.12pp), na.rm = T)) %>%
  
  # Clean up NAs
  mutate(across(PSS_tot.12pp, ~na_if(., 0))) %>%
  
  # Move the total score/subscales so they come immediately after the measures
  relocate(PSS_tot.12pp, .after = PSS14.12pp)
```

### Label

```{r}
df <- df %>% 
  # Create value and variable labels
  mutate(across(contains("PSS") & !contains("_"),
            ~ labelled(., 
                     c("Never" = 0, 
                       "Almost never" = 1, 
                       "Sometimes" = 2, 
                       "Fairly often" = 3, 
                       "Very often" = 4), 
                     label = "Perceived Stress Scale"))) %>%
  mutate(across(contains("PSS") & contains("_r"),
            ~ labelled(., 
                     c("Never" = 4, 
                       "Almost never" = 3,
                       "Sometimes" = 2,
                       "Fairly often" = 1, 
                       "Very often" = 0), 
                     label = "Perceived Stress Scale (reverse-scored)"))) %>%
  mutate(PSS_tot.12pp = labelled(PSS_tot.12pp, label = "Perceived Stress Scale: Total Score"))
```

### Check and Print

:::: panel-tabset
#### Check

::: panel-tabset
##### Check Counts

```{r}
#| echo: false
# Direct Score
check_categorical(df, contains("PSS") & !contains("_")) %>% arrange(value) %>% knitr::kable()
# Reverse Score
check_categorical(df, contains("PSS") & contains("_r")) %>% knitr::kable()
```

##### Check Numbers

```{r}
#| echo: false
check_continuous(df, PSS_tot.12pp) %>% knitr::kable()
```

##### Check Reliability

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, PSS1.12pp:PSS14.12pp), na.rm = T)
```

##### Check Variable Labels

```{r}
#| echo: false
inspect_labels(df, contains("PSS")) 
```
:::

#### Print

```{r}
#| echo: false
print_slice(df, contains("PSS"))
```
::::
:::::

## SCL: Symptom Checklist-90

:::::: panel-tabset
### Notes

-   Derogatis et al., 1973
-   90 items
    -   HATCH only includes 87 items
    -   2 suicidality items omitted:
        -   "Thoughts of ending your life" (#15) - depression subscale
        -   "Thoughts of death or dying" (#59) - additional items
    -   1 aggression item omitted:
        -   "Having urges to beat, injure, or harm someone." (#63) -
            anger-hostility subscale
-   0-4 Likert Scale
    -   0 = Not at all
    -   4 = Extremely
-   Mean scores
    -   Higher scores = higher distress
-   9 subscales, 3 global scales, and an "additional items" category:
    -   Subscales:
        -   Somatization (1, 4, 12, 27, 40, 42, 48, 49, 52, 53, 56, and
            58) 
        -   Obsessive-Compulsive (3, 9, 10, 28, 38, 45, 46, 51, 55, and
            65) terpersonal Sensitivity (6, 21, 34, 36, 37, 41, 61, 69,
                and 73)
        -   Depression (5, 14, 20, 22, 26, 29, 30, 31, 32, 54, 71, and
            79) 
        -   Anxiety (17, 23, 33, 39, 57, 72, 78, 80, and 86)
        -   Hostility (11, 24, 63, 67, 74, and 81)
        -   Phobic-Anxiety (13, 25, 47, 50, 70, 75, and 82)
        -   Paranoid Ideation (8, 18, 43, 68, 76, and 83)
        -   Psychoticism (7, 16, 35, 62, 77, 84, 85, 87, 88, and 90)
    -   Global scales:
        -   Global Severity Index (All items)
        -   Positive Symptom Distress Index (Mean of non-zero responses)
        -   Positive Symptom Total (Count of non-zero items)
    -   "Additional Items" category (19, 44, 59, 60, 64, and 89)
-   Reverse scored items: none
-   Other notes: Add .005 based on most recent scoring instructions in
    QGlobal

### Script

::: panel-tabset
#### Recode item scores

```{r SCL-recode}
df <- df %>%
# Re-code items
 mutate(across(SCL1.12pp:SCL90.12pp, 
            ~case_when( 
                        . == 1 ~ 0,
                        . == 2 ~ 1,
                        . == 3 ~ 2,
                        . == 4 ~ 3,
                        . == 5 ~ 4, 
                        .default = NA)))
```

#### Calculate symptom dimensions

```{r}
df <- df %>% 
  
  # Tell R that we want to take the mean across a row
  rowwise() %>%
  
  # Tell R that scores are numeric
  mutate(across(SCL1.12pp:SCL90.12pp, as.numeric)) %>%
  
  # Calculate subscales
  mutate(SCL_som.12pp = mean(c(SCL1.12pp, SCL4.12pp, SCL12.12pp, 
                             SCL27.12pp, SCL40.12pp, SCL42.12pp, 
                             SCL48.12pp, SCL49.12pp, SCL50.12pp, 
                             SCL53.12pp, SCL56.12pp, SCL58.12pp), 
                           na.rm = T) + .005, 
         SCL_oc.12pp = mean(c(SCL3.12pp, SCL9.12pp, SCL10.12pp, 
                            SCL28.12pp, SCL38.12pp, SCL45.12pp, 
                            SCL46.12pp, SCL51.12pp, SCL55.12pp, SCL65.12pp), 
                          na.rm = T) + .005, 
         SCL_is.12pp = mean(c(SCL6.12pp, SCL21.12pp, SCL34.12pp,
                            SCL36.12pp, SCL37.12pp, SCL41.12pp, 
                            SCL61.12pp, SCL69.12pp, SCL73.12pp), 
                          na.rm = T) + .005, 
         SCL_dep.12pp = mean(c(SCL5.12pp, SCL14.12pp, SCL20.12pp, 
                             SCL22.12pp, SCL26.12pp, SCL29.12pp, 
                             SCL30.12pp, SCL31.12pp, SCL32.12pp, 
                             SCL54.12pp, SCL71.12pp, SCL79.12pp), 
                           na.rm = T) + .005, 
         SCL_anx.12pp = mean(c(SCL2.12pp, SCL17.12pp, SCL23.12pp, 
                             SCL33.12pp, SCL39.12pp, SCL57.12pp, 
                             SCL72.12pp, SCL78.12pp, SCL80.12pp, SCL86.12pp), 
                           na.rm = T) + .005, 
         SCL_hos.12pp = mean(c(SCL11.12pp, SCL24.12pp, SCL67.12pp,
                              SCL74.12pp, SCL81.12pp), 
                            na.rm = T) + .005, 
         SCL_phob.12pp = mean(c(SCL13.12pp, SCL25.12pp, SCL47.12pp, 
                              SCL50.12pp, SCL70.12pp, SCL75.12pp, SCL82.12pp), 
                            na.rm = T) + .005, 
         SCL_par.12pp = mean(c(SCL8.12pp, SCL18.12pp, SCL43.12pp, 
                             SCL68.12pp, SCL76.12pp, SCL83.12pp), 
                           na.rm = T) + .005, 
         SCL_psy.12pp = mean(c(SCL7.12pp, SCL16.12pp, SCL35.12pp, 
                             SCL62.12pp, SCL77.12pp, SCL84.12pp, 
                             SCL85.12pp, SCL88.12pp, SCL90.12pp), 
                           na.rm = T) + .005, 
         SCL_add.12pp = mean(c(SCL19.12pp, SCL44.12pp,SCL60.12pp, 
                             SCL64.12pp, SCL66.12pp, SCL89.12pp), 
                           na.rm = T) + .005 
         ) %>%
  
  # Round to two decimals
  mutate(across(c(SCL_som.12pp:SCL_add.12pp), ~round(., 2))) %>%
  
  # Replace NaN with NAs
  mutate(across(c(SCL_som.12pp:SCL_add.12pp), ~coalesce(., NA_real_)))
```

#### Calculate global scales

##### Global Severity Index

```{r}
df <- df %>% 
  
  # Tell R that we want to take the mean across a row
  rowwise() %>%
  
  # Count number of NAs in a row
  row_count(SCL1.12pp:SCL90.12pp, count = NA, var = "SCL_count_NA", append = T) %>%
  
  # Calculate total number of responses in a row
  mutate(SCL_totr = 87 - SCL_count_NA) %>%

  # Calculate Global Severity Index by dividing the sum of all responses by the total number of responses and adding .005
  mutate(SCL_gsi.12pp = sum(c_across(SCL1.12pp:SCL90.12pp), na.rm = T)/SCL_totr + .005) %>%
  
  # Round to two decimals
  mutate(SCL_gsi.12pp = round(SCL_gsi.12pp, 2))
```

##### Positive Symptom Scales

```{r}
df <- df %>%
  
  # Tell R that we want to take the mean across a row
  rowwise() %>%
  
  # Count number of zero-scored items in a row
  row_count(SCL1.12pp:SCL90.12pp, count = 0, var = "SCL_count_0", append = T) %>%

  # Calculate the Positive Symptom Total by subtracting the number of zero-value responses from the total number of responses
  mutate(SCL_pst.12pp = SCL_totr - SCL_count_0) %>%
  
  # Calculate the Positive Symptoms Distress Index by dividing the sum of all responses by the PST  and adding .005
  mutate(SCL_psdi.12pp = round(sum(c_across(SCL1.12pp:SCL90.12pp), na.rm = T)/SCL_pst.12pp + .005, 2)) 
```

#### Clean up subscales

```{r}
df <- df %>%
  
  # Remove helper variables
  select(-c(SCL_count_NA, SCL_count_0, SCL_totr)) %>% 

  # Replace NaN with NAs
   mutate(across(c(SCL_som.12pp:SCL_psdi.12pp), ~coalesce(., NA_real_))) %>%
  
  # Rowwise operation to set global scaleas to NA if all SCL1–SCL90 are NA
  rowwise() %>%
  mutate(across(SCL_gsi.12pp:SCL_psdi.12pp,
                ~ case_when(
                  all(is.na(c_across(SCL1.12pp:SCL90.12pp))) ~ NA_real_,
                  TRUE ~ .
                ))) %>%
  ungroup() %>%
  
  # Move the subscales so they come immediately after the measures
  relocate(SCL_som.12pp:SCL_psdi.12pp, .after = SCL90.12pp)
```
:::

### Label

```{r}
df <- df %>% 
  # Raw Items
  mutate(across(SCL1.12pp:SCL90.12pp,
            ~ labelled(., 
                     c("Not at all" = 0, 
                       "A little bit" = 1, 
                       "Moderately" = 2, 
                       "Quite a bit" = 3, 
                       "Extremely" = 4),
                     label = "Symptom Checklist 90"))) %>%
  
  # Subscales
  mutate(SCL_som.12pp = labelled(SCL_som.12pp, label = "SCL: Somatization Scale"), 
         SCL_oc.12pp = labelled(SCL_oc.12pp, label = "SCL: Obsessive Compulsive Scale"), 
         SCL_is.12pp = labelled(SCL_is.12pp, label = "SCL: Interpersonal Sensitivity Scale"), 
         SCL_dep.12pp = labelled(SCL_dep.12pp, label = "SCL: Depression Scale"),
         SCL_anx.12pp = labelled(SCL_anx.12pp, label = "SCL: Anxiety Scale"),
         SCL_hos.12pp = labelled(SCL_hos.12pp, label = "SCL: Hostility Scale"),
         SCL_phob.12pp = labelled(SCL_phob.12pp, label = "SCL: Phobic Anxiety Scale"),
         SCL_par.12pp = labelled(SCL_par.12pp, label = "SCL: Paranoid Ideation Scale"),
         SCL_psy.12pp = labelled(SCL_psy.12pp, label = "SCL: Psychoticism Scale"),
         SCL_add.12pp = labelled(SCL_add.12pp, label = "SCL: Additional Items")) %>%
  
  # Global Scales
  mutate(SCL_gsi.12pp = labelled(SCL_gsi.12pp, label = "SCL: Global Severity Index"), 
         SCL_pst.12pp = labelled(SCL_pst.12pp, label = "SCL: Positive Symptom Total"), 
         SCL_psdi.12pp = labelled(SCL_psdi.12pp, label = "SCL: Positive Symptom Distress Index"))
```

### Check and Print

:::: panel-tabset
#### Check

::: panel-tabset
##### Check Counts

```{r}
#| echo: false
check_categorical(df, contains("SCL") & !contains("_")) %>% arrange(value) %>% knitr::kable()
```

##### Check Numbers

```{r}
#| echo: false
check_continuous(df, SCL_som.12pp:SCL_psdi.12pp) %>% knitr::kable()
```

##### Check Reliability

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, SCL1.12pp:SCL90.12pp), na.rm = T)
```

##### Check Variable Labels

```{r}
#| echo: false
inspect_labels(df, contains("SCL")) 
```
:::

#### Print

```{r}
#| echo: false
print_slice(df, contains("SCL"))
```
::::
::::::

# HATCH-Designed Questions

## PRQ: Parenting Responsibilities Questionnaire

::::: panel-tabset
### Notes

-   Designed for HATCH
-   5 items
-   1-5 and 1-6 Likert Scales
    -   "Total time" questions are 1-6
    -   "Primary caregiver time" and share of time questions are 1-5
-   No summary score
-   No subscales
-   Reverse code: all items so that higher scores indicate more time
    spent with baby

### Script

#### Reverse Score Items

```{r}
df <- df %>% 
  mutate(across(c(PRQ_WeekTot.12pp, PRQ_WkendTot.12pp), 
                ~7-.)) %>%
  
  mutate(across(c(PRQ_WeekPrimary.12pp, PRQ_WkendPrimary.12pp, PRQ_Share.12pp), 
                ~6-.))
```

### Label

```{r}
df <- df %>% 
  # Weekday Hours
  mutate(PRQ_WeekTot.12pp = labelled(PRQ_WeekTot.12pp, 
                     c("8+ hours" = 6, 
                       "5-8 hours" = 5,
                       "3-4 hours" = 4, 
                       "2-3 hours" = 3, 
                       "1-2 hours" = 2, 
                       "0-1 hours" = 1),
                     label = "Waking hours with baby, average weekday")) %>%
  
  # Weekday Primary
  mutate(PRQ_WeekPrimary.12pp = labelled(PRQ_WeekPrimary.12pp, 
                     c("75-100%" = 5,
                       "50-75%" = 4, 
                       "About 50%" = 3, 
                       "25-50%" = 2, 
                       "0-25%" = 1),
                     label = "Percent of weekday hours spent alone with baby or as main caregiver")) %>%
  
    # Weekend Hours
  mutate(PRQ_WkendTot.12pp = labelled(PRQ_WkendTot.12pp, 
                     c("The whole day" = 6,
                       "8+ hours" = 5, 
                       "5-8 hours" = 4,
                       "3-4 hours" = 3, 
                       "1-3 hours" = 2, 
                       "0-1 hours" = 1),
                     label = "Waking hours with baby, average weekend day")) %>%
  
  # Weekend Primary
  mutate(PRQ_WkendPrimary.12pp = labelled(PRQ_WkendPrimary.12pp, 
                     c("75-100%" = 5,
                       "50-75%" = 4, 
                       "About 50%" = 3, 
                       "25-50%" = 2, 
                       "0-25%" = 1),
                     label = "Percent of weekend day hours spent alone with baby or as main caregiver")) %>%
  
  # Share of Infant Care
  mutate(PRQ_Share.12pp = labelled(PRQ_Share.12pp, 
                     c("I do 80% or more" = 5,
                       "I do 60% or more" = 4, 
                       "50-50" = 3, 
                       "I do 40% or less" = 2, 
                       "I do 20% or less" = 1),
                     label = "Compared to partner, what is your overall share of infant care")) 
```

### Check and Print

:::: panel-tabset
#### Check

::: panel-tabset
##### Check Counts

```{r}
#| echo: false
check_categorical(df, PRQ_WeekTot.12pp) %>% knitr::kable()
check_categorical(df, PRQ_WkendTot.12pp) %>% knitr::kable()
check_categorical(df, contains("PRQ") & contains("Primary")) %>% knitr::kable()
check_categorical(df, PRQ_Share.12pp) %>% knitr::kable()
```

##### Check Reliability

```{r}
#| echo: false
ltm::cronbach.alpha(data = select(df, contains("PRQ")), na.rm = T)
```

##### Check Variable Labels

```{r}
#| echo: false
inspect_labels(df, contains("PRQ")) 
```
:::

#### Print

```{r}
#| echo: false
print_slice(filter(df, !is.na(PRQ_WeekTot.12pp)), contains("PRQ"))
```
::::
:::::

## COVID Parenting Questions

:::::: panel-tabset
### Notes

-   Designed for HATCH
-   16 items
-   Mix of scales and open-ended
-   No summary score
-   No subscales
-   No reverse scores

### Script

::: panel-tabset
#### Recode `Precautions`

##### Recode Values

```{r}
# Create a named vector for replacements
replace_map <- c(
  "1" = "1",   # avoid social gathering
  "6" = "2",   # social distance
  "3" = "3",   # wfh
  "4" = "4",   # only go outside for essentials
  "13" = "5",  # cancelled medical appts
  "7" = "6",   # cancelled trips
  "9" = "7",   # cancelled events
  "10" = "8",  # changed hygiene habits
  "15" = "9",  # reduced baby's social contact with family
  "16" = "10", # reduced baby's social contact with friends
  "14" = "11"  # other
)

# Apply the replacements
df <- df %>%
  mutate(COVID_precautions.12pp = COVID_precautions.12pp %>%
           str_split(",") %>%  # Split the string into individual numbers
           map(~replace_map[.x]) %>%  # Replace each number using replace_map
           map_chr(~paste(.x, collapse = ","))) %>% # Combine back into a string
  mutate(COVID_precautions.12pp = na_if(COVID_precautions.12pp, "NA")) %>% # convert "NA" to NA
  mutate(COVID_precautions_text.12pp = na_if(COVID_precautions_text.12pp, "-99")) # convert -99 to NA
```

##### Split Up Multi-Select

```{r}
df <- df %>%
  separate_wider_delim(COVID_precautions.12pp, 
  delim = ",", 
  names = paste0("COVID_precautions_", 1:11, ".12pp"),
  too_few = "align_start")
```

#### Recode `Impact`

##### Recode Values

```{r}
# Create a named vector for replacements
replace_map <- c(
  "1" = "1",   # Lost my job
  "11" = "2",  # Changes to my job
  "5" = "3",   # Changes in partner's employment
  "35" = "4",  # Decrease in household income
  "22" = "5",  # Changes in childcare arrangements
  "12" = "6",  # Decreased number of in-person healthcare visits
  "31" = "7",  # Worry about contracting COVID-19
  "18" = "8",  # Worry about a family member's health
  "30" = "9",  # Death of someone I am close to
  "29" = "10", # Loneliness
  "32" = "11"  # Boredom
)

# Apply the replacements
df <- df %>%
  mutate(COVID_impact.12pp = COVID_impact.12pp %>%
           str_split(",") %>%  # Split the string into individual numbers
           map(~replace_map[.x]) %>%  # Replace each number using replace_map
           map_chr(~paste(.x, collapse = ",")))  %>% # Combine back into a string
  mutate(COVID_impact.12pp = na_if(COVID_impact.12pp, "NA")) # convert "NA" to NA
```

##### Split Up Multi-Select

```{r}
df <- df %>%
  separate_wider_delim(COVID_impact.12pp, 
  delim = ",", 
  names = paste0("COVID_impact_", 1:8, ".12pp"),
  too_few = "align_start")
```

#### Split Up `Childcare` Multi-Select

```{r}
df <- df %>%
  separate_wider_delim(COVID_childcare.12pp, 
  delim = ",", 
  names = paste0("COVID_childcare_", 1:3, ".12pp"),
  too_few = "align_start")
```

#### Recode `Contact`

```{r}
df <- df %>%
  mutate(across(COVID_contact1.12pp:COVID_contact5.12pp, 
                ~ case_when(
                  . == 1 ~ 1, #much less
                  . == 4 ~ 2, #somewhat less
                  . == 2 ~ 3, #about the same
                  . == 3 ~ 4, #somewhat more
                  . == 5 ~ 5, #much more
                  .default = NA)))
```

#### Recode `Social`

```{r}
df <- df %>%
  mutate(COVID_social.12pp = case_when(
    COVID_social.12pp == 1 ~ 1, #very negative
    COVID_social.12pp == 14 ~ 2, #somewhat negative
    COVID_social.12pp == 15 ~ 3, #no impact
    COVID_social.12pp == 16 ~ 4, #somewhat positive
    COVID_social.12pp == 17 ~ 5, #very positive
    .default = NA))
```

#### Recode `Mental Health`

```{r}
df <- df %>%
  mutate(COVID_mh.12pp = case_when(
    COVID_mh.12pp == -99 ~ NA, 
    .default = COVID_mh.12pp))
```

#### Recode `Parenting`

```{r}
df <- df %>%
  mutate(COVID_parenting.12pp = case_when(
    COVID_parenting.12pp == -99 ~ NA, 
    .default = COVID_parenting.12pp-1))
```

#### Recode `Work`

```{r}
df <- df %>%
  mutate(COVID_work.12pp = case_when(
    COVID_work.12pp == 5 ~ 3, #not currently working because pandemic
    COVID_work.12pp == 6 ~ 4, #on leave
    .default = COVID_work.12pp))
```

#### Recode `Contracted` & `Baby`

```{r}
df <- df %>%
  mutate(COVID_contracted.12pp = case_when(
    COVID_contracted.12pp == 1 ~ 1, #yes, tested
    COVID_contracted.12pp == 3 ~ 2, #yes, not tested
    COVID_contracted.12pp == 4 ~ 0, #no
    .default = NA)) %>%
  mutate(COVID_baby.12pp = case_when(
    COVID_baby.12pp == 3 ~ 0, #no
    .default = COVID_baby.12pp))
```

#### Recode `Open`

```{r}
df <- df %>%
  mutate(COVID_open.12pp = na_if(COVID_open.12pp, "-99"))
```
:::

### Label

#### Label `Precautions`

```{r}
# Define the labels with the new numbering (1-11)
vec_labels <- c(
  "Avoiding social gatherings" = 1,
  "Maintaining social distance" = 2,
  "Working from home" = 3,
  "Going outside only for essentials" = 4,
  "Cancelled or reduced medical care appointments" = 5,
  "Cancelled trips" = 6,
  "Cancelled events" = 7,
  "Changed hygiene habits" = 8,
  "Reduced baby's social contact with family" = 9,
  "Reduced baby's social contact with friends" = 10,
  "Other" = 11
)

# Apply labels
df <- df %>%
  mutate(across(COVID_precautions_1.12pp:COVID_precautions_11.12pp, ~as.numeric(.x))) %>%
  mutate(across(COVID_precautions_1.12pp:COVID_precautions_11.12pp, 
                ~ labelled(., 
                           labels = vec_labels,
                           label = "What precautions have you taken to avoid COVID-19 (multi-select)?"))) %>%
  mutate(COVID_precautions_text.12pp = labelled(COVID_precautions_text.12pp, label = "What precautions have you taken to avoid COVID-19 (open-ended for 'other')?"))
```

#### Label `Impact`

```{r}
# Define the labels with new numbering
vec_labels <- c(
  "Lost my job" = 1,
  "Changes to my job" = 2,
  "Changes in partner's employment" = 3,
  "Decrease in household income" = 4,
  "Changes in childcare arrangements" = 5,
  "Decreased number of in-person healthcare visits" = 6,
  "Worry about contracting COVID-19" = 7,
  "Worry about a family member's health" = 8,
  "Death of someone I am close to" = 9,
  "Loneliness" = 10,
  "Boredom" = 11
)

# Apply labels to COVID_impact without altering the original strings
df <- df %>%
  mutate(across(COVID_impact_1.12pp:COVID_impact_7.12pp, ~as.numeric(.x))) %>%
  mutate(across(COVID_impact_1.12pp:COVID_impact_7.12pp, 
                ~ labelled(., 
                           labels = vec_labels,
                           label = "What has occurred since your baby's birth as a result of COVID-19? (multi-select)")))
```

#### Label `Childcare`

```{r}
vec_labels <- c("I am spending more time taking care of my baby than previously planned" = 1, 
                "My partner is spending more time with my baby than previously planned" = 2, 
                "Someone else is spending more time with my baby than previously planned" = 3)

df <- df %>%
  mutate(across(contains("COVID_childcare"), ~as.numeric(.x))) %>%
  mutate(across(contains("COVID_childcare"), 
                ~ labelled(., 
                           labels = vec_labels,
                           label = "How have your childcare arrangements changed? (multi-select")))
```

#### Label `Contact`

```{r}
vec_labels <- c("Much less" = 1, 
                "Somewhat less" = 2, 
                "About the same" = 3, 
                "Somewhat more" = 4, 
                "Much more" = 5)

df <- df %>%
  mutate(COVID_contact1.12pp = 
           labelled(COVID_contact1.12pp, 
                    vec_labels, 
                    label = "Compared to before COVID, how much contact do you have with neighbors/community members?")) %>%
  mutate(COVID_contact2.12pp = 
           labelled(COVID_contact2.12pp, 
                    vec_labels, 
                    label = "Compared to before COVID, how much contact do you have with coworkers?")) %>%
  mutate(COVID_contact3.12pp = 
           labelled(COVID_contact3.12pp, 
                    vec_labels, 
                    label = "Compared to before COVID, how much contact do you have with close friends?")) %>%
  mutate(COVID_contact4.12pp = 
           labelled(COVID_contact4.12pp, 
                    vec_labels, 
                    label = "Compared to before COVID, how much contact do you have with your family?")) %>%
  mutate(COVID_contact5.12pp = 
           labelled(COVID_contact5.12pp, 
                    vec_labels, 
                    label = "Compared to before COVID, how much contact do you have with your partner?"))
  
```

#### Label `Social` & `Mental Health`

```{r}
vec_labels <- c("Very negative" = 1, 
                "Somewhat negative" = 2, 
                "No impact" = 3, 
                "Somewhat positive" = 4, 
                "Very positive" = 5)

df <- df %>%
  mutate(COVID_social.12pp = labelled(COVID_social.12pp, 
                                     vec_labels,
                                     label = "COVID's impact on your social relationships?")) %>%
  mutate(COVID_mh.12pp = labelled(COVID_mh.12pp, 
                                 vec_labels,
                                 label = "COVID's impact on your mental health"))
```

#### Label `Parenting` & `Work`

```{r}
df <- df %>%
  mutate(COVID_parenting.12pp = labelled(COVID_parenting.12pp, 
                                        c("Much worse" = 1, 
                                          "Slightly worse" = 2, 
                                          "No change" = 3, 
                                          "Slightly improved" = 4, 
                                          "Greatly improved" = 5), 
                                        label = "COVID's impact on experience of parenting")) %>%
  mutate(COVID_work.12pp = labelled(COVID_work.12pp, 
                                   c("Continuing work outside home" = 1, 
                                     "Working from home" = 2, 
                                     "Not working because of COVID" = 3, 
                                     "Not working because of parental leave" = 4), 
                                   label = "Current work situation"))
```

#### Label `Contracted` & `Baby` & `Open`

```{r}
vec_labels <- c("Yes, tested/diagnosed" = 1, 
                "Yes, not tested/diagnosed" = 2, 
                "No COVID" = 0)

df <- df %>%
  mutate(COVID_contracted.12pp = labelled(COVID_contracted.12pp, 
                                         vec_labels,
                                         label = "Have you contracted COVID-19 at any point since baby's birth?")) %>%
  mutate(COVID_baby.12pp = labelled(COVID_baby.12pp, 
                                   vec_labels, 
                                   label = "Has your baby contracted COVID-19?")) %>%
  mutate(COVID_open.12pp = labelled(COVID_open.12pp, label = "Open-ended about parenting during COVID"))
```

### Check and Print

:::: panel-tabset
#### Check

::: panel-tabset
##### Check Counts

```{r}
#| echo: false
# Precautions
check_categorical(df, contains("COVID_precautions") & !contains("text")) %>% arrange(value) %>% knitr::kable()

# Impact
check_categorical(df, COVID_impact_1.12pp:COVID_impact_7.12pp) %>% arrange(value) %>% knitr::kable()

# Childcare
check_categorical(df, contains("COVID_childcare")) %>% arrange(value) %>% knitr::kable()

# Contact
check_categorical(df, contains("COVID_contact")) %>% arrange(value) %>% knitr::kable()

# Social and Mental Health
check_categorical(df, (contains("COVID_social") | contains("COVID_mh"))) %>% arrange(value) %>% knitr::kable()

# Parenting
check_categorical(df, COVID_parenting.12pp) %>% arrange(value) %>% knitr::kable()

# Work
check_categorical(df, COVID_work.12pp) %>% arrange(value) %>% knitr::kable()

# Contract and Baby
check_categorical(df, c(COVID_contracted.12pp, COVID_baby.12pp)) %>% arrange(value) %>% knitr::kable()
```

##### Check Variable Labels

```{r}
#| echo: false
inspect_labels(df, contains("COVID")) 
```
:::

#### Print

```{r}
#| echo: false
print_slice(filter(df,!is.na(COVID_precautions_1.12pp)), contains("COVID"))
```
::::
::::::

# Finishing Up

::: panel-tabset
## Clean Up

```{r}
df <- df %>%
  # Re-order Columns
  relocate(c(
    
    # Demographics
    Parent:Future_child_partner.12pp,
    
    # Inventories 
    starts_with("ASQ"),
    starts_with("BCQ"),
    starts_with("BDI"),
    starts_with("COPE"), 
    starts_with("DAS"), 
    starts_with("ECR"), 
    starts_with("EPDS"), 
    starts_with("IBQR"),
    starts_with("IMS"), 
    starts_with("LAPR"),
    starts_with("MAI"), 
    starts_with("MAT"), 
    starts_with("MOS"), 
    starts_with("PAT"), 
    starts_with("PBQ"), 
    starts_with("PingSS"), 
    starts_with("PSI"), 
    starts_with("PSQI"), 
    starts_with("PSS"), 
    starts_with("SCL"), 
    
    # HATCH-Designed Questions
    starts_with("PRQ"),
    starts_with("COVID")), 
    
.after = CoupleID) %>%
  
  select(-test)

```

## Create Summary File

```{r}
df_sum <- df %>%
  select(
    
    # Demographics
    Parent:Future_child_partner.12pp,
    
    # Inventories
    ASQ12_comm.12pp:ASQ12_social.12pp,
    BCQ_structure.12pp, BCQ_attune.12pp,
    BDI_tot.12pp, 
    COPE_dist.12pp:COPE_blame.12pp,
    DAS_con.12pp:DAS_tot.12pp, 
    ECR_anx.12pp, ECR_avoid.12pp,
    EPDS_tot.12pp,
    IBQR_surgency.12pp:IBQR_effcontrol.12pp,
    IMS_satisfaction.12pp:IMS_commitment.12pp,
    LAPR_pur.12pp, LAPR_coh.12pp, LAPR_pmi.12pp,
    MAI_tot.12pp, 
    MAT_tot.12pp,
    MOS_emo.12pp:MOS_tot.12pp,
    PAT_ACF.12pp:PAT_PCF.12pp,
    PBQ_impaired.12pp:PBQ_abuse.12pp, 
    PingSS_tot.12pp, 
    PSI_dr.12pp:PSI_tot.12pp, 
    PSQI_global.12pp,
    PSS_tot.12pp, 
    SCL_som.12pp:SCL_psdi.12pp, 
    
    # HATCH-Designed Questionnaires
    starts_with("PRQ"),
    starts_with("COVID"))
```

## Write SAV Files

```{r}
write_sav(df, here("data/5_complete", "12pp_complete.sav"))
write_sav(df_sum, here("data/6_summary", "12pp_summary.sav"))
```
:::
