---
title: "6-Month Postpartum"
subtitle: "Rename Qualtrics Items"
format:
  html:
    toc: true
    toc-float: true
    df-print: paged
    code-folding: show
editor_options: 
  markdown: 
    wrap: 72
---

```{r include=FALSE}
knitr::opts_chunk$set(fig.width=2, fig.height=2, fig.align = "center")
```

# Set Up 
::: panel-tabset
## Packages
```{r load-pkg, message=FALSE, warning=FALSE}
library(tidyverse) # for data cleaning
library(here) # to quickly find data files
library(haven) # to manipulate SPSS files and add SPSS-style labels
library(chron) # to manipulate time and date variables
library(sjmisc) # for rowwise functions (row_count function)
library(data.table) # for renaming variables (setnames function)
library(kableExtra) # to print tables more neatly (kbl wrapping function) 
library(nestclean) # the package I wrote to help check our work
```


## Load Data
```{r load-data}
df <- read.csv(here("data/2_combined", "6pp_raw_combined.csv")) %>%
  mutate(across(where(is.character), ~ na_if(.x, ""))) %>% # Convert blanks to NA
  select(where(~ !all(is.na(.)))) # Remove empty columns
```
:::

# Demographics
::: panel-tabset
## Baby Weight
```{r}
# Set new names
setnames(df, 
         old = c("Baby.Weigh_1.6pp", "Baby.Weigh_2.6pp"),
         new = c("BabyWeight_lb.6pp", "BabyWeight_oz.6pp"))
```

## Age
```{r}
# Set new names
setnames(df, 
         old = c("Age_1.6pp"),
         new = c("Age.6pp"))
```

## Smoking
```{r}
# Set new names
setnames(df, 
         old = c("Packs.day_1.6pp", "Packs.day_2.6pp"),
         new = c("PackPerDay.6pp", "YearsSmoker.6pp"))
```

## Weight, Exercise, & Sleep
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="Weight_1.6pp"):which(colnames(df)=="Sleep_1.6pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "_1", replacement = "", x = colnames(df[,cols])))
```


## Breastfeeding
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="Breastfeed.6pp"):which(colnames(df)=="exclusive.6pp")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = c("BF_ever.6pp", "BF_current.6pp", "BF_length_months.6pp", "BF_length_day.6pp", "BF_exclusive.6pp"))
```

## Menstruation
```{r}
# Set new names
setnames(df, 
         old = c("Menstrual.6pp", "Q102.6pp"),
         new = c("Menstrual_start.6pp", "Menstrual_date.6pp"))
```

## Placenta
```{r}
# Set new names
setnames(df, 
         old = c("Placenta.6pp", "Q104.6pp"),
         new = c("Placenta_ingest.6pp", "Placenta_form.6pp"))
```


## Paid Leave and Childcare 
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="Q107.6pp"):which(colnames(df)=="Q109.6pp")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = c("Leave_time.6pp", "Leave_paid.6pp", "Childcare.6pp"))

# Move items
df <- df %>% relocate(Leave_time.6pp:Childcare.6pp, .after = Placenta_form.6pp)

```

## Check Demographics
```{r}
inspect_labels(df, CoupleID:Childcare.6pp) 
```
:::



# Inventories
::: panel-tabset
## AAS: Adult Attachment Scale
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="AAS_1.6pp"):which(colnames(df)=="AAS_18.6pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "_", replacement = "", x = colnames(df[,cols])))
```

## ASQ: Ages and Stages Questionnaire, 6-month
::: panel-tabset
### Communication (c)
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q122_1.6pp"):which(colnames(df)=="Q122_6.6pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("ASQ6_c", 1:6, ".6pp", sep = ""))
```

### Gross Motor (gm)
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q122_7.6pp"):which(colnames(df)=="Q122_12.6pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("ASQ6_gm", 1:6, ".6pp", sep = ""))
```

### Fine Motor (fm)
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q122_13.6pp"):which(colnames(df)=="Q122_18.6pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("ASQ6_fm", 1:6, ".6pp", sep = ""))
```

### Probem Solving (ps)
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q122_19.6pp"):which(colnames(df)=="Q122_24.6pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("ASQ6_ps", 1:6, ".6pp", sep = ""))
```

### Personal/Social (s)
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q122_25.6pp"):which(colnames(df)=="Q122_30.6pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("ASQ6_s", 1:6, ".6pp", sep = ""))
```

### Overall
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q123_1.6pp"):which(colnames(df)=="Q123_8.6pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("ASQ6_o", 1:8, ".6pp", sep = ""))
```
:::

## BCQ: Baby Care Questionnaire
### Sleep
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q94_1.6pp"):which(colnames(df)=="Q94_9.6pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("BCQ_S", c(1:9), ".6pp", sep = ""))
```

### Eating
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q94_10.6pp"):which(colnames(df)=="Q94_19.6pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("BCQ_E", c(1:3, 6, 7, 10, 4, 5, 8, 9), ".6pp", sep = ""))

# Reorder variables
df <- df %>%
  relocate(BCQ_E4.6pp, BCQ_E5.6pp, BCQ_E6.6pp, BCQ_E7.6pp, BCQ_E8.6pp, BCQ_E9.6pp, BCQ_E10.6pp, .after = BCQ_E3.6pp)
```

### Soothing
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q94_20.6pp"):which(colnames(df)=="Q94_30.6pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("BCQ_So", c(1, 2, 4, 9, 10, 3, 5:8, 11), ".6pp", sep = ""))

# Reorder variables
df <- df %>%
  relocate(BCQ_So3.6pp, BCQ_So4.6pp, BCQ_So5.6pp:BCQ_So8.6pp, BCQ_So9.6pp, BCQ_So10.6pp, BCQ_So11.6pp, .after = BCQ_So2.6pp)
```

### Check
```{r}
inspect_labels(df, contains("BCQ"))
```


## BDI: Beck Depression Inventory
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="BDI1_Sad.6pp"):which(colnames(df)=="BDI21_Sex.6pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("BDI", c(1:8, 10:21), ".6pp", sep = ""))
```

## COPE: Brief Cope
```{r COPE-rename}
# Get Column Numbers
cols <- which(colnames(df)=="COPE_1.6pp"):which(colnames(df)=="COPE_28.6pp")
# Set New Names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "_", replacement = "", x = colnames(df[,cols])))
```


## DAS: Dyadic Adjustment Scale
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="DAS1.15_1.6pp"):which(colnames(df)=="DAS.32.6pp")

# Set New Names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("DAS", 1:32, ".6pp", sep = ""))
```


## EPDS: Edinburgh Postnatal Depression Scale
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="PDS_1.6pp"):which(colnames(df)=="PDS_9.6pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "PDS_", replacement = "EPDS", x = colnames(df[,cols])))
```

## IBQR: Infant Behavior Questionnaire—Revised
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q87_1.6pp"):which(colnames(df)=="Q87_37.6pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "Q87_", replacement = "IBQR", x = colnames(df[,cols])))
```

## ISS: Index of Sexual Satisfaction
```{r ISS-rename}
# Get Column Numbers
cols <- which(colnames(df)=="Q89_1.6pp"):which(colnames(df)=="Q89_25.6pp")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "Q89_", replacement = "ISS", x = colnames(df[,cols])))
```

## LAPR: Life Attitudes Profile—Revised
```{r LAP-R-rename}
# Get Column Numbers
cols <- which(colnames(df)=="PMI_1.6pp"):which(colnames(df)=="PMI_16.6pp")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("LAPR",
                     c(1, 2, 5, 7, 12, 16,
                       18, 26, 27, 29, 31, 35, 
                       37, 38, 46, 48), 
                     ".6pp", sep = ""))
```

## MAI: Maternal Attachment Inventory
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="Q128_1.6pp"):which(colnames(df)=="Q128_26.6pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("MAI", c(1:26), ".6pp", sep = ""))
```

## MAT: Marital Adjustment Test
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="MAT_1.6pp"):which(colnames(df)=="MAT_15.6pp")

# Set New Names
setnames(df, 
         old = colnames(df[,cols]), 
         new = 
           c(paste("MAT", 1:11, ".6pp", sep = ""),
             "MAT12a.6pp", "MAT12b.6pp",
             paste("MAT", 13:15, ".6pp", sep = "")))
```


## PBQ: Postpartum Bonding Questionnaire
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q107_1.6pp"):which(colnames(df)=="Q107_25.6pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "Q107_", replacement = "PBQ", x = colnames(df[,cols])))
```

## PingSS: Parenting Stress Scale
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="PingSS_1.6pp"):which(colnames(df)=="PingSS_18.6pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "_", replacement = "", x = colnames(df[,cols])))
```

## PSI: Parenting Stress Index
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="PSI_1.6pp"):which(colnames(df)=="PSI_33.1.6pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("PSI", c(1:21, 23:31, 34:36, 22, 32, 33), ".6pp", sep = ""))

# Reorder variables
df <- df %>%
  relocate(c(PSI22.6pp, PSI23.6pp:PSI31.6pp, PSI32.6pp, PSI33.6pp), .after = PSI21.6pp)
```


## PSQI: Pittsburgh Sleep Quality Index
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="Q114.6pp"):which(colnames(df)=="Q121.6pp")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = c(
           # Questions 1-4
           paste("PSQI", 1:4, ".6pp", sep = ""),
           # Questions 5a-5j
           paste("PSQI", "5", letters[1:10], ".6pp", sep = ""), 
           # Questions 6-9
           paste("PSQI", c(9, 6:8), ".6pp", sep = "")))

# Relocate question 9 to be in the correct order
df <- df %>%
  relocate(PSQI9.6pp, .after = PSQI8.6pp)
```

## PSS: Perceived Stress Scale
```{r PSS-rename}
# Get Column Numbers
cols <- which(colnames(df)=="PSS_1.6pp"):which(colnames(df)=="PSS_14.6pp")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "_", replacement = "", x = colnames(df[,cols])))
```



## PYB: Parenting Your Baby
- Formerly "PARYC: Parenting Young Children"
- Per Darby in 2/28 Slack to Lizzie: 
  + Subscales are planning ahead (pa) and supporting/enjoying your baby (se)
  + Qualtrics has one additional item, which was dropped by the authors after factor analysis
 
```{r }
# Get Column Numbers
cols <- which(colnames(df)=="Q108.1_1.6pp"):which(colnames(df)=="Q112_1.6pp")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = c(
           # Supporting and Enjoying
           paste("PYB_se", 1:8, ".6pp", sep = ""),
           paste("PYB_se", "_change", ".6pp", sep = ""),
           paste("PYB_pa", 1:5, ".6pp", sep = ""),
           paste("PYB_pa", "_extra", ".6pp", sep = ""), # item deleted from final 2023 measure
           paste("PYB_pa", 6:8, ".6pp", sep = ""),
           paste("PYB_pa", "_change", ".6pp", sep = "")))

# Move "extra" to end
df <- df %>%
  relocate(PYB_pa_extra.6pp, .after = PYB_pa_change.6pp)
```


## SCL: Symptom Checklist 90
- in the 6pp version, #87 and #88 have been accidentally combined to read "The idea that something serious is wrong with your body ever feeling close to another person"
- we will treat that item as #87 ("The idea that something serious is wrong with your body")
- "Thoughts and images of a frightening nature (83)" replaces "feeling pushed to get things done (86)"
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="SCL90_1.6pp"):which(colnames(df)=="SCL90_86.6pp")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("SCL", c(1:14, # rename 1-14; remove 15
                              16:58, # rename 16-58; remove 59
                              60:62, # rename 60-62; remove 63
                              64:86, # rename 64-90; remove 87
                              88:90), 
                     ".6pp", sep = ""))

```

## STAI: State-Trait Anxiety Scale (State only)
- 6pp only includes "State"
```{r STAI-rename}
# Get Column Numbers
cols <- which(colnames(df)=="STAI_State_1.6pp"):which(colnames(df)=="STAI_State_20.6pp")

# Set new names (State)
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "State_", replacement = "s", x = colnames(df[,cols])))
```

# HATCH-Designed Questions


## COVID Parenting Questions
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q136.6pp"):which(colnames(df)=="Q146.6pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = c("COVID_precautions.6pp",
                 "COVID_precautions_text.6pp",
                 "COVID_impact.6pp", 
                 "COVID_childcare.6pp", 
                 paste("COVID_contact", 1:5, ".6pp", sep = ""), 
                 "COVID_social.6pp", 
                 "COVID_mh.6pp", 
                 "COVID_parenting.6pp", 
                 "COVID_work.6pp", 
                 "COVID_contracted.6pp", 
                 "COVID_baby.6pp", 
                 "COVID_open.6pp"))


```

## PRQ: Parenting Responsibilities Questionnaire
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q131.6pp"):which(colnames(df)=="Q135.6pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = c("PRQ_WeekTot.6pp", 
                 "PRQ_WeekPrimary.6pp", 
                 "PRQ_WkendTot.6pp", 
                 "PRQ_WkendPrimary.6pp", 
                 "PRQ_Share.6pp"))
```

## Life Experiences 
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q124.6pp"):which(colnames(df)=="Q126.6pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = c("LifeExperience_Occur.6pp", 
                 "LifeExperience_Describe.6pp", 
                 "LifeExperience_Impact.6pp"))
```
:::

# HATCH Questionnaires
```{r}
inspect_labels(df, c(contains("COVID"), contains("PRQ"), contains("LifeExperience"), -contains("MRI")))
```
:::


# COVID MRI Questions
::: panel-tabset
## General and PRQ
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="VisitDate_covidMRI.6pp"):which(colnames(df)=="Q11_covidMRI.6pp")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = c("MRI_VisitDate.6pp", 
                 "MRI_LiveWBaby.6pp", "MRI_SeeBaby.6pp", 
                 "MRI_PRQ_WeekTot.6pp", 
                 "MRI_PRQ_WeekPrimary.6pp", 
                 "MRI_PRQ_WkendTot.6pp", 
                 "MRI_PRQ_WkendPrimary.6pp", 
                 "MRI_PRQ_Share.6pp", 
                 "MRI_Cry.6pp", 
                 "MRI_SleepTrain.6pp", "MRI_SleepTrainAge.6pp", "MRI_SleepTrainDays.6pp"))
```

## PSQI
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="Q24_covidMRI.6pp"):which(colnames(df)=="Q31_covidMRI.6pp")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = c(
           # Questions 1-4
           paste("MRI_PSQI", 1:4, ".6pp", sep = ""),
           # Questions 5a-5j
           paste("MRI_PSQI", "5", letters[1:10], ".6pp", sep = ""), 
           # Questions 6-9
           paste("MRI_PSQI", c(9, 6:8), ".6pp", sep = "")))

# Relocate question 9 to be in the correct order
df <- df %>%
  relocate(MRI_PSQI9.6pp, .after = MRI_PSQI8.6pp)
```

## PYB: Parenting Your Baby
- Formerly "PARYC: Parenting Young Children"
- Per Darby in 2/28 Slack to Lizzie: 
  + Subscales are planning ahead (pa) and supporting/enjoying your baby (se)
  + Qualtrics has one additional item, which was dropped by the authors after factor analysis
 
```{r }
# Get Column Numbers
cols <- which(colnames(df)=="Q40.1_1_covidMRI.6pp"):which(colnames(df)=="Q43_1_covidMRI.6pp")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = c(
           # Supporting and Enjoying
           paste("MRI_PYB_se", 1:8, ".6pp", sep = ""),
           paste("MRI_PYB_se", "_change", ".6pp", sep = ""),
           paste("MRI_PYB_pa", 1:5, ".6pp", sep = ""),
           paste("MRI_PYB_pa", "_extra", ".6pp", sep = ""), # item deleted from final 2023 measure
           paste("MRI_PYB_pa", 6:8, ".6pp", sep = ""),
           paste("MRI_PYB_pa", "_change", ".6pp", sep = "")))

# Move "extra" to end
df <- df %>%
  relocate(MRI_PYB_pa_extra.6pp, .after = MRI_PYB_pa_change.6pp)
```
 

## Household Composition
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="Q13_covidMRI.6pp"):which(colnames(df)=="Q17_covidMRI.6pp")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = c("MRI_RelStat.6pp", 
                 "MRI_Household.6pp", 
                 "MRI_HouseholdN.6pp"))
```

## COVID Parenting Questions
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q19_1_covidMRI.6pp"):which(colnames(df)=="Q33_covidMRI.6pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = c(paste("MRI_COVID_contact", 1:5, ".6pp", sep = ""), 
                 "MRI_COVID_social.6pp", 
                 "MRI_COVID_impact.6pp", 
                 "MRI_COVID_mh.6pp",
                 "MRI_COVID_precautions.6pp",
                 "MRI_COVID_precautions_intensity.6pp",
                 "MRI_COVID_contracted.6pp"))


```
:::

# Finishing up 
::: panel-tabset
## Reorder alphabetically
```{r}
df <- df %>%
  relocate(
    contains("AAS"), 
    contains("ASQ"), 
    contains("BCQ"), 
    contains("BDI"), 
    contains("COPE"), 
    contains("DAS"), 
    contains("EPDS"), 
    contains("IBQR"), 
    contains("ISS"), 
    contains("LAPR"), 
    contains("MAI"), 
    contains("MAT"), 
    contains("PARYC") & !contains("MRI"), 
    contains("PBQ"), 
    contains("PingSS"), 
    contains("PSI"), 
    contains("PSQI")& !contains("MRI"), 
    contains("PSS"), 
    contains("SCL"), 
    contains("STAI"), 
    
    # HATCH Items
    contains("COVID") & !contains("MRI"), 
    contains("PRQ") & !contains("MRI"), 
    contains("LifeExperience"), 
    
    # MRI COVID Items
    contains("COVID") & !contains("MRI"), 
    contains("PRQ"), 
    contains("LifeExperience"), 
    MRI_VisitDate.6pp:MRI_SleepTrainDays.6pp, 
    MRI_RelStat.6pp:MRI_HouseholdN.6pp,
    contains("MRI_PARYC"), 
    contains("MRI_PRQ"), 
    contains("MRI_PSQI"), 
    contains("MRI_COVID"),
    
    
    .after = Childcare.6pp
  )
```



## Check for unnamed 
```{r}
inspect_labels(df, Placenta_form.6pp:ncol(df))
#sinspect_labels(df, starts_with("Q"))
```

## Write CSV Files
```{r}
write_sav(df, here("data/3_renamed", "6pp_renamed.sav"))
```
:::


