---
title: "12-Month Postpartum"
subtitle: "Rename Qualtrics Items"
format:
  html:
    toc: true
    toc-float: true
    df-print: paged
    code-folding: show
editor_options: 
  markdown: 
    wrap: 72
---

```{r include=FALSE}
knitr::opts_chunk$set(fig.width=2, fig.height=2, fig.align = "center")
```


# Set Up 
::: panel-tabset
## Packages
```{r load-pkg, message=FALSE, warning=FALSE}
library(tidyverse) # for data cleaning
library(here) # to quickly find data files
library(haven) # to manipulate SPSS files and add SPSS-style labels
library(chron) # to manipulate time and date variables
library(sjmisc) # for rowwise functions (row_count function)
library(data.table) # for renaming variables (setnames function)
library(kableExtra) # to print tables more neatly (kbl wrapping function) 
library(nestclean) # the package I wrote to help check our work
```

## Load Data
```{r load-data}
df <- read.csv(here("data/2_combined", "12pp_raw_combined.csv")) %>%
  mutate(across(where(is.character), ~ na_if(.x, ""))) %>%
  select(where(~ !all(is.na(.)))) %>% # Remove empty columns
  select(-contains("Birthdate_1")) # not sure what these items are or where they're from
```
:::

# Demographics
::: panel-tabset
## Baby Weight
```{r}
# Set new names
setnames(df, 
         old = c("Baby.Weigh_1.12pp", "Baby.Weigh_2.12pp"),
         new = c("BabyWeight_lb.12pp", "BabyWeight_oz.12pp"))
```

## Age
```{r}
# Set new names
setnames(df, 
         old = c("Age_1.12pp"),
         new = c("Age.12pp"))
```

## Smoking
```{r}
# Set new names
setnames(df, 
         old = c("Packs.day_1.12pp", "Packs.day_2.12pp"),
         new = c("PackPerDay.12pp", "YearsSmoker.12pp"))
```

## Weight, Exercise, & Sleep
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="Weight_1.12pp"):which(colnames(df)=="Sleep_1.12pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "_1", replacement = "", x = colnames(df[,cols])))
```


## Breastfeeding
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="Breastfeed.12pp"):which(colnames(df)=="Q114.12pp")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = c("BF_ever.12pp", "BF_current.12pp", "BF_length.12pp", "BF_exclusive.12pp", "BF_plan.12pp", "BF_satisfied.12pp"))
```

## Menstruation
```{r}
# Set new names
setnames(df, 
         old = c("Menstrual.12pp", "Q102.12pp"),
         new = c("Menstrual_start.12pp", "Menstrual_date.12pp"))
```

## Placenta
```{r}
# Set new names
setnames(df, 
         old = c("Placenta.12pp", "Q105.12pp"),
         new = c("Placenta_ingest.12pp", "Placenta_form.12pp"))
```


## Paid Leave and Childcare ("Addition to postpartum survey")
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="Leave.12pp"):which(colnames(df)=="Q119.12pp")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = c("Leave_type.12pp", "Leave_time.12pp", "Leave_satisfied.12pp", "Leave_open.12pp"))
```

## Future children
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="Q120.12pp"):which(colnames(df)=="Q121.12pp")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = c("Future_child.12pp", "Future_child_partner.12pp"))
```

## Check Demographics 
::: panel-tabset
### Check Names
```{r}
inspect_labels(df, CoupleID:Future_child_partner.12pp) 
```

### Print
```{r eval = knitr::is_html_output(), echo = FALSE}
print_slice(df, CoupleID:Leave_open.12pp)
```
:::
:::

# Inventories
::: panel-tabset
## ASQ12: Ages and Stages Questionnaire, 12-month
::: panel-tabset
### Communication (c)
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q106_1.12pp"):which(colnames(df)=="Q106_6.12pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("ASQ12_c", 1:6, ".12pp", sep = ""))
```

### Gross Motor (gm)
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q106_7.12pp"):which(colnames(df)=="Q106_12.12pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("ASQ12_gm", 1:6, ".12pp", sep = ""))
```

### Fine Motor (fm)
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q106_13.12pp"):which(colnames(df)=="Q106_18.12pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("ASQ12_fm", 1:6, ".12pp", sep = ""))
```

### Probem Solving (ps)
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q106_19.12pp"):which(colnames(df)=="Q106_24.12pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("ASQ12_ps", 1:6, ".12pp", sep = ""))
```

### Personal/Social (s)
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q106_25.12pp"):which(colnames(df)=="Q106_30.12pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("ASQ12_s", 1:6, ".12pp", sep = ""))
```

### Overall
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q107.12pp"):which(colnames(df)=="Q116.1.12pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("ASQ12_o", 1:9, ".12pp", sep = ""))
```

### Check
```{r}
inspect_labels(df, contains("ASQ"))
```
:::

## BCQ: Baby Care Questionnaire
### Sleep
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q94_1.12pp"):which(colnames(df)=="Q94_9.12pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("BCQ_S", c(1:9), ".12pp", sep = ""))
```

### Eating
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q94_10.12pp"):which(colnames(df)=="Q94_19.12pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("BCQ_E", c(1:3, 6, 7, 10, 4, 5, 8, 9), ".12pp", sep = ""))

# Reorder variables
df <- df %>%
  relocate(BCQ_E4.12pp, BCQ_E5.12pp, BCQ_E6.12pp, BCQ_E7.12pp, BCQ_E8.12pp, BCQ_E9.12pp, BCQ_E10.12pp, .after = BCQ_E3.12pp)
```

### Soothing
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q94_20.12pp"):which(colnames(df)=="Q94_30.12pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("BCQ_So", c(1, 2, 4, 9, 10, 3, 5:8, 11), ".12pp", sep = ""))

# Reorder variables
df <- df %>%
  relocate(BCQ_So3.12pp, BCQ_So4.12pp, BCQ_So5.12pp:BCQ_So8.12pp, BCQ_So9.12pp, BCQ_So10.12pp, BCQ_So11.12pp, .after = BCQ_So2.12pp)
```

## BDI: Beck Depression Inventory
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="BDI1_Sad.12pp"):which(colnames(df)=="BDI21_Sex.12pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("BDI", c(1:8, 10:21), ".12pp", sep = ""))
```

## COPE: Brief Cope
```{r COPE-rename}

# Get Column Numbers
cols <- which(colnames(df)=="Q121_1.12pp"):which(colnames(df)=="Q121_28.12pp")
# Set New Names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "Q121_", replacement = "COPE", x = colnames(df[,cols])))
```

## DAS: Dyadic Adjustment Scale
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="DAS1.15_1.12pp"):which(colnames(df)=="DAS.32.12pp")

# Set New Names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("DAS", 1:32, ".12pp", sep = ""))
```


## ECR: Experiences in Close Relationships
```{r ECR-R-rename}
# Get Column Numbers
cols <- which(colnames(df)=="Q97_1.12pp"):which(colnames(df)=="Q97_36.12pp")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "Q97_", replacement = "ECR", x = colnames(df[,cols])))
```




## EPDS: Edinburgh Postnatal Depression Scale
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="PDS_1.12pp"):which(colnames(df)=="PDS_9.12pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "PDS_", replacement = "EPDS", x = colnames(df[,cols])))
```



## IBQR: Infant Behaviora Questionnaire—Revised
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q87_1.12pp"):which(colnames(df)=="Q87_37.12pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "Q87_", replacement = "IBQR", x = colnames(df[,cols])))
```
## IMS: Investment Model Scale (new)
### Satisfaction (s)
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="Q107_1.1.12pp"):which(colnames(df)=="Q108_5.1.12pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = c(
           # Facet Questions 1a-1e
           paste("IMS_sat_facet_", letters[1:5], ".12pp", sep = ""),
           # Global Questions 2-6
           paste("IMS", 1:5, ".12pp", sep = "")))
```

### Alternatives (a)
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="Q109_1.12pp"):which(colnames(df)=="Q110_5.12pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = c(
           # Facet Questions 1a-1e
           paste("IMS_alt_facet_", letters[1:5], ".12pp", sep = ""),
           # Global Questions 2-6
           paste("IMS", 6:10, ".12pp", sep = "")))
```

### Investment (i)
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="Q111_1.12pp"):which(colnames(df)=="Q112_5.12pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = c(
           # Facet Questions 1a-1e
           paste("IMS_inv_facet_", letters[1:5], ".12pp", sep = ""),
           # Global Questions 2-6
           paste("IMS", 11:15, ".12pp", sep = "")))
```

### Committment (c)
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="Q112_6.12pp"):which(colnames(df)=="Q112_12.12pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("IMS", 16:22, ".12pp", sep = ""))
```

### Check
```{r}
inspect_labels(df, contains("IMS"))
```



## LAPR: Life Attitudes Profile—Revised
```{r LAP-R-rename}
# Get Column Numbers
cols <- which(colnames(df)=="Q123_1.12pp"):which(colnames(df)=="Q123_16.12pp")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("LAPR",
                     c(1, 2, 5, 7, 12, 16,
                       18, 26, 27, 29, 31, 35, 
                       37, 38, 46, 48), 
                     ".12pp", sep = ""))
```






## MAI: Maternal Attachment Inventory
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="Q107_1.12pp"):which(colnames(df)=="Q107_26.12pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("MAI", c(1:26), ".12pp", sep = ""))
```

## MAT: Marital Adjustment Test
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="MAT_1.12pp"):which(colnames(df)=="MAT_15.12pp")

# Set New Names
setnames(df, 
         old = colnames(df[,cols]), 
         new = 
           c(paste("MAT", 1:11, ".12pp", sep = ""),
             "MAT12a.12pp", "MAT12b.12pp",
             paste("MAT", 13:15, ".12pp", sep = "")))
```

## MOS: MOS Social Support
```{r MOS-rename}
# Get Column Numbers
cols <- which(colnames(df)=="Q103_1.12pp"):which(colnames(df)=="Q103_19.12pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "Q103_", replacement = "MOS", x = colnames(df[,cols])))
```

## PAT: Parental Attribution Test
- The item numbers (1a-1f and 2a-2l) on our item list do not correspond to the author scoring information
        - Doesn't matter for US scale, where all 6 items are from #1 and are direct coded
        - 2a-2l get recoded as 2b-2d, 2f, 2i-2k, 2m, 2q, 2t, 2u, 2z
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="Q122_1.12pp"):which(colnames(df)=="Q123_12.1.12pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = c(paste("PAT1", letters[1:6], ".12pp", sep = ""),
                 paste("PAT2", c("b", "c", "d", "f", "i", "j", "k", "m", "q", "t", "u", "z"), ".12pp", sep = "")))
```

## PBQ: Postpartum Bonding Questionnaire
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q119_1.12pp"):which(colnames(df)=="Q119_25.12pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "Q119_", replacement = "PBQ", x = colnames(df[,cols])))
```

## PingSS: Parenting Stress Scale
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="PingSS_1.12pp"):which(colnames(df)=="PingSS_18.12pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "_", replacement = "", x = colnames(df[,cols])))
```

## PSI: Parenting Stress Index
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="PSI_1.12pp"):which(colnames(df)=="PSI_33.1.12pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("PSI", c(1:21, 23:31, 34:36, 22, 32, 33), ".12pp", sep = ""))

# Reorder variables
df <- df %>%
  relocate(c(PSI22.12pp, PSI23.12pp:PSI31.12pp, PSI32.12pp, PSI33.12pp), .after = PSI21.12pp)
```


## PSQI: Pittsburgh Sleep Quality Index
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="Q100.12pp"):which(colnames(df)=="Q114.2.12pp")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = c(
           # Questions 1-4
           paste("PSQI", 1:4, ".12pp", sep = ""),
           # Questions 5a-5j
           paste("PSQI", "5", letters[1:10], ".12pp", sep = ""), 
           # Questions 6-9
           paste("PSQI", c(9, 6:8), ".12pp", sep = "")))

# Relocate question 9 to be in the correct order
df <- df %>%
  relocate(PSQI9.12pp, .after = PSQI8.12pp)
```


## PSS: Perceived Stress Scale
```{r PSS-rename}
# Get Column Numbers
cols <- which(colnames(df)=="PSS_1.12pp"):which(colnames(df)=="PSS_14.12pp")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "_", replacement = "", x = colnames(df[,cols])))
```


## SCL: Symptoms Checklist 90
- in the 12pp version, #87 and #88 have been accidentally combined to read "The idea that something serious is wrong with your body ever feeling close to another person"
- we will treat that item as #87 ("The idea that something serious is wrong with your body")
- "Thoughts and images of a frightening nature (83)" replaces "feeling pushed to get things done (86)"
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="SCL90_1.12pp"):which(colnames(df)=="SCL90_86.12pp")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("SCL", c(1:14, # rename 1-14; remove 15
                              16:58, # rename 16-58; remove 59
                              60:62, # rename 60-62; remove 63
                              64:86, # rename 64-90; remove 87
                              88:90), 
                     ".12pp", sep = ""))

```
:::

# HATCH-Designed Questions
::: panel-tabset
## PRQ: Parenting Responsibilities Questionnaire
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q153.12pp"):which(colnames(df)=="Q157.12pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = c("PRQ_WeekTot.12pp", 
                 "PRQ_WeekPrimary.12pp", 
                 "PRQ_WkendTot.12pp", 
                 "PRQ_WkendPrimary.12pp", 
                 "PRQ_Share.12pp"))
```

## COVID Parenting Questions
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q167.12pp"):which(colnames(df)=="Q143.12pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = c("COVID_precautions.12pp",
                 "COVID_precautions_text.12pp",
                 "COVID_impact.12pp", 
                 "COVID_childcare.12pp", 
                 paste("COVID_contact", 1:5, ".12pp", sep = ""), 
                 "COVID_social.12pp", 
                 "COVID_mh.12pp", 
                 "COVID_parenting.12pp", 
                 "COVID_work.12pp", 
                 "COVID_contracted.12pp", 
                 "COVID_baby.12pp", 
                 "COVID_open.12pp"))
```




## Check HATCH Questionnaires
```{r}
inspect_labels(df, c(contains("COVID"), contains("PRQ"), contains("Future"), -contains("MRI")))
```

:::

# Finishing up 
::: panel-tabset
## Reorder alphabetically
```{r}
df <- df %>%
  relocate(
    contains("ASQ"), 
    contains("BCQ"), 
    contains("BDI"), 
    contains("COPE"), 
    contains("DAS"),
    contains("ECR"), 
    contains("EPDS"), 
    contains("IBQR"), 
    contains("IMS"), 
    contains("LAPR"), 
    contains("MAI"), 
    contains("MAT"),
    contains("MOS"), 
    contains("PAT"),
    contains("PBQ"), 
    contains("PingSS"), 
    contains("PSI"), 
    contains("PSQI"), 
    contains("PSS"), 
    contains("SCL"), 
    
    # HATCH Items
    contains("COVID"),
    contains("PRQ"),
    
    
    .after = Future_child_partner.12pp
  )
```



## Check for unnamed 
```{r}
inspect_labels(df, Future_child_partner.12pp:ncol(df))
#inspect_labels(df, starts_with("Q"))
```

## Write CSV Files
```{r}
write_sav(df, here("data/3_renamed", "12pp_renamed.sav"))
```

:::

