---
title: "Prenatal"
subtitle: "Rename Qualtrics Items"
format:
  html:
    toc: true
    toc-float: true
    df-print: paged
    code-folding: show
editor_options: 
  markdown: 
    wrap: 72
---

```{r include=FALSE}
knitr::opts_chunk$set(fig.width=2, fig.height=2, fig.align = "center")
```

# Set Up

::: panel-tabset
## Packages

```{r load-pkg, message=FALSE, warning=FALSE}
library(tidyverse) # for data cleaning
library(here) # to quickly find data files
library(haven) # to manipulate SPSS files and add SPSS-style labels
library(chron) # to manipulate time and date variables
library(sjmisc) # for rowwise functions (row_count function)
library(data.table) # for renaming variables (setnames function)
library(kableExtra) # to print tables more neatly (kbl wrapping function) 
library(nestclean) # the package I wrote to help check our work
```

## Load Data

```{r load-data}
df <- read.csv(here("data/2_combined", "0pn_raw_combined.csv")) 

# Add blank rows for missing data
df <- df %>%
  add_row(CoupleID = 73, Parent = "mom") %>%
  arrange(CoupleID) 
```
:::

# Demographics

::::::: panel-tabset
## Full-Sample Variables

::: panel-tabset
### Reorder Full-Sample Columns

```{r}
df <- relocate(df, 
                  c(Parent, 
                    DueDate, VisitDate.pn, RelStat.pn, # Couple-Level variables
                    Ethnicity, Education,  starts_with("Height"),   # Time-stable individual variables
                    starts_with("Weight"), Age.pn, # Time-variable individual variables
                    starts_with("Exercise"), starts_with("Sleep"), starts_with("Smoker"), starts_with("Packperday"),
                    starts_with("Illnesses")), 
                  .after = "CoupleID")
```

### Rename `Education` Column

```{r}
setnames(df, 
         old = "Education", 
         new = "Education.pn")
```

### Rename `Illnesses` Columns

```{r}
## Get Column Numbers
cols.type <- which(colnames(df)=="Illnesses.1_1_1.pn"):which(colnames(df)=="Illnesses.1_7_1.pn")
cols.cur <- which(colnames(df)=="Illnesses.2_1.pn"):which(colnames(df)=="Illnesses.2_7.pn")

## Set new names
setnames(df, 
         old = colnames(df[,cols.type]), 
         new = paste("Illness", 1:7, ".pn", sep = ""))
setnames(df, 
         old = colnames(df[,cols.cur]), 
         new = paste("Illness", 1:7, "_current.pn", sep = ""))
```

### Rename `Exercise` and `Sleep` Columns

```{r}
## Get Column Numbers
cols <- which(colnames(df)=="Exercise_1.pn"):which(colnames(df)=="Sleep_1.pn")
## Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "_1", replacement = "", x = colnames(df[,cols])))
```

### Rename `Smoking` Columns

```{r}
## Get Column Numbers
cols <- which(colnames(df)=="Packperday_4.pn"):which(colnames(df)=="Packperday_7.pn")
## Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = c("PackPerDay.pn", "YearsSmoker.pn", "Drugs.pn", "DrugFrequency.pn"))
```
:::

## Later additions to demographics variables

::: panel-tabset
### Batch rename

```{r}
# Get Column Numbers
cols <- which(colnames(df)=="Q125.pn"):which(colnames(df)=="Q136.pn")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = c("Preg_Planned.pn", "Paid_Leave.pn", "Time_Off.pn", "Income.pn", 
                 "Born_US.pn", "Origin_Country.pn", "Immigration_Age.pn", 
                 "Occupation_Status.pn", "Occupation.pn", "Insurance_Status.pn"))
```

### Reorder

```{r}
df <- relocate(df, 
                  c(Born_US.pn, Origin_Country.pn, Immigration_Age.pn, 
                    Preg_Planned.pn, Paid_Leave.pn, Time_Off.pn, 
                    Income.pn, Occupation_Status.pn, Occupation.pn, Insurance_Status.pn),
                  .before = Illness1.pn)
```
:::

## Check Demographics

::: panel-tabset
### Check Names

```{r}
inspect_labels(df, CoupleID:Illness7_current.pn) 
```

### Print

```{r eval = knitr::is_html_output(), echo = FALSE}
print_slice(df, CoupleID:Insurance_Status.pn)
```
:::
:::

# Inventories

::: panel-tabset
## AAS: Adult Attachment Scale

```{r AAS-rename}
# Get Column Numbers
cols <- which(colnames(df)=="AAS_1.pn"):which(colnames(df)=="AAS_18.pn")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "_", replacement = "", x = colnames(df[,cols])))
```

## BDI: Beck Depression Inventory

```{r BDI-rename}
# Get Column Numbers
cols <- which(colnames(df)=="BDI1_Sad.pn"):which(colnames(df)=="BDI21_Sex.pn")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("BDI", c(1:8, 10:21), ".pn", sep = ""))
```

## BFI: Big Five Inventory

```{r BFI-rename}
# Get Column Numbers
cols <- which(colnames(df)=="BFI_2_1.pn"):which(colnames(df)=="BFI_2_44.pn")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "_2_", replacement = "", x = colnames(df[,cols])))
```

## COPE: Brief Cope

```{r COPE-rename}

# Get Column Numbers
cols <- which(colnames(df)=="COPE_1.pn"):which(colnames(df)=="COPE_28.pn")
# Set New Names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "_", replacement = "", x = colnames(df[,cols])))
```

## DAS: Dyadic Adjustment Scale

```{r DAS-rename}
# Get Column Numbers
cols <- which(colnames(df)=="DAS1.15_1.pn"):which(colnames(df)=="DAS.32.pn")

# Set New Names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("DAS", 1:32, ".pn", sep = ""))
```

## ECR-R: Experiences in Close Relationships

```{r ECR-R-rename}
# Get Column Numbers
cols <- which(colnames(df)=="ECR.R_1.pn"):which(colnames(df)=="ECR.R_36.pn")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = ".R_", replacement = "", x = colnames(df[,cols])))
```

## IRI: Interpersonal Reactivity Index

#### Rename `IRI` columns

```{r IRI-Rename}
# Get Column Numbers
cols <- which(colnames(df)=="IRI_1.pn"):which(colnames(df)=="IRI_28.pn")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "_", replacement = "", x = colnames(df[,cols])))
```

## ISS: Index of Sexual Satisfaction

```{r ISS-rename}
# Get Column Numbers
cols <- which(colnames(df)=="ISS_1.pn"):which(colnames(df)=="ISS_25.pn")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "_", replacement = "", x = colnames(df[,cols])))
```

## LAPR: Life Attitudes Profile—Revised

```{r LAP-R-rename}
# Get Column Numbers
cols <- which(colnames(df)=="LAP.R_1.pn"):which(colnames(df)=="LAP.R_16.pn")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("LAPR",
                     c(1, 2, 5, 7, 12, 16,
                       18, 26, 27, 29, 31, 35, 
                       37, 38, 46, 48), 
                     ".pn", sep = ""))
```

## LEC: Life Experiences Checklist

```{r LEC-rename}
# Get Column Numbers
cols <- which(colnames(df)=="LEC_1.pn"):which(colnames(df)=="LEC_17.pn")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "_", replacement = "", x = colnames(df[,cols])))
```

## LES: Life Experiences Scale

#### Rename `LES` columns

##### *Happened*

```{r}
# Get Column Numbers
cols <- which(colnames(df)=="LES.1_1.pn"):which(colnames(df)=="LES.1_22.pn")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("LES", 1:22, "_hap.pn", sep = ""))
```

##### *Impact*

```{r}
# Get Column Numbers
cols <- which(colnames(df)=="LES.2_1.pn"):which(colnames(df)=="LES.2_22.pn")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("LES", 1:22, "_impact.pn", sep = ""))
```

## MAAS/PAAS: Maternal/Paternal Antenatal Attachment Scale

### Rename `MAAS` columns

```{r MAAS-rename,}
# Get Column Numbers
cols <- which(colnames(df)=="Q106.pn"):which(colnames(df)=="Q124.pn")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("MAAS", 1:19, ".pn", sep = ""))
```

### Rename `PAAS` columns

```{r PAAS-rename,}
# Get Column Numbers
cols <- which(colnames(df)=="Q90.1.pn"):which(colnames(df)=="Q105.pn")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("PAAS", 1:16, ".pn", sep = ""))
```

## MAT: Marital Adjustment Test

```{r MAT-rename}
# Get Column Numbers
cols <- which(colnames(df)=="MAT_1.pn"):which(colnames(df)=="MAT_15.pn")

# Set New Names
setnames(df, 
         old = colnames(df[,cols]), 
         new = 
           c(paste("MAT", 1:11, ".pn", sep = ""),
             "MAT12a.pn", "MAT12b.pn",
             paste("MAT", 13:15, ".pn", sep = "")))
```

## MOS Social Support

```{r MOS-rename}
# Get Column Numbers
cols <- which(colnames(df)=="MOS_1.pn"):which(colnames(df)=="MOS_19.pn")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "_", replacement = "", x = colnames(df[,cols])))
```

## PAS: Pregnancy Anxiety Scale

```{r PAS-rename}
# Get Column Numbers
cols <- which(colnames(df)=="Q72_1.pn"):which(colnames(df)=="Q73_7.pn")

# Set New Names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("PAS", 1:13, ".pn", sep = ""))

```

## Pregnancy/Couvade Syndrome Symptoms

#### Rename `PregSymp` Columns

##### Presence/ Absence

```{r}
# Get Column Numbers
cols <- which(colnames(df)=="PregSymp.1_1.pn"):which(colnames(df)=="PregSymp.1_44.pn")

# Set New Names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("PregSymp", 1:44, "_presence.pn", sep = ""))

```

##### Severity

```{r}
# Get Column Numbers
cols <- which(colnames(df)=="PregSymp.2_1.pn"):which(colnames(df)=="PregSymp.2_44.pn")

# Set New Names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("PregSymp", 1:44, "_severe.pn", sep = ""))
```

##### Distressing-ness

```{r}
# Get Column Numbers
cols <- which(colnames(df)=="PregSymp.3_1.pn"):which(colnames(df)=="PregSymp.3_44.pn")

# Replace ".3" in column names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("PregSymp", 1:44, "_distress.pn", sep = ""))
```

##### Frequency (removed from dataset)

```{r}
df <- select(df, -c(starts_with("PregSymp.4")))
```

## PSAM: Pregnancy Specific Anxiety Scale
```{r PSAM-rename}
# Get Column Numbers
cols <- which(colnames(df)=="PSAM_1.pn"):which(colnames(df)=="PSAM_13.pn")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "_", replacement = "", x = colnames(df[,cols])))
```

## PSQI: Pittsburgh Sleep Quality Index

```{r}
# Get Column Numbers
cols <- which(colnames(df)=="Q84.pn"):which(colnames(df)=="Q98.pn")
# Set new names
setnames(df, 
         old = colnames(df[,cols]),
         new = c(
           # Questions 1-4
           paste("PSQI", 1:4, ".pn", sep = ""), 
           # Question 5a-5j
           paste("PSQI", "5", letters[1:10], ".pn", sep = ""), 
           # Questions 6-9
           new = paste("PSQI", c(9, 6:8), ".pn", sep = "")))

# Relocate question 9 to be in the correct order
df <- df %>%
  relocate(PSQI9.pn, .after = PSQI8.pn)
         
```

## PSS: Perceived Stress Scale

```{r PSS-rename}
# Get Column Numbers
cols <- which(colnames(df)=="PSS_1.pn"):which(colnames(df)=="PSS_14.pn")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "_", replacement = "", x = colnames(df[,cols])))
```

## RF: Risky Families

#### Rename `RF` Columns

```{r RF-rename}
# Get Column Numbers
cols <- which(colnames(df)=="RF_1.pn"):which(colnames(df)=="RF_11.pn")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "_", replacement = "", x = colnames(df[,cols])))
```

## SCL: Symptoms Checklist 90

-   "Thoughts and images of a frightening nature (83)" replaces "feeling
    pushed to get things done (86)"

#### Rename `SCL` columns

```{r SCL-rename}
# Get Column Numbers
cols <- which(colnames(df)=="SCL90_1.pn"):which(colnames(df)=="SCL90_87.pn")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("SCL", c(1:14, # rename 1-14; remove 15
                              16:58, # rename 16-58; remove 59
                              60:62, # rename 60-62; remove 63
                              64:90), # rename 64-90
                     ".pn", sep = ""))
```

## STAI: State-Trait Anxiety Index

```{r STAI-rename}
# Get Column Numbers
cols <- which(colnames(df)=="STAI_State_1.pn"):which(colnames(df)=="STAI_Trait_20.pn")

# Set new names (State)
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "State_", replacement = "s", x = colnames(df[,cols])))

# Set new names (Trait)
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "Trait_", replacement = "t", x = colnames(df[,cols])))
```

## WIAF: What is a Father

#### Rename `WIAF` columns

```{r WIAF-rename}
# Get Column Numbers
cols <- which(colnames(df)=="WIAF_1.pn"):which(colnames(df)=="WIAF_15.pn")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "_", replacement = "", x = colnames(df[,cols])))
```
:::

# Write CSV File

```{r}
write_sav(df, here("data/3_renamed", "0pn_renamed.sav"))
```

