---
title: "3-Month Postpartum"
subtitle: "Rename Qualtrics Items"
format:
  html:
    toc: true
    toc-float: true
    df-print: paged
    code-folding: show
editor_options: 
  markdown: 
    wrap: 72
---

```{r include=FALSE}
knitr::opts_chunk$set(fig.width=2, fig.height=2, fig.align = "center")
```



# Set Up 
::: panel-tabset
## Packages
```{r load-pkg, message=FALSE, warning=FALSE}
library(tidyverse) # for data cleaning
library(here) # to quickly find data files
library(haven) # to manipulate SPSS files and add SPSS-style labels
library(chron) # to manipulate time and date variables
library(sjmisc) # for rowwise functions (row_count function)
library(data.table) # for renaming variables (setnames function)
library(kableExtra) # to print tables more neatly (kbl wrapping function) 
library(nestclean) # the package I wrote to help check our work
```


## Load Data
```{r load-data}
df <- read.csv(here("data/2_combined", "3pp_raw_combined.csv")) %>%
  mutate(across(where(is.character), ~ na_if(.x, ""))) %>% # replace blank cells with NA
  select(-Q129...Topics.3pp) %>% # remove meaningless column 
  select(where(~ !all(is.na(.)))) # remove blank columns
```
:::
    
    

# Demographics
::: panel-tabset
## Baby Weight
```{r}
# Set new names
setnames(df, 
         old = c("Baby.Weigh_1.3pp", "Baby.Weigh_2.3pp"),
         new = c("BabyWeight_lb.3pp", "BabyWeight_oz.3pp"))
```

## Age, Weight, Exercise
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="Age_1.3pp"):which(colnames(df)=="Exercise_1.3pp")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "_1", replacement = "", x = colnames(df[,cols])))
```

## Sleep
```{r}
# Set new names
setnames(df, 
         old = c("Sleep_1.3pp"),
         new = c("Sleep.3pp"))

# Move columns
df <- df %>%
  relocate(Sleep.3pp, .after = Exercise.3pp)
```

## Smoking
```{r}
# Set new names
setnames(df, 
         old = c("Packs.day_1.3pp", "Packs.day_2.3pp"),
         new = c("PackPerDay.3pp", "YearsSmoker.3pp"))

# Move columns
df <- df %>%
  relocate(Smoker.3pp:YearsSmoker.3pp, .after = Sleep.3pp)
```

## Breastfeeding
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="Breastfeed.3pp"):which(colnames(df)=="exclusive.3pp")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = c("BF_ever.3pp", "BF_current.3pp", "BF_length_months.3pp", "BF_length_day.3pp", "BF_exclusive.3pp"))
         
```

## Menstruation
```{r}
# Set new names
setnames(df, 
         old = c("Menstrual.3pp", "Q102.3pp"),
         new = c("Menstrual_start.3pp", "Menstrual_date.3pp"))
```

## Placenta
```{r}
# Set new names
setnames(df, 
         old = c("Placenta.3pp", "Q105.3pp"),
         new = c("Placenta_ingest.3pp", "Placenta_form.3pp"))
```

## Check Demographics 
::: panel-tabset
### Check Names
```{r}
inspect_labels(df, CoupleID:Placenta_form.3pp) 
```

### Print
```{r eval = knitr::is_html_output(), echo = FALSE}
print_slice(df, CoupleID:Placenta_form.3pp)
```
:::
:::

# Inventories 
::: panel-tabset
## ASQ: Ages and Stages Questionnaire, 2+4 month
::: panel-tabset
### Communication (c)
#### 2 Months
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q106_1.3pp"):which(colnames(df)=="Q106_6.3pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("ASQ2_c", 1:6, ".3pp", sep = ""))
```

#### 4 Months
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q106_7.3pp"):which(colnames(df)=="Q106_10.3pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("ASQ4_c", 3:6, ".3pp", sep = ""))

# Add duplicates from 2mo
df <- df %>%
  mutate(ASQ4_c1.3pp = ASQ2_c5.3pp, 
         ASQ4_c2.3pp = ASQ2_c6.3pp, 
         .before = ASQ4_c3.3pp, .keep = "all")
```

### Gross Motor (gm)
#### 2 Months
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q106_11.3pp"):which(colnames(df)=="Q106_16.3pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("ASQ2_gm", 1:6, ".3pp", sep = ""))
```

#### 4 Months
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q106_17.3pp"):which(colnames(df)=="Q106_20.3pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("ASQ4_gm", 3:6, ".3pp", sep = ""))

# Add duplicates from 2mo
df <- df %>%
  mutate(ASQ4_gm1.3pp = ASQ2_gm5.3pp, 
         ASQ4_gm2.3pp = ASQ2_gm6.3pp, 
         .before = ASQ4_gm3.3pp, .keep = "all")
```

### Fine Motor (fm)
#### 2 Months
##### Questions 1-3
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q106_21.3pp"):which(colnames(df)=="Q106_23.3pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("ASQ2_fm", 1:3, ".3pp", sep = ""))
```

##### Questions 4-6
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q106_25.3pp"):which(colnames(df)=="Q106_27.3pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("ASQ2_fm", 4:6, ".3pp", sep = ""))
```

#### 4 Months
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q106_28.3pp"):which(colnames(df)=="Q106_30.3pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("ASQ4_fm", 4:6, ".3pp", sep = ""))

# Add duplicates from 2mo and rename question #2
df <- df %>%
  mutate(ASQ4_fm1.3pp = ASQ2_fm5.3pp, 
         ASQ4_fm3.3pp = ASQ2_fm6.3pp) %>%
  rename(ASQ4_fm2.3pp = Q106_24.3pp) %>%
  relocate(ASQ4_fm1.3pp, ASQ4_fm2.3pp, ASQ4_fm3.3pp, .before = ASQ4_fm4.3pp)
```

### Problem Solving (ps)
#### 2 Months
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q106_31.3pp"):which(colnames(df)=="Q106_36.3pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("ASQ2_ps", 1:6, ".3pp", sep = ""))
```

#### 4 Months
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q106_37.3pp"):which(colnames(df)=="Q106_38.3pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("ASQ4_ps", 4:5, ".3pp", sep = ""))

# Add duplicates from 2mo
df <- df %>%
  mutate(ASQ4_ps1.3pp = ASQ2_ps3.3pp, 
         ASQ4_ps2.3pp = ASQ2_ps4.3pp, 
         ASQ4_ps3.3pp = ASQ2_ps5.3pp, 
         ASQ4_ps6.3pp = ASQ2_ps6.3pp) %>%
  relocate(ASQ4_ps1.3pp:ASQ4_ps3.3pp, ASQ4_ps4.3pp, ASQ4_ps5.3pp, ASQ4_ps6.3pp, .after = ASQ2_ps6.3pp)
```

### Personal/Social (s)
#### 2 Months
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q106_39.3pp"):which(colnames(df)=="Q106_44.3pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("ASQ2_s", 1:6, ".3pp", sep = ""))
```

#### 4 Months
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q106_45.3pp"):which(colnames(df)=="Q106_48.3pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("ASQ4_s", c(2, 4:6), ".3pp", sep = ""))

# Add duplicates from 2mo
df <- df %>%
  mutate(ASQ4_s1.3pp = ASQ2_s5.3pp, 
         ASQ4_s3.3pp = ASQ2_s6.3pp) %>%
  relocate(ASQ4_s1.3pp, ASQ4_s2.3pp, ASQ4_s3.3pp, .before = ASQ4_s4.3pp)
```

### Overall (o)
#### 2 Months
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q107.3pp"):which(colnames(df)=="Q112.3pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("ASQ2_o", 1:6, ".3pp", sep = ""))
```

#### 4 Months
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q114.3pp"):which(colnames(df)=="Q117.3pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("ASQ4_o", c(2, 3, 5, 6), ".3pp", sep = ""))

# Add duplicates from 2mo
df <- df %>%
  mutate(ASQ4_o1.3pp = ASQ2_o2.3pp, 
         ASQ4_o4.3pp = ASQ2_o3.3pp, 
         ASQ4_o7.3pp = ASQ2_o5.3pp, 
         ASQ4_o8.3pp = ASQ2_o6.3pp) %>%
  relocate(ASQ4_o1.3pp, ASQ4_o2.3pp, ASQ4_o3.3pp, ASQ4_o4.3pp,
           ASQ4_o5.3pp, ASQ4_o6.3pp, ASQ4_o7.3pp, ASQ4_o8.3pp,
           .after = ASQ2_o6.3pp)
```

### Relocate
```{r}
df <- df %>%
  relocate(contains("ASQ4"), .after = ASQ2_o6.3pp)
```

### Check
```{r}
inspect_labels(df, contains("ASQ"))
```
:::

## BCQ: Baby Care Questionnaire
### Sleep
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q94_1.3pp"):which(colnames(df)=="Q94_9.3pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("BCQ_S", c(1:9), ".3pp", sep = ""))
```

### Eating
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q94_10.3pp"):which(colnames(df)=="Q94_19.3pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("BCQ_E", c(1:3, 6, 7, 10, 4, 5, 8, 9), ".3pp", sep = ""))

# Reorder variables
df <- df %>%
  relocate(BCQ_E4.3pp, BCQ_E5.3pp, BCQ_E6.3pp, BCQ_E7.3pp, BCQ_E8.3pp, BCQ_E9.3pp, BCQ_E10.3pp, .after = BCQ_E3.3pp)
```

### Soothing
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q94_20.3pp"):which(colnames(df)=="Q94_30.3pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("BCQ_So", c(1, 2, 4, 9, 10, 3, 5:8, 11), ".3pp", sep = ""))

# Reorder variables
df <- df %>%
  relocate(BCQ_So3.3pp, BCQ_So4.3pp, BCQ_So5.3pp:BCQ_So8.3pp, BCQ_So9.3pp, BCQ_So10.3pp, BCQ_So11.3pp, .after = BCQ_So2.3pp)
```

### Check
```{r}
inspect_labels(df, contains("BCQ"))
```





## BDI: Beck Depression Inventory
```{r BDI-rename}
# Get Column Numbers
cols <- which(colnames(df)=="BDI1_Sad.3pp"):which(colnames(df)=="BDI21_Sex.3pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("BDI", c(1:8, 10:21), ".3pp", sep = ""))
```

## DAS: Dyadic Adjustment Scale
```{r DAS-rename}
# Get Column Numbers
cols <- which(colnames(df)=="DAS1.15_1.3pp"):which(colnames(df)=="DAS.32.3pp")

# Set New Names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("DAS", 1:32, ".3pp", sep = ""))
```

## EPDS: Edinburgh Postnatal Depression Scale
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="PDS_1.3pp"):which(colnames(df)=="PDS_9.3pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "PDS_", replacement = "EPDS", x = colnames(df[,cols])))
```

## IBQR: Infant Behavior Questionnaire-Revised
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q87_1.3pp"):which(colnames(df)=="Q87_37.3pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "Q87_", replacement = "IBQR", x = colnames(df[,cols])))
```

## MAI: Maternal Attachment Inventory
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="Q102_1.3pp"):which(colnames(df)=="Q102_26.3pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("MAI", c(1:26), ".3pp", sep = ""))
```

## MAT: Marital Adjustment Test
```{r MAT-rename}
# Get Column Numbers
cols <- which(colnames(df)=="MAT_1.3pp"):which(colnames(df)=="MAT_15.3pp")

# Set New Names
setnames(df, 
         old = colnames(df[,cols]), 
         new = 
           c(paste("MAT", 1:11, ".3pp", sep = ""),
             "MAT12a.3pp", "MAT12b.3pp",
             paste("MAT", 13:15, ".3pp", sep = "")))
```


## MOS Social Support
```{r MOS-rename}
# Get Column Numbers 
cols <- which(colnames(df)=="Q103_1.3pp"):which(colnames(df)=="Q103_19.3pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("MOS", 1:19, ".3pp", sep = ""))
```

## MPAS/PPAS: Maternal/Paternal Postnatal Attachment Scale
### MPAS
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q129.1.3pp"):which(colnames(df)=="Q147.3pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("MPAS", 1:19, ".3pp", sep = ""))
```

### PPAS
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q103.3pp"):which(colnames(df)=="Q121.3pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("PPAS", 1:19, ".3pp", sep = ""))
```

## PBQ: Postpartum Bonding Questionnaire
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q119_1.3pp"):which(colnames(df)=="Q119_25.3pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "Q119_", replacement = "PBQ", x = colnames(df[,cols])))
```

## PingSS: Parenting Stress Scale
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="PingSS_1.3pp"):which(colnames(df)=="PingSS_18.3pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "_", replacement = "", x = colnames(df[,cols])))
```

## PSI: Parenting Stress Index
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="PSI_1.3pp"):which(colnames(df)=="PSI_33.1.3pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("PSI", c(1:21, 23:31, 34:36, 22, 32, 33), ".3pp", sep = ""))

# Reorder variables
df <- df %>%
  relocate(c(PSI22.3pp, PSI23.3pp:PSI31.3pp, PSI32.3pp:PSI33.3pp), .after = PSI21.3pp)
```
## PSQI: Pittsburgh Sleep Quality Index
```{r}
# Get Column Numbers
cols <- which(colnames(df)=="Q123.3pp"):which(colnames(df)=="Q137.3pp")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = c(
           # Questions 1-4
           paste("PSQI", 1:4, ".3pp", sep = ""),
           # Questions 5a-5j
           paste("PSQI", "5", letters[1:10], ".3pp", sep = ""), 
           # Questions 6-9
           paste("PSQI", c(9, 6:8), ".3pp", sep = "")))

# Relocate question 9 to be in the correct order
df <- df %>%
  relocate(PSQI9.3pp, .after = PSQI8.3pp)
```



## PSS: Perceived Stress Scale
```{r PSS-rename}
# Get Column Numbers
cols <- which(colnames(df)=="PSS_1.3pp"):which(colnames(df)=="PSS_14.3pp")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = gsub(pattern = "_", replacement = "", x = colnames(df[,cols])))
```



## SCL: Symptom Checklist 90 
- in the 3pp version, #87 and #88 have been accidentally combined to read "The idea that something serious is wrong with your body ever feeling close to another person"
- we will treat that item as #87 ("The idea that something serious is wrong with your body")
- "Thoughts and images of a frightening nature (83)" replaces "feeling pushed to get things done (86)"

```{r SCL-rename}
# Get Column Numbers
cols <- which(colnames(df)=="SCL90_1.3pp"):which(colnames(df)=="SCL90_86.3pp")
# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = paste("SCL", c(1:14, # rename 1-14; remove 15
                              16:58, # rename 16-58; remove 59
                              60:62, # rename 60-62; remove 63
                              64:86, # rename 64-90; remove 87
                              88:90), 
                     ".3pp", sep = ""))
```
:::





# HATCH-Designed Questions
::: panel-tabset
## COVID Parenting Questions
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q182.3pp"):which(colnames(df)=="Q192.3pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = c("COVID_precautions.3pp",
                 "COVID_impact.3pp", 
                 #"COVID_childcare.3pp", # not actually in 3pp?
                 "COVID_contact_community.3pp", 
                 "COVID_contact_coworkers.3pp", 
                 "COVID_contact_friends.3pp",
                 "COVID_contact_family.3pp", 
                 "COVID_contact_partner.3pp",
                 "COVID_social.3pp", 
                 "COVID_mh.3pp", 
                 "COVID_parenting.3pp", 
                 "COVID_work.3pp", 
                 "COVID_contracted.3pp", 
                 "COVID_baby.3pp", 
                 "COVID_open.3pp"))
```

## PRQ: Parenting Responsibilities Questionnaire
```{r}
# Get Column Numbers 
cols <- which(colnames(df)=="Q148.3pp"):which(colnames(df)=="Q154.3pp")

# Set new names
setnames(df, 
         old = colnames(df[,cols]), 
         new = c("PRQ_WeekTot.3pp", 
                 "PRQ_WeekPrimary.3pp", 
                 "PRQ_WkendTot.3pp", 
                 "PRQ_WkendPrimary.3pp", 
                 "PRQ_Share.3pp"))
```
:::

# Finishing up 
::: panel-tabset
## Reorder alphabetically
```{r}
df <- df %>%
  relocate(
    # Inventories
    contains("ASQ"), 
    contains("BCQ"), 
    contains("BDI"), 
    contains("DAS"), 
    contains("EPDS"), 
    contains("IBQR"), 
    contains("MAI"), 
    contains("MAT"), 
    contains("MOS"), 
    contains("MPAS"), 
    contains("PPAS"), 
    contains("PBQ"),
    contains("PingSS"), 
    contains("PSI"), 
    contains("PSQI"), 
    contains("PSS"), 
    contains("SCL"), 
    
    # HATCH Items
    contains("COVID"), 
    contains("PRQ"), 
    .after = Placenta_form.3pp
  )
```

## Check for unnamed 
```{r}
inspect_labels(df, Placenta_form.3pp:ncol(df))
```

## Write CSV Files
```{r}
write_sav(df, here("data/3_renamed", "3pp_renamed.sav"))
```

:::

